### 2015-12-15 Bellec_ADHD200_2016.tex
Initial ShareLaTeX Import

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,12pt,1p]{elsarticle}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{url}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

\biboptions{sort&compress}

\journal{Neuroimage}

\begin{document}

\begin{frontmatter}

\title{The ADHD200 preprocessed experiment:\\lowering the barriers to a neuroimaging competition}

%\tnotetext[label0]{This is only an example}

\author[label0,label1,label2]{Pierre Bellec\corref{cor1}}
\address[label0]{The Neuro Bureau Research Institute, Leipzig, Germany}
\address[label1]{Centre de Recherche de l'Institut Universitaire de G\'eriatrie de Montr\'eal, Montr\'eal, CA}
\address[label2]{D\'epartement d'Informatique et de Recherche Op\'erationnelle, Universit\'e de Montr\'eal, Montr\'eal, CA}

\cortext[cor1]{Corresponding authors.}

\ead{pierre.bellec@criugm.qc.ca}
\ead[url]{bellec.simexp-lab.org}

\author[label0,label3]{Carlton Chu}
\address[label3]{Deep Mind, London, UK}
\ead{carltonchu1@gmail.com}

\author[label0,label1,label4]{Fran\c{c}ois Chouinard-Descortes}
\address[label4]{McGill University, Montreal, CA}
\ead{carltonchu1@gmail.com}

\author[label0,label5]{Daniel S. Margulies}
\address[label5]{Max Planck Insitute, Leipzig, GER}
5\ead{daniel.margulies@gmail.com}

\author[label0,lab6,lab7]{R. Cameron Craddock\corref{cor1}}
\address[lab6]{Computational Neuroimaging Laboratory, Center for Biomedical Imaging and Neuromodulation, Nathan S. Kline Institute for Psychiatric Research, Orangeburg, NY, USA}
\address[lab7]{Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
\ead{ccraddock@nki.rfmh.org}
\ead[url]{computational-neuroimaging-lab.org}

\begin{abstract}
Text of abstract. Text of abstract. Text of abstract. Text of abstract. Text of abstract. 
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
preprocessed fMRI, data sharing, neuroimaging competition
\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

\section{Introduction}

In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention deficit hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (R-fMRI) data \cite{Milham2012}. The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent studies and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}. The data includes R-fMRI, structural MRI (sMRI), and basic phenotypic information for 973 individuals (554 TDC, 419 ADHD) \cite{Milham2012}. Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels for test data for which diagnostic information was withheld. The competition data was distributed in a raw form and before any analysis could begin, had to be preprocessed to make it comparable across individuals and to remove nuisance variation that would obscure the underlying biological signal. These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to the high performance computing resources required to process such a large data collection in a short amount of time. Realizing this barrier to entry for  statisticians and computer scientists, who were potentially the most qualified for the machine learning aspect of the competition, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.

The ``ADHD-200 Preprocessed'' is a repository of preprocessed R-fMRI and sMRI data along with statistical derivatives from the ADHD-200 Sample. Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated. The Athena pipeline processing R-fMRI and sMRI images using a custom BASH script that combines functionality from AFNI \cite{Cox1996} and FSL \cite{Smith2004} neuroimaging toolkits. The Burner pipeline used SPM8 \cite{ashburner} to process sMRI data for voxel-based morphometry style analyses. The NIAK pipeline was implemented using tools from the neuroimaging analysis kit (NIAK) \cite{bellecNIAK} pipelined together using the Pipeline System for Octave and Matlab (PSOM) \cite{slcPSOM} to process both sMRI and R-fMRI datasets. The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}. The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians with limited prior neuroimaging experience \cite{Eloyan2012}. The initiative has had an significant impact beyond the competition, having been used in 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} in just over 3 years, with more in press or under review.

\section{Contents of the repository}

The ADHD-200 preprocessed data was released in the summer of 2012 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}. No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account. This registration enables downloads to be tracked for usage statistics and so that users can be contacted in the event that errors are found. The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/adhd200/}}. There are no more restrictions placed on the preprocessed data or derivatives other than the request that the ADHD-200 Preprocessed Initiative is cited appropriately and that the specific pipeline is acknowledged in publications using the data. A forum is available on the Neuro Bureau's NITRC project page for users to ask questions or report
problems\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=2046}}. Questions regarding data acquisition or phenotypic variables should be directed to INDI's support forum\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=1735}}. 
\par
ADHD-200 Preprocessed data is available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative. The following preprocessed derivatives are available.

\begin{table}[!ht]
\caption{{\bf Summary of ADHD-200 data by site.}}\label{part_tab}
  \begin{tabular}{L{.1in}L{.1in}L{1.1in}L{1.1in}L{1.1in}L{.7in}}
    \hline
	\\
    \multicolumn{3}{l}{\textbf{Bradley Hostpital/Brown University}} & & \\
    & \multicolumn{4}{l}{\emph{Scanner:} Siemens TIM Trio 3T}\\
    & \multicolumn{5}{l}{\emph{sMRI:} 3D MPRAGE, FA = 9$^{\circ}$, TR = 2250 ms, TE = 2.98 ms,}\\
    & &  \multicolumn{3}{l}{TI = 900 ms, $1\times1\times1$ mm$^3$} \\
    & \multicolumn{4}{l}{\emph{R-fMRI:} EPI w/ prospective motion correction (PACE), FA = 9$^{\circ}$,}\\
    & & \multicolumn{4}{l}{TR = 2000 ms, TE = 25 ms, 35 3-mm thick slices, $3.0 \times 3.0$ mm$^2$}\\
    & & \multicolumn{4}{l}{in-plan resolution. Participants were asked to relax with their eyes}\\
    & & \multicolumn{4}{l}{open and fixate on the text ``relax'' that was projected on a screen.}\\
    & \multicolumn{2}{l}{\emph{TDC}:} 27, 
    %& \multicolumn{4}{l} \emph{T1 weighted anatomical scans:}  
	\hline
	\end{tabular}
\end{table}

\subsection{The Athena and NIAK pipelines}

\paragraph{Preprocessed sMRI and R-fMRI} Both the Athena and NIAK pipelines released denoised R-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz). Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL .xfm transform files for Athena and in .xfm MINC files for NIAK. In addition, the estimated motion parameters (bundled with additional intermediate outputs) were released in separate archives, inside text files (AFNI .1D tab-separated-value files) for Athena, and inside Matlab HDF5 files for NIAK.

\paragraph{Regional time series} Regional time series were extracted based on a series of different brain parcellations. The Athena ppipeline used functional parcels generated by a spectral clustering method (Craddock et al. 2012) as well as a number of parcellations established from anatomical landmarks, with a resolution ranging from 93 to 351 parcels. The NIAK pipeline only used functional parcels generated by a region growing method (Bellec et al. 2006) with two resolutions: 954 and 2843 parcels. The Athena pipeline distributed regional time series as text files (.1D AFNI) and the NIAK distributed them as HDF5 files (.mat Matlab). All brain parcellations were also released as compressed nifti files (.nii.gz). Note that the phenotypic information of the ADHD200 sample was also released as comma-separated-values files (.csv).

\paragraph{Other derivatives}
The Athena pipeline derived a number of additional metrics from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on the (Smith et al. 2009) group independent component analysis (ICA) with 10 resting-state networks. One compressed nifti file (.nii.gz) was released per fMRI dataset and type of derivative, with in addition the time courses of the dual regression available in text files (.1D AFNI).

\subsection{The Burner pipeline}

The Burner pipeline included a segmentation of the grey matter of the structural scans, after a non-linear transformation in stereotaxic space was generated by the DARTEL tool from SPM8. Note that this release was purely based on structural MRI, and did not include any fMRI derivatives. This pipeline was specifically oriented towards a voxel-based-morphometry analysis of the ADHD200 sample, which could be used as a complement of the functional analysis perfomed with the two other pipelines.

\section{Processing strategies}

\subsection{Preprocessed sMRI and R-fMRI}
% http://onlinelibrary.wiley.com/doi/10.1002/hbm.22790/epdf
\paragraph{The Athena pipeline} The preprocessing steps of functional MRI datasets included removal of the first four volumes to allow for magnetization to reach equilibrium, slice timing correction, motion correction, normalization to MNI152 standard space at 4 mm isotropic voxel resolution, regression of nuisance covariates including head motion parameters, global mean, white matter, and cerebrospinal ﬂuid signals, band-pass filtering of fMRI ($0.009 Hz < f < 0.08 Hz$) to reduce low-frequency drift and high-frequency physiological noise, and finally spatial smoothing with a 6 mm full-width-at-half-maximum isotropic Gaussian kernel.

\paragraph{The NIAK pipeline} The preprocessing steps followed those of the Athena pipeline with the following differences: (1) only the first three volumes were suppressed, instead of four; (2) only a high-pass filter was implemented ($0.009 Hz < f$), instead of a band pass, and no regression of confounds such as motion parameters, global average, etc. Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{Perlbarg2007}. The fMRI volumes were resampled in stereotaxic space at 3 mm isotropic (instead of 4 mm), and this was done only right before spatial smoothing. Finally note that although both Athena and NIAK used the MNI non-linear stereotaxic template space described in \citep{Fonov2011}, the NIAK used the young adult (ICBM152) symmetric variant, while Athena used the NIHPD asymmetric pediatric template (4.5 y.o.-18.5 y.o.).

\subsection{Regional time series}

For both Athena and NIAK, regional time series were extracted by averaging preprocessed resting-state volumes within different brain regions. The Athena pipeline first used a series of anatomical templates:
\begin{itemize}
\item The automated anatomical labeling (AAL) template \citep{Tzourio-Mazoyer} 
\item The Eickhoff-Zilles (EZ) [8]
\end{itemize}
, , Talairach and Tournoux (TT) [9], and Harvard-Oxford (HO) anatomical atlases. In addition,  as well as, 200 (CC200) and 400 (CC400) ROI atlases derived from functionally parcellating the resting state data [10]. The AAL atlas is distributed with the AAL Toolbox. The atlas was fractionated into functional space using nearest-neighbor interpolation.
The EZ atlas was derived from the max-propagation atlas distributed with the SPM Anatomy Toolbox. The atlas was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary and fractionated into functional space using nearest-neighbor interpolation.
The HO atlas distributed with FSL is split into cortical and subcortical probabilistic atlases. A 25\% threshold was applied to each of these atlases and they were subsequently bisected into left and right hemispheres at the midline (x=0). ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical atlas. The subcortical and cortical ROIs were combined and then fractionated into functional space using nearest-neighbor interpolation.
The TT atlas distributed with AFNI was coregistered and warped into template space and subsequently fractionated into functional space using nearest neighbor interpolation.
\par
Functional parcellation was accomplished using the two-stage spatially-constrained functional procedure described in [10]. Preprocessed and unfiltered resting state data corresponding to 650 subjects with the cleanest data (as determined by registration quality and applying a max translation < 3mm and max rotation < 3 degrees). A grey matter mask was constructed for the subjects by averaging grey matter masks derived from freesurfer automated segmentation. Subject specific connectivity graphs were constructed by treating each withen-gm-mask voxel as a node and edges corresponding to super-threshold temporal correlations to the voxels' 3D (27 voxel) neighborhood. Each subjects' graph was partitioned into 200 or 400 regions using normalized cut spectral clustering. Association matrices were constructed from the clustering results by setting the connectivity between voxels to 1 if they are in the same ROI and 0 otherwise. A group-level correspondance matrix was constructed by averaging the individual level association matrices and subsequently partitioned into 200 or 400 regions using normalized cut clustering.
\par 
Regional homogeneity was calculated for the preprocessed and filtered whole brain resting state data using the procedure described in [11]. The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo. 
\par 
The FC maps for the Smith PNAS 2009 RSNs were constructed using a modified dual regression approach. I used a spatial multiple regression to extract time courses corresponding to spatial templates of the 10 Smith PNAS 2009 RSNs, and then independently correlated each of the 10 time courses with whole brain data to generate subject-specific FC maps for each RSN. Dr. Steve Smith suggested that instead of using univariate correlation to generate the FC maps, that I use multiple regression instead. These files are the result of that analysis.

\subsection{The Burner Pipeline}
Details on the Burner pipeline can be found on the NITRC website\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NiakPipeline}}.
T1 images were segmented into grey matter and white matter probability maps using "New Segmentation" in SPM8. The tissue maps were rigidly aligned (translation+rotation). Inter subject normalization was performed using DARTEL toolbox in SPM8. Images were iteratively registered to the group average (population template), and template was updated iteratively. This resulted finer and finer registration. The registration parameters were applied to each image to transform each image into the space of population average. Modulation was applied to conserve the global tissue volumes after normalization.

\subsection{The NIAK pipeline}
Details on the NIAK pipeline can be found on the NITRC website.

% http://www.nitrc.org/plugins/mwiki/index.php/niak:FmriPreprocessing064#Summary_of_the_pipeline

% Add a few words on the generation of the regions and extraction of regional time series. 
To reduce the computational burden of the analysis, the spatial dimension of the individual fMRI dataset was reduced using a region-growing algorithm. The spatial dimension was selected arbitrarily by setting the size where the growing process stopped (a threshold of 1000 mm3 resulted into R=957 regions). The regions were built to maximize the homogeneity of the time series within the region, i.e. the average correlation between the time series associated with any pair of voxels of the region. The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance), such that the homogeneity was maximized on average for all subjects, and the small homogeneous regions are identical for all subjects. Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{Tzourio-Mazoyer2002}. See (Bellec et al. 2006) for more details regarding the implementation of the region-growing algorithm. Overall, this process reduced the dataset of each subject into a (T x R) data array, where T is the number of time samples and R is the number of regions.

\section{Quality control}

The Athena pipeline did suggest a number of automated metrics to guide quality controls, but left to end users the task of checking individual data. The output of the Burner pipeline were visually inspected by Dr Chu. The individual results of the NIAK pipeline were visually reviewed for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space. The quality control report also included metrics of individual motion and recommendation for subjects to exclude on the basis of excessive motion.

\emph{We need to mention the forum, give examples of the identification of bugs as well as the release of bug fixes (and problems that came with it because of the way we released the data). This has to be kept brief, it's not super exciting, but it is part of the guidelines of the special issue.}

\section{Lessons learned and future work}

The ADHD200 preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD200 competition, with over 9,500 downloads by more than 490 users.  In the short time since their release, these statistical derivatives have already been used to generate 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012,     DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012} and three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} in just over 3 years, with more in press or under review. An important feature of the ADHD200 preprocessed initiative was that the regional time series took the form of time x space arrays easy to manipulate for any data scientist, even without a background in imaging. As a result, the publications using ADHD200 preprocessed include articles published in journals outside of the the neuroimaging field, e.g. \citep{}. In particular, the winning team of the ADHD200 global competition was based at the Johns Hopkins Biostatistics Department and used ADHD200 preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
\par 
In terms of its secondary objective, almost all variants of processing strategies included in the ADHD200 release have been used in subsequent analysis, although with markedly different rates of re-use. The most popular pipeline by far has been Athena. \emph{... we need a specific breackdown for this ... I'll prepare a table}. No publication we are aware of actually implemented a face-to-face comparison between processing techniques. The higher re-use rate of the Athena pipeline compared to the NIAK may be due to the fact that it was released earlier, had the most comprehensive catalogue of derivatives and also used tools more popular in the fMRI community (FSL, AFNI) than NIAK (MINC). The Burner pipeline only generated derivatives of the structural data, which did not align well with the positioning of the ADHD200 competition. It should be noted that, with the approach we took, any direct comparison between Athena and NIAK was challenging, as the two pipelines did not use the same specific stereotaxic space, varied in every possible way in terms of selected parameters, and also had quite different approaches for QC or derivatives. There is no plan to expand or update the ADHD200 release as such, which we hope will continue to serve as a benchmark dataset. To the best of our knowledge, the ADHD200 preprocessed release was the first large public resource of preprocessed resting-state fMRI data, and remains to this date the only resource featuring a battery of alternative processing paths. 
\par 
The success of the ADHD200 preprocessed experiment illustrates the need for large-scale efforts to reduce computational barriers to participation in discovery neuroscience. This need is further emphasized by a recent survey of FCP/INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community. Unfortunately, the Neuro Bureau’s efforts have been limited to a fraction of the datasets that are available through FCP and INDI due to funding and manpower limitations, and represent only a fraction of the statistical derivatives that can be derived from the data. A much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data to accelerate neuroimaging research. We are now working on new initiatives learning from the ADHD200 experiment, notably including better harmonized processing and quality control strategies. This could critically help fMRI researchers to identify optimal analytical paths for a specific task.

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%% References with bibTeX database:

\bibliographystyle{elsarticle-num}
% \bibliographystyle{elsarticle-harv}
% \bibliographystyle{elsarticle-num-names}
% \bibliographystyle{model1a-num-names}
% \bibliographystyle{model1b-num-names}
% \bibliographystyle{model1c-num-names}
% \bibliographystyle{model1-num-names}
% \bibliographystyle{model2-names}
% \bibliographystyle{model3a-num-names}
% \bibliographystyle{model3-num-names}
% \bibliographystyle{model4-names}
% \bibliographystyle{model5-names}
% \bibliographystyle{model6-num-names}

\bibliography{adhd200_pubs}

\end{document}

%%
%% End of file `elsarticle-template-num.tex'.

### 2015-12-19 Bellec_ADHD200_2016.tex
Fixed methods and citations.

@@
 %%
-\documentclass[preprint,12pt,1p]{elsarticle}
+\documentclass[preprint,12pt,3p]{elsarticle}
+\usepackage{rotating}
 
 \usepackage{array}
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\arraybackslash\hspace{0pt}}p{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}p{#1}}
 
@@
 
-\title{The ADHD200 preprocessed experiment:\\lowering the barriers to a neuroimaging competition}
+\title{The Neuro Bureau ADHD-200 Preprocessed Repository}
 
-%\tnotetext[label0]{This is only an example}
+% - CC - What about just sticking to the name of the repository? The experiment
+% part might make people think that is not an ongoing data sharing initiative.
+% We are sharing more that just the statistical derivatives and
+% we are also sharing processed structural MRI. I think that capturing all of that
+% in a subtitle would be too long.
+% - PB - Agreed, it's a cool title.
+
+% The ADHD-200 Preprocessed experiment: lowering the barriers to a neuroimaging competition
+% The ADHD-200 Preprocessed Repository:\Openly sharing preprocessed data and derivatives
 
 \author[label0,label1,label2]{Pierre Bellec\corref{cor1}}
-\address[label0]{The Neuro Bureau Research Institute, Leipzig, Germany}
+\address[label0]{The Neuro Bureau}
 \address[label1]{Centre de Recherche de l'Institut Universitaire de G\'eriatrie de Montr\'eal, Montr\'eal, CA}
@@
 \author[label0,label5]{Daniel S. Margulies}
-\address[label5]{Max Planck Insitute, Leipzig, GER}
-5\ead{daniel.margulies@gmail.com}
+\address[label5]{Max Planck Research Group for Neuroanatomy \& Connectivity, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany}
+\ead{daniel.margulies@gmail.com}
 
@@
 \begin{abstract}
-Text of abstract. Text of abstract. Text of abstract. Text of abstract. Text of abstract. 
+In 2011, the ``ADHD-200 Global Competition'' was held with the aim of identifying biomarkers of attention deficit hyperactivity disorder from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data collected on 973 individuals.
+Statisticians and computer scientists were potentially the most qualified for the machine learning aspect of the competition, but generally lacked the specialized skills to implement the necessary steps of data preparation for rs-fMRI.
+Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC) (\url{http://www.nitrc.org/frs/?group_id=383}).
+This ``ADHD200 preprocessed'' release included multiple analytical pipelines to cater to different philosophies of data analysis.
+The processed derivatives included denoised and registered 4D fMRI volumes, regional time series extracted from brain parcellations, maps of 10 intrinsic connectivity networks, fractional amplitude of low frequency fluctuation, and regional homogeneity, along with grey matter density maps.
+The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians.
+To the best of our knowledge, the ADHD200 preprocessed release was the first large public resource of preprocessed resting-state fMRI and structural MRI data, and remains to this day the only resource featuring a battery of alternative processing paths.
 \end{abstract}
@@
 % \linenumbers
-
+\section{Highlights}
+\begin{itemize}
+\item Processed derivatives generated from structural and resting-state fMRI in 973 individuals. 
+\item The sample includes 585 typically developing children, 362 children with attention deficit hyperactivity disorder, and 26 with unknown diagnostic status.
+\item Functional MRI volumes were denoised and aligned using two alternative processing pipelines. 
+\item Derivatives include regional time series, grey matter segmentation as well as two variants of connectivity maps and a measure of intrinsic brain activity. 
+\item These resources are freely available, with minimal access requirements. 
+\end{itemize}
 \section{Introduction}
 
-In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention deficit hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (R-fMRI) data \cite{Milham2012}.
-The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent studies and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}.
-The data includes R-fMRI, structural MRI (sMRI), and basic phenotypic information for 973 individuals (554 TDC, 419 ADHD) \cite{Milham2012}.
+In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention deficit hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}.
+The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}.
+The data includes rs-fMRI, structural MRI (sMRI), and basic phenotypic information for 973 individuals (585 TDC, 362 ADHD, 26 unknown) \cite{Milham2012}.
 Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels for test data for which diagnostic information was withheld.
@@
 These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to the high performance computing resources required to process such a large data collection in a short amount of time.
-Realizing this barrier to entry for  statisticians and computer scientists, who were potentially the most qualified for the machine learning aspect of the competition, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.
+This category includes statisticians and computer scientists, who were potentially the most qualified for the machine learning aspect of the competition.
+Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.
 
-The ``ADHD-200 Preprocessed'' is a repository of preprocessed R-fMRI and sMRI data along with statistical derivatives from the ADHD-200 Sample.
+The ``ADHD-200 Preprocessed'' is a repository of preprocessed rs-fMRI and s-MRI data along with statistical derivatives from the ADHD-200 Sample.
 Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated.
-The Athena pipeline processing R-fMRI and sMRI images using a custom BASH script that combines functionality from AFNI \cite{Cox1996} and FSL \cite{Smith2004} neuroimaging toolkits.
-The Burner pipeline used SPM8 \cite{ashburner} to process sMRI data for voxel-based morphometry style analyses.
-The NIAK pipeline was implemented using tools from the neuroimaging analysis kit (NIAK) \cite{bellecNIAK} pipelined together using the Pipeline System for Octave and Matlab (PSOM) \cite{slcPSOM} to process both sMRI and R-fMRI datasets.
+The Athena pipeline processed rs-fMRI and s-MRI images using a custom Bash script that combined AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
+The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry style tools.
+The NIAK pipeline processed rs-fMRI and s-MRI using tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011} assembled together into a workflow using the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
 The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
@@
 
-\section{Contents of the repository}
+\section{Organization and access to the repository}
 
@@
 Questions regarding data acquisition or phenotypic variables should be directed to INDI's support forum\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=1735}}.
-\par
+
+\section{Contents of the repository}
+
 ADHD-200 Preprocessed data is available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative.
@@
 
-\begin{table}[!ht]
-\caption{{\bf Summary of ADHD-200 data by site.}}\label{part_tab}
-  \begin{tabular}{L{.1in}L{.1in}L{1.1in}L{1.1in}L{1.1in}L{.7in}}
-    \hline
-	\\
-    \multicolumn{3}{l}{\textbf{Bradley Hostpital/Brown University}} & & \\
-    & \multicolumn{4}{l}{\emph{Scanner:} Siemens TIM Trio 3T}\\
-    & \multicolumn{5}{l}{\emph{sMRI:} 3D MPRAGE, FA = 9$^{\circ}$, TR = 2250 ms, TE = 2.98 ms,}\\
-    & &  \multicolumn{3}{l}{TI = 900 ms, $1\times1\times1$ mm$^3$} \\
-    & \multicolumn{4}{l}{\emph{R-fMRI:} EPI w/ prospective motion correction (PACE), FA = 9$^{\circ}$,}\\
-    & & \multicolumn{4}{l}{TR = 2000 ms, TE = 25 ms, 35 3-mm thick slices, $3.0 \times 3.0$ mm$^2$}\\
-    & & \multicolumn{4}{l}{in-plan resolution. Participants were asked to relax with their eyes}\\
-    & & \multicolumn{4}{l}{open and fixate on the text ``relax'' that was projected on a screen.}\\
-    & \multicolumn{2}{l}{\emph{TDC}:} 27, 
-    %& \multicolumn{4}{l} \emph{T1 weighted anatomical scans:}  
-	\hline
-	\end{tabular}
-\end{table}
-
-\subsection{The Athena and NIAK pipelines}
-
-\paragraph{Preprocessed sMRI and R-fMRI} Both the Athena and NIAK pipelines released denoised R-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz).
+\subsection{Preprocessed s-MRI and rs-fMRI} Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz).
 Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL .xfm transform files for Athena and in .xfm MINC files for NIAK.
@@
 
-\paragraph{Regional time series} Regional time series were extracted based on a series of different brain parcellations.
+\subsection{Regional time series} Regional time series were extracted based on a series of different brain parcellations.
 The Athena ppipeline used functional parcels generated by a spectral clustering method (Craddock et al.
@@
 
-\paragraph{Other derivatives}
-The Athena pipeline derived a number of additional metrics from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on the (Smith et al.
+\subsection{Connectivity maps}
+The Athena pipeline derived a number of brain maps capturing some aspects of RfMRI connectivity, derived from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on the (Smith et al.
 2009) group independent component analysis (ICA) with 10 resting-state networks.
@@
 
-\subsection{The Burner pipeline}
+\subsection{Voxel-based morphometry}
 
@@
 
+\begin{table}[!ht]
+\caption{{\bf ADHD-200 participants by site.} BHBU: Bradley Hospital/ Brown University, KKI: Kennedy Krieger Institute, NI: NeuroIMAGE sample, NYU: New York University Child Study Center, OHSU: Oregon Health Sciences University, PKU: Peking University, Pitt: University of Pittsburgh, WUSTL: Washington University at Saint Louis, avg.: average.
+$^*$Diagnostic labels are current not available for BHBU, they have been listed as TDC in the table, but not included in the totals.}\label{part_table}
+  \begin{tabular}{llrrrr}
+      \hline
+       & & \multicolumn{2}{c}{TDC} & \multicolumn{2}{c}{ADHD}\\
+      Site & Sex & N & Age Range (avg.) & N & Age Range (avg.) \\
+        \hline
+    \noalign{\vskip 1ex}  
+    BHBU & F & 17$^*$ & 8.50 - 17.87 (13.79) 
+             & 0 & - \\
+         & M &  9$^*$ & 12.00 - 17.83 (15.96) 
+             & 0 & - \\
+    KKI  & F & 28 & 8.12 - 12.36 (10.19) 
+             & 10 & 8.10 - 12.99 (9.97) \\
+         & M & 41 & 8.02 - 12.87 (10.35) 
+             & 15 & 8.19 - 12.98 (10.08) \\
+    NI  & F & 25 & 11.66 - 26.31 (18.69) 
+             & 5 & 11.85 - 19.66 (15.07) \\
+         & M & 12 & 12.84 - 25.04 (18.02) 
+             & 31 & 11.05 - 20.89 (17.05) \\
+    NYU  & F & 55 & 7.17 - 17.96 (12.20) 
+             & 34 & 7.35 - 17.15 (10.27) \\
+         & M & 56 & 7.19 - 17.96 (12.20) 
+             & 117 & 7.24 - 17.61 (11.19) \\
+    OHSU  & F & 40 & 7.33 - 12.50 (8.98) 
+             & 13 & 7.42 - 11.33 (9.01) \\
+         & M & 30 & 7.17 - 11.92 (9.48) 
+             & 30 & 7.42 - 11.83 (8.94) \\
+    PKU  & F & 59 & 8.33 - 15.17 (10.90) 
+             & 10 & 8.83 - 15.92 (10.88) \\
+         & M & 84 & 8.08 - 14.92 (11.80)  
+             & 92 & 8.33 - 17.33 (12.22) \\ 
+    Pitt  & F & 44 & 10.16 - 20.45 (15.65) 
+             & 1 & 15.04 \\
+         & M & 50 & 10.11 - 18.96 (14.55)  
+             & 3 & 13.72 - 17.03 (15.55) \\ 
+    WUSTL  & F & 28 & 7.09 - 21.81 (11.33) 
+             & 0 & - \\
+         & M & 33 & 7.25 - 21.83 (11.58)  
+             & 0 & - \\ 
+    \bf{Totals} & F & 279$^*$ & 7.09 - 26.31 (11.9)
+               & 73 & 7.35 - 19.66 (10.48) \\
+           & M & 306$^*$ & 7.17 - 25.04 (12.20)
+               & 288 & 7.24 - 20.89 (11.90) \\
+    \noalign{\vskip 1ex}  
+    \hline
+	\end{tabular}
+\end{table}
+
+\begin{sidewaystable}[!ht]
+\caption{{\bf Structural MRI acquisition parameters by site.} Seq: imaging sequence, FA: flip angle, TE: echo time, TR: repetition time, TI: inversion recovery delay, PA: parallel acquisition, Res: voxel resolution, BHBU: Bradley Hospital/ Brown University, KKI: Kennedy Krieger Institute, NI: NeuroIMAGE sample, NYU: New York University Child Study Center, OHSU: Oregon Health Sciences University, PKU: Peking University, Pitt: University of Pittsburgh, WUSTL: Washington University at Saint Louis, Trio: Siemens TIM Trio 3T, Allegra: Siemens Allegra, Avanto: Siemens Avanto, MPRAGE: magnetization prepared rapid gradient echo, S: sensitivity encoding (SENSE), G: generalized auto-calibrating partially parallel acquisition (GRAPPA)}\label{smri_params_table}
+  \begin{tabular}{lllllllll}
+      \hline
+    Site & Scanner & Seq & FA & TE & TR & TI & PA & Res. \\
+    \hline
+    \noalign{\vskip 1ex}  
+    BHBU & Trio 3T & 3D MPRAGE & 9$^{\circ}$ & 2.98 ms & 2250 ms & 900 ms & None & $1.00\times1.00\times1.00$ mm$^3$ \\
+    KKI & Phillips 3T & 3D MPRAGE & 8$^{\circ}$ & 3.7 ms & 3500 ms & 1000 ms & S $\times$2 & $1.00\times1.00\times1.00$ mm$^3$ \\
+    NI & Avanto 1.5T & 3D MPRAGE & 7$^{\circ}$ & 2.95 ms & 2730 ms & 1000 ms & G $\times$2 & $1.00\times1.00\times1.00$ mm$^3$ \\
+    NYU & Allegra 3T & 3D MPRAGE & 7$^{\circ}$ & 3.25 ms & 2530 ms & 1100 ms & None & $1.30\times1.00\times1.30$ mm$^3$ \\
+    OHSU & Trio 3T & 3D MPRAGE & 10$^{\circ}$ & 3.58 ms & 2300 ms & 900 ms & None & $1.00\times1.00\times1.10$ mm$^3$ \\
+    PKU 1 & Trio 3T & 3D MPRAGE & 7$^{\circ}$ & 3.39 ms & 2530 ms & 1100 ms & None & $1.30\times1.00\times1.30$ mm$^3$ \\
+    PKU 2 & Trio 3T & 3D MPRAGE & 7$^{\circ}$ & 3.45 ms & 2530 ms & 1100 ms & None & $1.00\times1.00\times1.00$ mm$^3$ \\
+    PKU 3 (1) & Trio 3T & 3D MPRAGE & 12$^{\circ}$ & 3.67 ms & 2000 ms & 1100 ms & None & $0.94\times0.94\times1.00$ mm$^3$ \\
+    PKU 3 (2) & Trio 3T & 3D MPRAGE & 10$^{\circ}$ & 2.60 ms & 1950 ms & 900 ms & None & $1.00\times1.00\times1.30$ mm$^3$ \\
+    PKU 3 (3) & Trio 3T & 3D MPRAGE  & 7$^{\circ}$ & 3.37 ms & 2530 ms & 1100 ms & None & $1.00\times1.00\times1.33$ mm$^3$ \\
+    PKU 3 (4) & Trio 3T & 3D MPRAGE & 12$^{\circ}$ & 3.92 ms & 1770 ms & 1100 ms & None & $0.50\times0.50\times1.00$ mm$^3$ \\
+    PKU 3 (5) & Trio 3T & 3D MPRAGE & 8$^{\circ}$ & 2.89 ms & 845 ms & 600 ms & None & $1.02\times1.02\times1.30$ mm$^3$ \\
+    Pitt & Trio 3T & 3D MPRAGE & 8$^{\circ}$ & 3.43 ms & 2100 ms & 1050 ms & None & $1.00\times1.00\times1.00$ mm$^3$ \\
+    WUSTL & Trio 3T & 3D MPRAGE & 8$^{\circ}$ & 3.08 ms & 2400 ms & 1000 ms & G $\times$2 & $1.00\times1.00\times1.00$ mm$^3$ \\
+    \noalign{\vskip 1ex}  
+    \hline
+	\end{tabular}
+\end{sidewaystable}
+
+\begin{sidewaystable}[!ht]
+\caption{{\bf Resting state fMRI acquisition parameters by site.} Seq: imaging sequence, FA: flip angle, TE: echo time, TR: repetition time, PA: parallel acquisition, N$_{slc}$: number of slices, Th.: slice thickness, Slc.
+Acq.: slice acquisition order, N$_{TR}$: number of measurements (TRs),  BHBU: Bradley Hospital/ Brown University, KKI: Kennedy Krieger Institute, NI: NeuroIMAGE sample, NYU: New York University Child Study Center, OHSU: Oregon Health Sciences University, PKU: Peking University, Pitt: University of Pittsburgh, Pitt 2: U.
+Pitt.
+parameters used for acquiring the testing data, WUSTL: Washington University at Saint Louis, EPI: echo planar imaging, PACE: Prospective Acquisition CorrEction (EPI with prospective motion correction), S: sensitivity encoding (SENSE), G: generalized autocalibrating partially parallel acquisition (GRAPPA), int+: slices were acquired interleaved ascending, seq+: slices were acquired sequentially ascending, var.: the number of measurements varies across datasets, fixate: participants were asked to keep their eyes open and fixate on an image, closed: participants were asked to keep their eyes closed, open: participants were asked to keep their eyes open.}\label{smri_params_table}
+  \begin{tabular}{llllllllllll}
+    \hline
+    Site & Seq & FA & TE & TR & PA & N$_{slc}$ & Th. & Slc. Acq. & Resolution & N$_{TR}$ & Instructions  \\ 
+        \hline
+    \noalign{\vskip 1ex} 
+    BHBU & PACE & 90$^{\circ}$ & 25 ms & 2000 ms  & None & 35 & 3 mm & int+ & $3.0 \times 3.0$ mm$^{2}$ & 256 & fixate \\
+    KKI & EPI & 75$^{\circ}$ & 30 ms & 2500 ms  & S $\times3$ & 47 & 3 mm & seq+ & $3.0 \times 3.0$ mm$^{2}$ & 128 & fixate \\
+    NI & EPI & 80$^{\circ}$ & 40 ms & 1960 ms  & G $\times2$ & 37 & 3 mm & int+ & $3.5 \times 3.5$ mm$^{2}$ & 266 & eyes closed \\
+    NYU & EPI & 90$^{\circ}$ & 15 ms & 2000 ms  & None & 33 & 4 mm & int+ & $3.0 \times 3.0$ mm$^{2}$ & 180 & eyes closed \\
+    OHSU & EPI & 90$^{\circ}$ & 30 ms & 2500 ms  & None & 36 & 3.8 mm & int+ & $3.8 \times 3.8$ mm$^{2}$ & 82 & fixate \\
+    PKU 1 & EPI & 90$^{\circ}$ & 30 ms & 2000 ms  & None & 33 & 4.2 mm & int+ & $3.1 \times 3.1$ mm$^{2}$ & 240 & closed or fixate \\
+    PKU 2 & EPI & 90$^{\circ}$ & 30 ms & 2000 ms  & None & 33 & 3.6 mm & int+ & $3.1 \times 3.1$ mm$^{2}$ & 240 & closed or fixate \\
+    PKU 3 & EPI & 90$^{\circ}$ & 30 ms & 2000 ms  & None & 30 & 4.5 mm & int+ & $3.44 \times 3.44$ mm$^{2}$ & 240 & closed or fixate \\
+    Pitt & EPI & 70$^{\circ}$ & 29 ms & 1500 ms  & G $\times2$ & 29 & 4.0 mm & int+ & $3.1 \times 3.1$ mm$^{2}$ & 200 & open or closed \\
+    Pitt 2 & EPI & 90$^{\circ}$ & 30 ms & 3000 ms  & None & 46 & 3.5 mm & int+ & $3.8 \times 3.8$ mm$^{2}$ & 128 & open or closed \\
+    WUSTL & EPI & 90$^{\circ}$ & 27 ms & 2500 ms  & None & 32 & 4.0 mm & int+ & $4.0 \times 4.0$ mm$^{2}$ & var. & fixate \\
+    \noalign{\vskip 1ex} 
+    \hline
+
+	\end{tabular}
+\end{sidewaystable}
+
 \section{Processing strategies}
+Further details on the processing strategies can be found on the ``ADHD200 preprocessed'' website\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:ADHDpreproc}}.
 
-\subsection{Preprocessed sMRI and R-fMRI}
+\subsection{Preprocessed sMRI and rs-fMRI}
 % http://onlinelibrary.wiley.com/doi/10.1002/hbm.22790/epdf
-\paragraph{The Athena pipeline} The preprocessing steps of functional MRI datasets included removal of the first four volumes to allow for magnetization to reach equilibrium, slice timing correction, motion correction, normalization to MNI152 standard space at 4 mm isotropic voxel resolution, regression of nuisance covariates including head motion parameters, global mean, white matter, and cerebrospinal ﬂuid signals, band-pass filtering of fMRI ($0.009 Hz < f < 0.08 Hz$) to reduce low-frequency drift and high-frequency physiological noise, and finally spatial smoothing with a 6 mm full-width-at-half-maximum isotropic Gaussian kernel.
+\paragraph{The Athena pipeline} The preprocessing steps of functional MRI datasets in the Athena pipeline included the following steps.
+(1) Removal of the first four volumes to allow for magnetization to reach equilibrium.
+(2) Slice timing correction.
+(3) Motion correction by means of estimation of a rigid body transform for each time frame.
+(4) Normalization to MNI152 stereotaxic space.
+(5) Resampling at 4 mm isotropic voxel resolution.
+(6) Regression of nuisance covariates including head motion parameters, global mean, white matter, and cerebrospinal ﬂuid signals.
+(7) Band-pass filtering of fMRI ($0.009 Hz < f < 0.08 Hz$) to reduce low-frequency drift and high-frequency physiological noise.
+(8) Spatial smoothing with a 6 mm full-width-at-half-maximum isotropic Gaussian kernel.
 
-\paragraph{The NIAK pipeline} The preprocessing steps followed those of the Athena pipeline with the following differences: (1) only the first three volumes were suppressed, instead of four; (2) only a high-pass filter was implemented ($0.009 Hz < f$), instead of a band pass, and no regression of confounds such as motion parameters, global average, etc.
-Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{Perlbarg2007}.
-The fMRI volumes were resampled in stereotaxic space at 3 mm isotropic (instead of 4 mm), and this was done only right before spatial smoothing.
-Finally note that although both Athena and NIAK used the MNI non-linear stereotaxic template space described in \citep{Fonov2011}, the NIAK used the young adult (ICBM152) symmetric variant, while Athena used the NIHPD asymmetric pediatric template (4.5 y.o.-18.5 y.o.).
+\paragraph{The NIAK pipeline} The preprocessing steps in NIAK followed those of the Athena pipeline with differences at the following steps.
+(1) Only the first three volumes were suppressed, instead of four.
+(4) Although both Athena and NIAK used the MNI non-linear stereotaxic template space described in \citep{fonov2011unbiased}, the NIAK used the young adult (ICBM152) symmetric variant, while Athena used the NIHPD asymmetric pediatric template (4.5 y.o.-18.5 y.o.).
+(5) The fMRI volumes were resampled in stereotaxic space at 3 mm isotropic (instead of 4 mm), and this was done only right before spatial smoothing (step 5 was moved before step 8).
+(6) No regression of confounds was performed.
+Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{perlbarg2007corsica} after temporal filtering (steps 6 and 7 were inverted).
+(7) Only a high-pass filter was implemented ($0.009 Hz < f$), instead of a band pass.
 
 \subsection{Regional time series}
+Table \ref{tab_parcellations} summarizes the characteristics of the parcellations, which were also presented in Figure \ref{fig_parcellations}. 
+\begin{table}[htbp]
+\label{tab_parcellations}
+\caption{Summary of the characteristics of all brain parcellations used in the ADHD200 preprocessed release. All reported size for the parcels are measured in mm$^3$.}
+\begin{tabular}{llrrrrr}
+Name & Type & \# parcels & mean size & std size & min size & max size \\
+\hline
+AAL	    & anatomical &  116 &  16726 & 11896 &  768 & 55552\\
+EZ	    & anatomical &  116 &  15880 & 11059 & 1344 & 52608\\
+HO	    & anatomical &  111 &  14540 & 15342 &   64 & 99200\\
+TT	    & anatomical & 	 97 &  17106 & 16164 &   64 & 70400\\
+CC200   & functional &  190 &  11351 &  2001 & 2880 & 17856\\
+CC400   & functional &  351 &   6144 &  1207 &   64 & 10048\\
+ROI1000 & functional &  954 &   1404 &   366 &   27 & 2781\\
+ROI3000	& functional & 2843	&    471 &   109 &   27 & 1026\\
+\end{tabular}
+\end{table}
 
-For both Athena and NIAK, regional time series were extracted by averaging preprocessed resting-state volumes within different brain regions.
-The Athena pipeline first used a series of anatomical templates:
+% PB - @CC: I found a mismatch between the # of ROIs for AAL, EZ, HO and TT from my own extraction and the NITRC table. Any idea why?
+% I suspect you eliminated small regions (HO, TT and CC400 have regions with only one voxel). But I am deriving the stats from the nifti files 
+% shipped with the release so I also want to be consistent with what people get.
+
+\paragraph{Anatomical parcellations} For both Athena and NIAK, regional time series were extracted by averaging preprocessed resting-state volumes within different brain parcels.
+The Athena pipeline first used a series of parcellations delineated on the basis of anatomical landmarks:
 \begin{itemize}
-\item The automated anatomical labeling (AAL) template \citep{Tzourio-Mazoyer} 
-\item The Eickhoff-Zilles (EZ) [8]
+\item The automated anatomical labeling (AAL) template \citep{tzourio2002automated}, as distributed with the AAL Toolbox. 
+\item The Talairach and Tournoux (TT) parcellation \citep{Lancaster2000automated}. The TT atlas distributed with AFNI was coregistered and warped into template space.
+\item The Eickhoff-Zilles (EZ) parcellation \citep{eickhoff2005new}.
+The EZ atlas was derived from the max-propagation atlas distributed with the SPM Anatomy Toolbox.
+The atlas was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary.
+\item The Harvard-Oxford (HO) parcellation, distributed with FSL, was split into cortical and subcortical probabilistic atlases.
+A 25\% threshold was applied to each of these atlases and they were subsequently bisected into left and right hemispheres at the midline ($x=0$).
+ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical atlas.
+The subcortical and cortical ROIs were combined.
 \end{itemize}
-, , Talairach and Tournoux (TT) [9], and Harvard-Oxford (HO) anatomical atlases.
-In addition,  as well as, 200 (CC200) and 400 (CC400) ROI atlases derived from functionally parcellating the resting state data [10].
-The AAL atlas is distributed with the AAL Toolbox.
-The atlas was fractionated into functional space using nearest-neighbor interpolation.
-The EZ atlas was derived from the max-propagation atlas distributed with the SPM Anatomy Toolbox.
-The atlas was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary and fractionated into functional space using nearest-neighbor interpolation.
-The HO atlas distributed with FSL is split into cortical and subcortical probabilistic atlases.
-A 25\% threshold was applied to each of these atlases and they were subsequently bisected into left and right hemispheres at the midline (x=0).
-ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical atlas.
-The subcortical and cortical ROIs were combined and then fractionated into functional space using nearest-neighbor interpolation.
-The TT atlas distributed with AFNI was coregistered and warped into template space and subsequently fractionated into functional space using nearest neighbor interpolation.
-\par
-Functional parcellation was accomplished using the two-stage spatially-constrained functional procedure described in [10].
-Preprocessed and unfiltered resting state data corresponding to 650 subjects with the cleanest data (as determined by registration quality and applying a max translation < 3mm and max rotation < 3 degrees).
-A grey matter mask was constructed for the subjects by averaging grey matter masks derived from freesurfer automated segmentation.
-Subject specific connectivity graphs were constructed by treating each withen-gm-mask voxel as a node and edges corresponding to super-threshold temporal correlations to the voxels' 3D (27 voxel) neighborhood.
+All the anatomical templates were resampled into the functional space using nearest-neighbor interpolation.
+
+\paragraph{The CC200 and CC400 functional parcellations} Two functional brain parcellations, called CC200 and CC400, were derived from rs-fMRI data using a two-stage spatially-constrained clustering procedure \cite{craddock2012whole}.
+Only a subset ($N=650$) of high-quality preprocessed and unfiltered rs-fMRI data was selected to generate the parcellations, as determined by registration quality and exclusion of subjects with more than 3 mm translation or 3 degrees rotations in their motion parametes.
+A group grey matter mask was constructed by averaging individual grey matter masks derived from freesurfer automated segmentation.
+Subject-specific connectivity graphs were constructed by treating each voxel in the grey matter as a node and edges corresponding to super-threshold temporal correlations to the voxels' 3D (27 voxel) neighborhood.
 Each subjects' graph was partitioned into 200 or 400 regions using normalized cut spectral clustering.
-Association matrices were constructed from the clustering results by setting the connectivity between voxels to 1 if they are in the same ROI and 0 otherwise.
-A group-level correspondance matrix was constructed by averaging the individual level association matrices and subsequently partitioned into 200 or 400 regions using normalized cut clustering.
-\par 
-Regional homogeneity was calculated for the preprocessed and filtered whole brain resting state data using the procedure described in [11].
-The scripts used to calculate ReHo were generously provided by Dr.
-Xinian Zuo.
-\par 
-The FC maps for the Smith PNAS 2009 RSNs were constructed using a modified dual regression approach.
-I used a spatial multiple regression to extract time courses corresponding to spatial templates of the 10 Smith PNAS 2009 RSNs, and then independently correlated each of the 10 time courses with whole brain data to generate subject-specific FC maps for each RSN.
-Dr.
-Steve Smith suggested that instead of using univariate correlation to generate the FC maps, that I use multiple regression instead.
-These files are the result of that analysis.
+Adjacency matrices were constructed from the clustering results by setting the connectivity between voxels to 1 if they are in the same ROI and 0 otherwise.
+A group-level consensus matrix was constructed by averaging the individual level adjacency matrices and subsequently partitioned into 200 or 400 regions using normalized cut clustering.
+% PB: @CC What was the threshold in "super-threshold"? Also how did you measure "registration quality"?
+%I've switched a few terms, to use adjacency and consensus.
+Adjacency is pretty standard, and based on Monti2003 I believe consensus was the first term used for this, and one that is pretty intuitive too.
+% The CC200 and CC400 actually have 190 and 351 ROIs, why?
+% Overall you may want to review closely this paragraph in particular, as I just copied it over from the wiki with few edits.
 
-\subsection{The Burner Pipeline}
-Details on the Burner pipeline can be found on the NITRC website\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NiakPipeline}}.
-T1 images were segmented into grey matter and white matter probability maps using "New Segmentation" in SPM8.
+\paragraph{The ROI1000 and ROI3000 functional parcellations} A region-growing algorithm \citep{bellec2006identification} based on the iterative merging of mutual-nearest-neighbours was implemented to generate functional brain parcellations.
+The spatial dimension was selected arbitrarily by setting the size where the growing process stopped, measured in mm$^3$.
+Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting into roughly 1000 and 3000 ROIs covering the grey matter.
+The regions were built to maximize the average correlation between the time series associated with any pair of voxels of the region.
+The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance) at the KKI site (training data only), such that the homogeneity was maximized on average for all subjects, and the small homogeneous regions were identical for all subjects.
+Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{tzourio2002automated}.
+
+\subsection{Connectivity maps}
+% We are missing the ALFF
+Regional homogeneity (ReHo) was calculated for the preprocessed and filtered whole brain rs-fMRI data using the procedure described in \citep{zang2004regional}.
+The functional connectivity maps for 10 resting-state networks reported by \cite{smith2009correspondence} were constructed using a modified dual regression approach.
+A spatial multiple regression was first used to extract time courses corresponding to each network.
+In a second step, each time course was independently correlated with whole brain time series to generate subject-specific functional connectivity maps for each network.
+Alternatively, all time courses were entered simultaneously into a multiple (temporal) regression, and the regression cofficients associated with each time course constituted the functional connectivity maps.
+Both approaches have been released.
+
+% The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo.
+\subsection{Voxel-based morphometry}
+%Details on the Burner pipeline can be found on the NITRC website\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NiakPipeline}}.
+The T1 images were segmented into grey matter and white matter probability maps using the "New Segmentation" method implemented in SPM8.
 The tissue maps were rigidly aligned (translation+rotation).
 Inter subject normalization was performed using DARTEL toolbox in SPM8.
-Images were iteratively registered to the group average (population template), and template was updated iteratively.
-This resulted finer and finer registration.
-The registration parameters were applied to each image to transform each image into the space of population average.
-Modulation was applied to conserve the global tissue volumes after normalization.
+Images were iteratively registered to the group average (population template), and the template was updated iteratively.
+This iterative process resulted into finer and finer registrations.
+The registration parameters were applied to each image to resample them into the space of the population average.
+A modulation was applied to preserve the global tissue volumes after normalization.
 
-\subsection{The NIAK pipeline}
-Details on the NIAK pipeline can be found on the NITRC website.
+%Details on the NIAK pipeline can be found on the NITRC website.
 
@@
 
-% Add a few words on the generation of the regions and extraction of regional time series. 
-To reduce the computational burden of the analysis, the spatial dimension of the individual fMRI dataset was reduced using a region-growing algorithm.
-The spatial dimension was selected arbitrarily by setting the size where the growing process stopped (a threshold of 1000 mm3 resulted into R=957 regions).
-The regions were built to maximize the homogeneity of the time series within the region, i.e.
-the average correlation between the time series associated with any pair of voxels of the region.
-The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance), such that the homogeneity was maximized on average for all subjects, and the small homogeneous regions are identical for all subjects.
-Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{Tzourio-Mazoyer2002}.
-See (Bellec et al.
-2006) for more details regarding the implementation of the region-growing algorithm.
-Overall, this process reduced the dataset of each subject into a (T x R) data array, where T is the number of time samples and R is the number of regions.
-
 \section{Quality control}
 
-The Athena pipeline did suggest a number of automated metrics to guide quality controls, but left to end users the task of checking individual data.
+Both the Athena and NIAK pipelines generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset.
+For each brain map statistical derivative, the Athena pipeline calculated a $z$-score at each voxel and for each individual, based on the group mean and std.
+This $z$ transform was used to detect outlier values in the images, which could potentially be used by participants to identify problematic datasets.
 The output of the Burner pipeline were visually inspected by Dr Chu.
-The individual results of the NIAK pipeline were visually reviewed for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space.
-The quality control report also included metrics of individual motion and recommendation for subjects to exclude on the basis of excessive motion.
-
-\emph{We need to mention the forum, give examples of the identification of bugs as well as the release of bug fixes (and problems that came with it because of the way we released the data).
-This has to be kept brief, it's not super exciting, but it is part of the guidelines of the special issue.}
+The individual results of the NIAK pipeline were visually reviewed by M.
+Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space.
 
@@
 
-The ADHD200 preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD200 competition, with over 9,500 downloads by more than 490 users.
-In the short time since their release, these statistical derivatives have already been used to generate 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012,     DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012} and three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} in just over 3 years, with more in press or under review.
+The ADHD200 preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD200 competition, with over 9,500 downloads by more than 490 users, as well as tens of publication derived from the release.
 An important feature of the ADHD200 preprocessed initiative was that the regional time series took the form of time x space arrays easy to manipulate for any data scientist, even without a background in imaging.
-As a result, the publications using ADHD200 preprocessed include articles published in journals outside of the the neuroimaging field, e.g.
+As a result, some of the publications that have used ADHD200 preprocessed were published in journals outside of the the neuroimaging field, e.g.
 \citep{}.
@@
 \par 
-In terms of its secondary objective, almost all variants of processing strategies included in the ADHD200 release have been used in subsequent analysis, although with markedly different rates of re-use.
-The most popular pipeline by far has been Athena.
-\emph{...
-we need a specific breackdown for this ...
-I'll prepare a table}.
-No publication we are aware of actually implemented a face-to-face comparison between processing techniques.
-The higher re-use rate of the Athena pipeline compared to the NIAK may be due to the fact that it was released earlier, had the most comprehensive catalogue of derivatives and also used tools more popular in the fMRI community (FSL, AFNI) than NIAK (MINC).
-The Burner pipeline only generated derivatives of the structural data, which did not align well with the positioning of the ADHD200 competition.
-It should be noted that, with the approach we took, any direct comparison between Athena and NIAK was challenging, as the two pipelines did not use the same specific stereotaxic space, varied in every possible way in terms of selected parameters, and also had quite different approaches for QC or derivatives.
-There is no plan to expand or update the ADHD200 release as such, which we hope will continue to serve as a benchmark dataset.
-To the best of our knowledge, the ADHD200 preprocessed release was the first large public resource of preprocessed resting-state fMRI data, and remains to this date the only resource featuring a battery of alternative processing paths.
+Our conclusions are more mitigated regarding the secondary objective of ADHD200, which was to cater to multiple data processing philosophies.
+It wass a success in the sense that almost all variants of processing strategies included in the ADHD200 release have been used in follow-up published manuscripts.
+However, no publication we are aware of actually implemented a face-to-face comparison between processing techniques.
+With the approach we took, any direct comparison between Athena and NIAK was difficult to interpret, as the two pipelines did not use the same specific stereotaxic space, varied in many ways in terms of selected parameters, and also had quite different approaches for QC, derivatives or even packaging the derivatives.
+This lack of harmonization was essentially driven by the tight deadline for data release imposed by the competition, rather than a design choice.
+We also came to the conclusion that it would be useful to build the processing pipelines on a common stereotaxic space and possibly sets of registration, so that the strategies of noise reduction can be more readily compared.
 \par 
-The success of the ADHD200 preprocessed experiment illustrates the need for large-scale efforts to reduce computational barriers to participation in discovery neuroscience.
+The success of the ADHD200 preprocessed experiment still emphasized the need to reduce computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions using neuroimaging data.
 This need is further emphasized by a recent survey of FCP/INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
-Unfortunately, the Neuro Bureau’s efforts have been limited to a fraction of the datasets that are available through FCP and INDI due to funding and manpower limitations, and represent only a fraction of the statistical derivatives that can be derived from the data.
-A much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data to accelerate neuroimaging research.
-We are now working on new initiatives learning from the ADHD200 experiment, notably including better harmonized processing and quality control strategies.
-This could critically help fMRI researchers to identify optimal analytical paths for a specific task.
+We do not plan to expand or update the ADHD200 release as such, which we hope will continue to serve as a legacy benchmark dataset.
+We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data to accelerate neuroimaging research.
+We are now working on new initiatives learning from the ADHD200 preprocessed experiment, notably including better harmonized processing, quality control and data packaging strategies.
+Our hope is that ADHD200 preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.
 

### 2015-12-21 Bellec_ADHD200_2016_backup.tex
Re-organized derivatives and pipelines. Added substantial detail to describtions of Athena and Burner pipelines.

--- 2015-12-19 Bellec_ADHD200_2016.tex
@@
 % \linenumbers
-\section{Highlights}
+\section*{Highlights}
 \begin{itemize}
@@
 Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels for test data for which diagnostic information was withheld.
-The competition data was distributed in a raw form and before any analysis could begin, had to be preprocessed to make it comparable across individuals and to remove nuisance variation that would obscure the underlying biological signal.
-These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to the high performance computing resources required to process such a large data collection in a short amount of time.
-This category includes statisticians and computer scientists, who were potentially the most qualified for the machine learning aspect of the competition.
+The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise.
+These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to high performance computing resources.
 Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.
@@
 The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry style tools.
-The NIAK pipeline processed rs-fMRI and s-MRI using tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011} assembled together into a workflow using the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
-The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
+The NIAK pipeline processed rs-fMRI and s-MRI using a workflow composed of tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011}, which were assembled with the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
+
+% PB -> CC: the following information is redundant with the rest of the paper. It's also not introductory material. As the paper is short, I would tend to avoid repetition.
+
+%The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
 The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians with limited prior neuroimaging experience \cite{Eloyan2012}.
@@
 
-The ADHD-200 preprocessed data was released in the summer of 2012 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
+The ADHD-200 preprocessed data was released in 2011 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
 No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account.
-This registration enables downloads to be tracked for usage statistics and so that users can be contacted in the event that errors are found.
+This registration enables downloads to be tracked for usage statistics.
+Registered users can also be contacted in the event that errors would be found.
 The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/adhd200/}}.
@@
 
-ADHD-200 Preprocessed data is available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative.
-The following preprocessed derivatives are available.
+The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis see table \ref{part_table}).
+For each individual, phenotypic data includes sex, age, handedness, ADHD diagnosis (585 TDC, 362 ADHD, 26 unknown), ADHD subtype (ADHD-combined, ADHD-inattentive, ADHD-hyperactive/impulsive), one of three different measures of ADHD severity, one of five measures of intelligence, co-morbid diagnoses, and whether or not they have used medication to treat their symptoms \cite{Milham2012}.
+Imaging data for each individual includes one or more T1-weighted high-resolution s-MRI scan (s-MRI) and one or more rs-fMRI scan.
+Most of the data was collected from a single imaging session, although a second session is available for 15 individuals from the WUSTL site.
+There is a substantial amount of variation in how the data was collected across sites including the type of MRI system and scanning parameters used, the length of the rs-fMRI scans, and the instructions given to the participants prior to the scan (see tables \ref{smri_params_table} and \ref{rsfmri_params_table}).
+
+Nearly all of the imaging data from the ADHD-200 Sample was included in the preprocessing effort, some individuals were excluded for poor quality or missing data.
+The results of the preprocessing are made available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative.
+A group level file containing this phenotypic data is available in comma-separated-values format (.csv).
+
+% PB->CC I did the breakdown by derivatives, not by pipeline.
+Otherwise there is too much repetition between NIAK and Athena.
+This is true for content description but even more for the methods section, where it's nice for example to have the different approaches for generating parcellations under one section, rather than disjointed into two "Athena" and "NIAK" sections.
+I've also left the details of the methods (e.g.
+resolution for resampling) to the methods section.
+
+% I understand, but I am not sure that the repetition is bad.
+From my understanding, since this is essentially a data paper, we need to be very explicit about what data is available.
+the way it was before missed alot of useful details, i haven't removed your original content yet, just experimenting with an alternative approach.
+I would actually prefer it if we could put it into a table, but since what is available varies so much by pipeline, it would be a very lopsided table.
+Also, since most of the derivatives are pipeline specific, you are essentially breaking them down by derivatives.
+I think it would be better if the processing and 'contents' sections were merged.
+
+\subsection{Athena Pipeline} Data from the Athena pipeline includes processed structural data and processed functional data along with extracted features and statistical derivatives.
+For the structural data the repository contains the skull-stripped whole brain images, along with spatially smoothed and unsmoothed grey matter density maps, written into template space as compressed 3D nifti files (nii.gz).
+The transformation from native space to the template is provided as a FSL fNIRT warp file (nii.gz).
+For the functional data, the repository contains denoised rs-fMRI volumes, processed with and without temporal bandpass filtering, written into template space at 4 $\times$ 4 $\times$ 4 mm$^3$ resolution and spatially smoothed with a 6-mm FWHM Gaussian filter (compressed 4D nifti, nii.gz).
+Ancillary files including the mean rs-fMRI image and masks that differentiate brain data from background in template space (nii.gz), and six parameter head motion traces (tab separated value, AFNI .1D files).
+Regional time series extracted using four different anatomical atlases\cite{tzourio2002automated, lancaster2000automated, eickhoff2005new, HO_atlas_1, HO_atlas_2, HO_atlas_3, HO_atlas_4}, two atlases derived by clustering the functional data \cite{craddock2012whole}, and 10 highly reproducible intrinsic connectivity networks (ICNs) \cite{smith2009correspondence}  are available in tab separated value files (AFNI .1D).
+Derivatives include fractional amplitude of low frequency fluctuations (fALFF) \cite{zuo2008falff},  spatial maps for the 10 ICNs calculated from the non-bandpass-filtered data, and regional homogeneity (ReHo) \cite{zang2004regional} maps calculated from the bandpass-filtered data.
+The derivatives are available in template space at 4 $\times$ 4 $\times$ 4 mm$^3$ resolution and smoothed with a 6-mm FWHM Gaussian filter as compressed 3D (fALFF, ReHo) or 4D nifti (ICNs) files (.nii.gz).
 
 \subsection{Preprocessed s-MRI and rs-fMRI} Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz).
-Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL .xfm transform files for Athena and in .xfm MINC files for NIAK.
-In addition, the estimated motion parameters (bundled with additional intermediate outputs) were released in separate archives, inside text files (AFNI .1D tab-separated-value files) for Athena, and inside Matlab HDF5 files for NIAK.
+Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL wrap .nii.gz file for Athena and in .xfm/.mnc MINC wrap files for NIAK.
+In addition, ancillary files such as the estimated rigid-body motion parameters (AFNI .1D tab-separated-value for Athena, and HDF5 files .mat files for NIAK), mean functional image (.nii.gz files) as well as individual and group brain masks (.nii.gz files) were released in separate archives.
 
 \subsection{Regional time series} Regional time series were extracted based on a series of different brain parcellations.
-The Athena ppipeline used functional parcels generated by a spectral clustering method (Craddock et al.
-2012) as well as a number of parcellations established from anatomical landmarks, with a resolution ranging from 93 to 351 parcels.
-The NIAK pipeline only used functional parcels generated by a region growing method (Bellec et al.
-2006) with two resolutions: 954 and 2843 parcels.
+The Athena ppipeline used functional parcels generated by a spectral clustering method \cite{craddock2012whole} as well as a number of parcellations established from anatomical landmarks, with a resolution ranging from 93 to 351 parcels.
+The NIAK pipeline only used functional parcels generated by a region growing method \cite{bellec2006identification} with two resolutions: 954 and 2843 parcels.
 The Athena pipeline distributed regional time series as text files (.1D AFNI) and the NIAK distributed them as HDF5 files (.mat Matlab).
@@
 
-\subsection{Connectivity maps}
-The Athena pipeline derived a number of brain maps capturing some aspects of RfMRI connectivity, derived from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on the (Smith et al.
-2009) group independent component analysis (ICA) with 10 resting-state networks.
-One compressed nifti file (.nii.gz) was released per fMRI dataset and type of derivative, with in addition the time courses of the dual regression available in text files (.1D AFNI).
+\subsection{Brain maps}
+The Athena pipeline derived a number of brain maps derived from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on a group independent component analysis (ICA) with 10 resting-state networks \citep{smith2009correspondence}.
+One compressed nifti file (.nii.gz) was released per fMRI dataset and type of brain map, with in addition the time courses of the dual regression available in text files (.1D AFNI).
 
@@
 Pitt.
-parameters used for acquiring the testing data, WUSTL: Washington University at Saint Louis, EPI: echo planar imaging, PACE: Prospective Acquisition CorrEction (EPI with prospective motion correction), S: sensitivity encoding (SENSE), G: generalized autocalibrating partially parallel acquisition (GRAPPA), int+: slices were acquired interleaved ascending, seq+: slices were acquired sequentially ascending, var.: the number of measurements varies across datasets, fixate: participants were asked to keep their eyes open and fixate on an image, closed: participants were asked to keep their eyes closed, open: participants were asked to keep their eyes open.}\label{smri_params_table}
+parameters used for acquiring the testing data, WUSTL: Washington University at Saint Louis, EPI: echo planar imaging, PACE: Prospective Acquisition CorrEction (EPI with prospective motion correction), S: sensitivity encoding (SENSE), G: generalized autocalibrating partially parallel acquisition (GRAPPA), int+: slices were acquired interleaved ascending, seq+: slices were acquired sequentially ascending, var.: the number of measurements varies across datasets, fixate: participants were asked to keep their eyes open and fixate on an image, closed: participants were asked to keep their eyes closed, open: participants were asked to keep their eyes open.}\label{rsfmri_params_table}
   \begin{tabular}{llllllllllll}
@@
 (6) Regression of nuisance covariates including head motion parameters, global mean, white matter, and cerebrospinal ﬂuid signals.
-(7) Band-pass filtering of fMRI ($0.009 Hz < f < 0.08 Hz$) to reduce low-frequency drift and high-frequency physiological noise.
+(7) Band-pass filtering of fMRI ($0.009$ Hz $< f < 0.08$ Hz) to reduce low-frequency drift and high-frequency physiological noise.
 (8) Spatial smoothing with a 6 mm full-width-at-half-maximum isotropic Gaussian kernel.
@@
 Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{perlbarg2007corsica} after temporal filtering (steps 6 and 7 were inverted).
-(7) Only a high-pass filter was implemented ($0.009 Hz < f$), instead of a band pass.
+(7) Only a high-pass filter was implemented ($0.01$ Hz $< f$), instead of a band pass.
 
@@
 \item The automated anatomical labeling (AAL) template \citep{tzourio2002automated}, as distributed with the AAL Toolbox. 
-\item The Talairach and Tournoux (TT) parcellation \citep{Lancaster2000automated}. The TT atlas distributed with AFNI was coregistered and warped into template space.
 \item The Eickhoff-Zilles (EZ) parcellation \citep{eickhoff2005new}.
@@
 The subcortical and cortical ROIs were combined.
+\item The Talairach and Tournoux (TT) parcellation \citep{Lancaster2000automated}. The TT atlas distributed with AFNI was coregistered and warped into template space.
 \end{itemize}
@@
 
-\subsection{Connectivity maps}
+\subsection{Brain maps}
 % We are missing the ALFF
@@
 The T1 images were segmented into grey matter and white matter probability maps using the "New Segmentation" method implemented in SPM8.
-The tissue maps were rigidly aligned (translation+rotation).
-Inter subject normalization was performed using DARTEL toolbox in SPM8.
+The tissue maps were rigidly aligned (translation and rotation).
+Inter subject normalization was performed using the DARTEL toolbox in SPM8.
 Images were iteratively registered to the group average (population template), and the template was updated iteratively.
-This iterative process resulted into finer and finer registrations.
 The registration parameters were applied to each image to resample them into the space of the population average.
@@
 Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space.
+The conclusions of the NIAK quality control procedure are available on NITRC\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
 
@@
 
-The ADHD200 preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD200 competition, with over 9,500 downloads by more than 490 users, as well as tens of publication derived from the release.
-An important feature of the ADHD200 preprocessed initiative was that the regional time series took the form of time x space arrays easy to manipulate for any data scientist, even without a background in imaging.
-As a result, some of the publications that have used ADHD200 preprocessed were published in journals outside of the the neuroimaging field, e.g.
-\citep{}.
-In particular, the winning team of the ADHD200 global competition was based at the Johns Hopkins Biostatistics Department and used ADHD200 preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
+The ADHD200 preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD200 competition, with over 10,500 downloads by more than 600 users, as well as 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over 3 years, with more in press or under review.
+The resource was also used outside of the neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
+In particular, the winning team of the ADHD200 global competition was based at the Johns Hopkins Biostatistics Department and used ADHD200
+% i don't think that we can conclude that the availability of the time series was the driving factor behind the pubs by non-neuroimagers
+% PB->CC OK so I quickly checked some of these references, and they are definitely using a variety of derivatives. OK. 
+% Just a note is She2014.
+In this paper if you blink you will miss the fMRI section.
+It's 10 lines long, in an otherwise highly theoretical paper, and the other application (also 10 lines) is about yeast gene regulation network.
+I think this is awesome, and possible because you can grab time series without having any clue what they represent and run with it.
+But I am extrapolating too much from this example.
+preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
 \par 
-Our conclusions are more mitigated regarding the secondary objective of ADHD200, which was to cater to multiple data processing philosophies.
-It wass a success in the sense that almost all variants of processing strategies included in the ADHD200 release have been used in follow-up published manuscripts.
+Our conclusions are more mitigated regarding the secondary objective of ``ADHD200 preprocessed'', which was to cater to multiple data processing philosophies.
+The release was a success in the sense that almost all variants of processing strategies included in the ADHD200 release have been used in follow-up published manuscripts.
 However, no publication we are aware of actually implemented a face-to-face comparison between processing techniques.
@@
 This lack of harmonization was essentially driven by the tight deadline for data release imposed by the competition, rather than a design choice.
-We also came to the conclusion that it would be useful to build the processing pipelines on a common stereotaxic space and possibly sets of registration, so that the strategies of noise reduction can be more readily compared.
+We since came to the conclusion that it would be useful to build the processing pipelines on a common stereotaxic space and possibly sets of registration, so that the strategies of noise reduction can be more readily compared.
 \par 
-The success of the ADHD200 preprocessed experiment still emphasized the need to reduce computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions using neuroimaging data.
+The impact of the ``ADHD200 preprocessed'' repository emphasized the need to reduce computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
 This need is further emphasized by a recent survey of FCP/INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
@@
 We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data to accelerate neuroimaging research.
-We are now working on new initiatives learning from the ADHD200 preprocessed experiment, notably including better harmonized processing, quality control and data packaging strategies.
+We are now working on new initiatives learning from the ADHD200 preprocessed experiment, notably including a larger number of alternative analytical workflows as well as a careful harmonization of processing, quality control and data packaging strategies.
 Our hope is that ADHD200 preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.

### 2015-12-21 Bellec_ADHD200_2016.tex
added figure 1

@@
+% Relevant Links:
+% http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline
+% http://neurovault.org/collections/1025/
+
 %%
@@
 \newcolumntype{R}[1]{>{\raggedleft\let\newline\\arraybackslash\hspace{0pt}}p{#1}}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated.
-The Athena pipeline processed rs-fMRI and s-MRI images using a custom Bash script that combined AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
+The Athena pipeline processed rs-fMRI and s-MRI images using a combination of AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
 The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry style tools.
-The NIAK pipeline processed rs-fMRI and s-MRI using tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011} assembled together into a workflow using the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
-The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
+The NIAK pipeline processed rs-fMRI and s-MRI using a workflow composed of tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011}, which were assembled with the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
+
+% PB -> CC: the following information is redundant with the rest of the paper. It's also not introductory material. As the paper is short, I would tend to avoid repetition.
+
+%The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
 The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians with limited prior neuroimaging experience \cite{Eloyan2012}.
@@
 
-ADHD-200 Preprocessed data is available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative.
-The following preprocessed derivatives are available.
+The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis see table \ref{part_table}).
+For each individual, phenotypic data includes sex, age, handedness, ADHD diagnosis (585 TDC, 362 ADHD, 26 unknown), ADHD subtype (ADHD-combined, ADHD-inattentive, ADHD-hyperactive/impulsive), one of three different measures of ADHD severity, one of five measures of intelligence, co-morbid diagnoses, and whether or not they have used medication to treat their symptoms \cite{Milham2012}.
+Imaging data for each individual includes one or more T1-weighted high-resolution s-MRI scan (s-MRI) and one or more rs-fMRI scan.
+Most of the data was collected from a single imaging session, although a second session is available for 15 individuals from the WUSTL site.
+There is a substantial amount of variation in how the data was collected across sites including the type of MRI system and scanning parameters used, the length of the rs-fMRI scans, and the instructions given to the participants prior to the scan (see tables \ref{smri_params_table} and \ref{rsfmri_params_table}).
 
-\subsection{Preprocessed s-MRI and rs-fMRI} Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz).
-Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL .xfm transform files for Athena and in .xfm MINC files for NIAK.
-In addition, the estimated motion parameters (bundled with additional intermediate outputs) were released in separate archives, inside text files (AFNI .1D tab-separated-value files) for Athena, and inside Matlab HDF5 files for NIAK.
+Nearly all of the imaging data from the ADHD-200 Sample was included in the preprocessing effort, some individuals were excluded for poor quality or missing data.
+The results of the preprocessing are made available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative.
+A group level file containing the phenotypic data is available in comma-separated-values format (.csv).
+
+Shared preprocessed data and extracted features include:
+\begin{itemize}
+\tightlist
+\item 3D grey matter density maps suitable for voxel-based morphometry as compressed nifti - Athena, Burner and NIAK
+\item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment (Athena and NIAK)
+\item Average time courses for brain regions from structurally defined atlases (Athena)
+\item Average time courses for brain regions for regions defined by functional parcellation (Athena and NIAK)
+\item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) - Athena
+\end{enumerate}
+
+% PB->CC I did the breakdown by derivatives, not by pipeline.
+Otherwise there is too much repetition between NIAK and Athena.
+This is true for content description but even more for the methods section, where it's nice for example to have the different approaches for generating parcellations under one section, rather than disjointed into two "Athena" and "NIAK" sections.
+I've also left the details of the methods (e.g.
+resolution for resampling) to the methods section.
+
+% I understand, but I am not sure that the repetition is bad.
+From my understanding, since this is essentially a data paper, we need to be very explicit about what data is available.
+the way it was before missed alot of useful details, i haven't removed your original content yet, just experimenting with an alternative approach.
+I would actually prefer it if we could put it into a table, but since what is available varies so much by pipeline, it would be a very lopsided table.
+Also, since most of the derivatives are pipeline specific, you are essentially breaking them down by derivatives.
+I think it would be better if the processing and 'contents' sections were merged.
+
+\subsection{Athena Pipeline} 
+The Athena pipeline\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline}}  processed rs-fMRI and s-MRI images using a custom BASH script that combined AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
+The processing scripts for each site are distributed in the repository, along with output log files for each processed dataset.
+
+\subsubsection{Structural processing} Athena's s-MRI pipeline began with skull-stripping the images to remove non-brain tissue and background from the images \cite{smith2002_bet} and segmenting the results into white matter (WM), cerebro-spinal fluid (CSF), and grey matter (GM) probability maps \cite{zhang2001_fast}.
+A non-linear warp was calculated between the skull-off image and MNI space as represented by the NIHPD 4.5\textendash18.5y age-specific assymmetric template \cite{fonov2011unbiased} using a two step procedure that calculates a linear transform \cite{jenkinson2002_flirt} that is subsequently refined by a non-linear registration procedure \cite{andersson2007non}.
+\emph{Shared s-MRI outputs include:} skull stripped whole brain images and smoothed (by a 6-mm FWHM Gaussian) and unsmoothed GM density maps in MNI space at 1$\times$1$\times$1 mm$^3$ resolution, along with the FSL fNIRT non-linear warp, as compressed nifti files (.nii.gz).
+
+\subsubsection{Functional processing} Athena's rs-fMRI pipeline involved removing the first four volumes to allow for magnetization to reach equilibrium, site-specific slice timing correction to the middle slice, re-aligning each volume to the first volume to correct for motion \cite{cox1999_motion}, and calculating a linear transform between the mean functional volume and the corresponding s-MRI \cite{jenkinson2002_flirt}.
+The rs-fMRI to s-MRI transform was then combined with the s-MRI to MNI non-linear warp to write the functional into MNI152 space at $4\times4\times4$ mm$^3$ resolution.
+Mean WM and CSF signals extracted using the masks calculated during s-MRI processing were included along with 6 head motion parameters and a third-order polynomial in voxel-wise nuisance regression models to remove variation due to physiological noise, head motion and scanner drifts from the time series\cite{lund2006_nvr,fox2005}.
+The resulting de-noised time series were band-pass filtered ($0.009$ Hz $< f < 0.08$ Hz) to limit the data to the frequencies implicated in resting state functional connectivity \cite{biswal1995,cordes2001} and then spatially smoothed with a 6-mm FWHM Gaussian filter.
+\emph{Shared rs-fMRI outputs include:} denoised rs-fMRI volumes, with and without temporal bandpass filtering, in MNI space (compressed 4D niftis, nii.gz), the mean rs-fMRI image and brain mask in template space (nii.gz), and six parameter head motion traces (tab separated value, AFNI .1D files).
+
+\paragraph{Time series for structurally defined brain areas} Regional time series were extracted for the automated anatomical labeling (AAL) \cite{tzourio2002automated}, Eickhoff-Zilles (EZ) \cite{eickhoff2005new}, Harvard-Oxford (HO) \cite{HO_atlas_1, HO_atlas_2, HO_atlas_3, HO_atlas_4}, and Talairach and Tournoux (TT) \cite{lancaster2000automated} parcellations.
+The EZ atlas was derived from the max-propagation atlas distributed with the SPM Anatomy Toolbox\footnote{\url{http://www.fz-juelich.de/inm/inm-1/EN/Forschung/_docs/SPMAnatomyToolbox/SPMAnatomyToolbox_node.html}} and was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary.
+The HO atlas was constructed from 25\% thresholded cortical and subcortical max-propagation atlases distributed with FSL.
+The atlases were bisected into left and right hemispheres at the midline ($x=0$), ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical atlas and then the subcortical and cortical ROIs were combined into a single atlas.
+The AAL atlas distributed with the SPM8 version of the AAL Toolbox\footnote{\url{http://www.cyceron.fr/index.php/en/plateforme-en/freeware}} and the TT atlas distributed with AFNI were coregistered and warped into template space.
+Each of the anatomical templates were resampled into the functional space using nearest-neighbor interpolation.
+Time series were extracted for each atlas from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
+Each of the conformed ROI atlases are available as compressed 3D nifti files (.nii.gz).
+
+\paragraph{Time series for functionally defined regions} The CC200 and CC400 functional brain parcellations were constructed using a two-stage spatially-constrained spectral clustering procedure \cite{craddock2012whole} applied to unfiltered preprocessed rs-fMRI data from a subset ($N=650$) of the participants in the training dataset.
+Participants were chose for inclusion based on registration quality and after exclusion of participants with more than 3 mm translation or 3 degrees rotations in their motion parameters.
+To reduce computation time, the clustering was restricted to grey matter using a group GM mask that was constructed by averaging individual GM masks derived from freesurfer automated segmentation.
+Although 200 and 400 ROIs were specified in the functional parcellation procedure, the normalized cut algorithm resulted in 190 and 351 clusters respectfully.
+Time series were extracted for each atlas from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
+CC200 and CC400 brain parcellations are available as compressed 3D nifti files (.nii.gz).
+
+\paragraph{ICN time series and spatial maps} Time series and spatial maps were derived for 10 ICNs that have been found to be consistent across resting state and a variety of neuroimaging tasks  \cite{smith2009correspondence} by applying a modified dual regression approach \cite{Beckmann2009dualreg} to the unfiltered preprocessed data.
+A spatial multiple regression was first used to extract time courses corresponding to each network.
+In a second step, each time course was independently correlated with whole brain time series to generate subject-specific functional connectivity maps for each network.
+Alternatively, all time courses were entered simultaneously into a multiple (temporal) regression, and the regression cofficients associated with each time course constituted the functional connectivity maps.
+The resulting ICN time series are distributed as tab-separated values (AFNI .1D) files and the spatial maps for both temporal regression approaches are distributed as compressed 4D NIFTI files (.nii.gz).
+
+\paragraph{fALFF and ReHo} Whole brain fALFF maps were generated by dividing the variance of each voxel's bandpass-filtered time series by the variance of its unfiltered time series \cite{zuo2008falff}.
+ReHo was estimated from the unfiltered data at each voxel by the Kendall's Coefficient of Concordance \cite{kendall1939w} between the voxel and its 26 face-, edge-, and corner- touching neighbors.
+The resulting fALFF and ReHo whole brain maps are distributed as compressed 3D NIFTI files (.nii.gz).
+
+\subsubsection{Quality Assessment}
+
+No specific quality control was applied to Athena data before release, this was left out to accommodate different opinions on what qualifies as good data.
+In addition to files containing the six motion parameters for each rs-fMRI dataset, and anatomical and mean EPI images in template space, which can be visually inspected to determine high motion data or poor registrations, quality metrics derived from structural data, GM masks, mean EPI images, fALFF maps and FC maps were included to help with the QC process.
+For each data type a mean and standard deviation image is calculated from all of the scans from all of the subjects.
+These images are used to perform a voxel-wise z-score transformation on each data type for each subject $z_i = \frac{(v_i-m_i)}{\sigma_i}$.
+The absolute values of these z-scores are then thresholded at 3, and then summed across voxels for a quality score for that image.
+The higher the resulting sum, the larger the number of voxels a image has that are $\geq 3$ and the more likely the images are outliers.
+Using this metric it is possible to rank images, and allows a more directed search for poor quality scans.
+These metrics are distributed in participant specific text files along with the BASH scripts that implement the procedure.
+
+\subsection{Burner Pipeline}
+
+The Burner pipeline\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:BurnerPipeline}} used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry \cite{ashburner2000vbm} style analyses.
+
+\subsubsection{Structural processing}
+
+Processing begins by segmenting s-MRI images into GM and WM probability maps using SPM8's unified segmentation procedure, which iteratively registers the data to a template and performs tissue classification until both are optimized \cite{ashburner2005unified}.
+Next, SPM8's DARTEL toolbox \cite{ashburner2007dartel} was used to generate a template from the s-MRI data of all participants using another iterative method based on that calculates the nonlinear transforms for warping all participant WM and GM maps to a common space.
+The resulting non-linear deformations were applied to each participants GM probability maps to transform them into the space of population average at 1.5 $\times$ 1.5 $\times$ 1.5 mm$^3$ resolution and modulated to conserve the global tissue volumes after normalization.
+The resulting grey matter density maps are distributed at 3D NIFTI files (.nii).
+
+\subsubsection{Quality Assessment}
+Stringent quality control was not applied to the data to accommodate different opinions on what constitutes poor quality data.
+Images for four participants were excluded after visual inspection by Dr.
+Chiu because they were determined to be too poor quality to be processed.
+
+\subsection{NIAK Pipeline}
+
+Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz).
+Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL wrap .nii.gz file for Athena and in .xfm/.mnc MINC wrap files for NIAK.
+In addition, ancillary files such as the estimated rigid-body motion parameters (AFNI .1D tab-separated-value for Athena, and HDF5 files .mat files for NIAK), mean functional image (.nii.gz files) as well as individual and group brain masks (.nii.gz files) were released in separate archives.
 
 \subsection{Regional time series} Regional time series were extracted based on a series of different brain parcellations.
-The Athena ppipeline used functional parcels generated by a spectral clustering method (Craddock et al.
-2012) as well as a number of parcellations established from anatomical landmarks, with a resolution ranging from 93 to 351 parcels.
-The NIAK pipeline only used functional parcels generated by a region growing method (Bellec et al.
-2006) with two resolutions: 954 and 2843 parcels.
-The Athena pipeline distributed regional time series as text files (.1D AFNI) and the NIAK distributed them as HDF5 files (.mat Matlab).
+The NIAK pipeline only used functional parcels generated by a region growing method \cite{bellec2006identification} with two resolutions: 954 and 2843 parcels.
+The  NIAK distributed them as HDF5 files (.mat Matlab).
 All brain parcellations were also released as compressed nifti files (.nii.gz).
-Note that the phenotypic information of the ADHD200 sample was also released as comma-separated-values files (.csv).
 
-\subsection{Connectivity maps}
-The Athena pipeline derived a number of brain maps capturing some aspects of RfMRI connectivity, derived from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on the (Smith et al.
-2009) group independent component analysis (ICA) with 10 resting-state networks.
-One compressed nifti file (.nii.gz) was released per fMRI dataset and type of derivative, with in addition the time courses of the dual regression available in text files (.1D AFNI).
-
-\subsection{Voxel-based morphometry}
-
-The Burner pipeline included a segmentation of the grey matter of the structural scans, after a non-linear transformation in stereotaxic space was generated by the DARTEL tool from SPM8.
-Note that this release was purely based on structural MRI, and did not include any fMRI derivatives.
-This pipeline was specifically oriented towards a voxel-based-morphometry analysis of the ADHD200 sample, which could be used as a complement of the functional analysis perfomed with the two other pipelines.
+\subsection{Brain maps}
+The Athena pipeline derived a number of brain maps derived from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on a group independent component analysis (ICA) with 10 resting-state networks \citep{smith2009correspondence}.
+One compressed nifti file (.nii.gz) was released per fMRI dataset and type of brain map, with in addition the time courses of the dual regression available in text files (.1D AFNI).
 
@@
     \noalign{\vskip 1ex}  
-    BHBU & F & 17$^*$ & 8.50 - 17.87 (13.79) 
+    BHBU & F & 17$^*$ & 8 - 18 (13.8) 
              & 0 & - \\
@@
 \subsection{Preprocessed sMRI and rs-fMRI}
-% http://onlinelibrary.wiley.com/doi/10.1002/hbm.22790/epdf
-\paragraph{The Athena pipeline} The preprocessing steps of functional MRI datasets in the Athena pipeline included the following steps.
-(1) Removal of the first four volumes to allow for magnetization to reach equilibrium.
-(2) Slice timing correction.
-(3) Motion correction by means of estimation of a rigid body transform for each time frame.
-(4) Normalization to MNI152 stereotaxic space.
-(5) Resampling at 4 mm isotropic voxel resolution.
-(6) Regression of nuisance covariates including head motion parameters, global mean, white matter, and cerebrospinal ﬂuid signals.
-(7) Band-pass filtering of fMRI ($0.009 Hz < f < 0.08 Hz$) to reduce low-frequency drift and high-frequency physiological noise.
-(8) Spatial smoothing with a 6 mm full-width-at-half-maximum isotropic Gaussian kernel.
 
@@
 The Athena pipeline first used a series of parcellations delineated on the basis of anatomical landmarks:
-\begin{itemize}
-\item The automated anatomical labeling (AAL) template \citep{tzourio2002automated}, as distributed with the AAL Toolbox. 
-\item The Talairach and Tournoux (TT) parcellation \citep{Lancaster2000automated}. The TT atlas distributed with AFNI was coregistered and warped into template space.
-\item The Eickhoff-Zilles (EZ) parcellation \citep{eickhoff2005new}.
-The EZ atlas was derived from the max-propagation atlas distributed with the SPM Anatomy Toolbox.
-The atlas was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary.
-\item The Harvard-Oxford (HO) parcellation, distributed with FSL, was split into cortical and subcortical probabilistic atlases.
-A 25\% threshold was applied to each of these atlases and they were subsequently bisected into left and right hemispheres at the midline ($x=0$).
-ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical atlas.
-The subcortical and cortical ROIs were combined.
-\end{itemize}
-All the anatomical templates were resampled into the functional space using nearest-neighbor interpolation.
-
-\paragraph{The CC200 and CC400 functional parcellations} Two functional brain parcellations, called CC200 and CC400, were derived from rs-fMRI data using a two-stage spatially-constrained clustering procedure \cite{craddock2012whole}.
-Only a subset ($N=650$) of high-quality preprocessed and unfiltered rs-fMRI data was selected to generate the parcellations, as determined by registration quality and exclusion of subjects with more than 3 mm translation or 3 degrees rotations in their motion parametes.
-A group grey matter mask was constructed by averaging individual grey matter masks derived from freesurfer automated segmentation.
-Subject-specific connectivity graphs were constructed by treating each voxel in the grey matter as a node and edges corresponding to super-threshold temporal correlations to the voxels' 3D (27 voxel) neighborhood.
-Each subjects' graph was partitioned into 200 or 400 regions using normalized cut spectral clustering.
-Adjacency matrices were constructed from the clustering results by setting the connectivity between voxels to 1 if they are in the same ROI and 0 otherwise.
-A group-level consensus matrix was constructed by averaging the individual level adjacency matrices and subsequently partitioned into 200 or 400 regions using normalized cut clustering.
-% PB: @CC What was the threshold in "super-threshold"? Also how did you measure "registration quality"?
-%I've switched a few terms, to use adjacency and consensus.
-Adjacency is pretty standard, and based on Monti2003 I believe consensus was the first term used for this, and one that is pretty intuitive too.
-% The CC200 and CC400 actually have 190 and 351 ROIs, why?
-% Overall you may want to review closely this paragraph in particular, as I just copied it over from the wiki with few edits.
 
@@
 
-\subsection{Connectivity maps}
-% We are missing the ALFF
-Regional homogeneity (ReHo) was calculated for the preprocessed and filtered whole brain rs-fMRI data using the procedure described in \citep{zang2004regional}.
-The functional connectivity maps for 10 resting-state networks reported by \cite{smith2009correspondence} were constructed using a modified dual regression approach.
-A spatial multiple regression was first used to extract time courses corresponding to each network.
-In a second step, each time course was independently correlated with whole brain time series to generate subject-specific functional connectivity maps for each network.
-Alternatively, all time courses were entered simultaneously into a multiple (temporal) regression, and the regression cofficients associated with each time course constituted the functional connectivity maps.
-Both approaches have been released.
-
 % The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo.
-\subsection{Voxel-based morphometry}
-%Details on the Burner pipeline can be found on the NITRC website\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NiakPipeline}}.
-The T1 images were segmented into grey matter and white matter probability maps using the "New Segmentation" method implemented in SPM8.
-The tissue maps were rigidly aligned (translation+rotation).
-Inter subject normalization was performed using DARTEL toolbox in SPM8.
-Images were iteratively registered to the group average (population template), and the template was updated iteratively.
-This iterative process resulted into finer and finer registrations.
-The registration parameters were applied to each image to resample them into the space of the population average.
-A modulation was applied to preserve the global tissue volumes after normalization.
 
@@
 Both the Athena and NIAK pipelines generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset.
-For each brain map statistical derivative, the Athena pipeline calculated a $z$-score at each voxel and for each individual, based on the group mean and std.
-This $z$ transform was used to detect outlier values in the images, which could potentially be used by participants to identify problematic datasets.
+
 The output of the Burner pipeline were visually inspected by Dr Chu.
@@
 
-\bibliographystyle{elsarticle-num}
+\bibliographystyle{elsarticle-num-names}
 % \bibliographystyle{elsarticle-harv}

### 2015-12-22 Bellec_ADHD200_2016.tex
figure integration
Many many changes...

@@
 \address[label5]{Max Planck Research Group for Neuroanatomy \& Connectivity, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany}
-\ead{daniel.margulies@gmail.com}
+\ead{margulies@cbs.mpg.de}
 
@@
 \begin{abstract}
-In 2011, the ``ADHD-200 Global Competition'' was held with the aim of identifying biomarkers of attention deficit hyperactivity disorder from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data collected on 973 individuals.
+In 2011, the ``ADHD-200 Global Competition'' was held with the aim of identifying biomarkers of attention-deficit/hyperactivity disorder from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data collected on 973 individuals.
 Statisticians and computer scientists were potentially the most qualified for the machine learning aspect of the competition, but generally lacked the specialized skills to implement the necessary steps of data preparation for rs-fMRI.
 Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC) (\url{http://www.nitrc.org/frs/?group_id=383}).
-This ``ADHD200 preprocessed'' release included multiple analytical pipelines to cater to different philosophies of data analysis.
+This ``ADHD-200 Preprocessed'' release included multiple analytical pipelines to cater to different philosophies of data analysis.
 The processed derivatives included denoised and registered 4D fMRI volumes, regional time series extracted from brain parcellations, maps of 10 intrinsic connectivity networks, fractional amplitude of low frequency fluctuation, and regional homogeneity, along with grey matter density maps.
 The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians.
-To the best of our knowledge, the ADHD200 preprocessed release was the first large public resource of preprocessed resting-state fMRI and structural MRI data, and remains to this day the only resource featuring a battery of alternative processing paths.
+To the best of our knowledge, the ADHD-200 Preprocessed release was the first large public resource of preprocessed resting-state fMRI and structural MRI data, and remains to this day the only resource featuring a battery of alternative processing paths.
 \end{abstract}
@@
 \item Processed derivatives generated from structural and resting-state fMRI in 973 individuals. 
-\item The sample includes 585 typically developing children, 362 children with attention deficit hyperactivity disorder, and 26 with unknown diagnostic status.
+\item The sample includes 585 typically developing children, 362 children with attention-deficit/hyperactivity disorder, and 26 with unknown diagnostic status.
 \item Functional MRI volumes were denoised and aligned using two alternative processing pipelines. 
@@
 
-In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention deficit hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}.
+In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}.
 The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}.
-The data includes rs-fMRI, structural MRI (sMRI), and basic phenotypic information for 973 individuals (585 TDC, 362 ADHD, 26 unknown) \cite{Milham2012}.
+The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}.
 Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels for test data for which diagnostic information was withheld.
@@
 The ``ADHD-200 Preprocessed'' is a repository of preprocessed rs-fMRI and s-MRI data along with statistical derivatives from the ADHD-200 Sample.
-Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated.
+Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in the toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated.
 The Athena pipeline processed rs-fMRI and s-MRI images using a combination of AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
-The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry style tools.
+The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry.
 The NIAK pipeline processed rs-fMRI and s-MRI using a workflow composed of tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011}, which were assembled with the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
@@
 
-%The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
+% The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
 The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians with limited prior neuroimaging experience \cite{Eloyan2012}.
@@
 
-The ADHD-200 preprocessed data was released in 2011 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
+The ADHD-200 Preprocessed data was released in 2011 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
 No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account.
 This registration enables downloads to be tracked for usage statistics.
-Registered users can also be contacted in the event that errors would be found.
-The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/adhd200/}}.
+Registered users can also be contacted in the event that errors are found in the dataset.
+The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/ADHD-200/}}.
 There are no more restrictions placed on the preprocessed data or derivatives other than the request that the ADHD-200 Preprocessed Initiative is cited appropriately and that the specific pipeline is acknowledged in publications using the data.
-A forum is available on the Neuro Bureau's NITRC project page for users to ask questions or report
-problems\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=2046}}.
+A forum is available on the Neuro Bureau's NITRC project page for users to ask questions or report problems\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=2046}}.
 Questions regarding data acquisition or phenotypic variables should be directed to INDI's support forum\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=1735}}.
@@
 
-The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis see table \ref{part_table}).
+The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis see Table~\ref{part_table}).
 For each individual, phenotypic data includes sex, age, handedness, ADHD diagnosis (585 TDC, 362 ADHD, 26 unknown), ADHD subtype (ADHD-combined, ADHD-inattentive, ADHD-hyperactive/impulsive), one of three different measures of ADHD severity, one of five measures of intelligence, co-morbid diagnoses, and whether or not they have used medication to treat their symptoms \cite{Milham2012}.
 Imaging data for each individual includes one or more T1-weighted high-resolution s-MRI scan (s-MRI) and one or more rs-fMRI scan.
-Most of the data was collected from a single imaging session, although a second session is available for 15 individuals from the WUSTL site.
-There is a substantial amount of variation in how the data was collected across sites including the type of MRI system and scanning parameters used, the length of the rs-fMRI scans, and the instructions given to the participants prior to the scan (see tables \ref{smri_params_table} and \ref{rsfmri_params_table}).
+The majority of data was acquired during a single imaging session, although a second session is available for 15 individuals from the Washington University at Saint Louis (WUSTL) site.
+There is a substantial amount of variation in data acquisition procedures across sites including the type of MRI system and scanning parameters, the length of the rs-fMRI scans, and the instructions given to participants prior to the scan (see Tables~\ref{smri_params_table} and \ref{rsfmri_params_table}).
 
-Nearly all of the imaging data from the ADHD-200 Sample was included in the preprocessing effort, some individuals were excluded for poor quality or missing data.
-The results of the preprocessing are made available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivative.
-A group level file containing the phenotypic data is available in comma-separated-values format (.csv).
+Nearly all of the imaging data from the ADHD-200 Sample was included in the preprocessing effort, though some individuals were excluded for poor quality or missing data.
+\footnote{Further information regarding excluded data can be found at the respective pipeline wiki page: Athena: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline#Excluded_Data}; Burner: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:BurnerPipeline}; NIAK: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}.}
+The results of the preprocessing are made available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivatives.
+A group-level file containing the phenotypic data is available in comma-separated-values format (.csv).
 
@@
 \tightlist
-\item 3D grey matter density maps suitable for voxel-based morphometry as compressed nifti - Athena, Burner and NIAK
-\item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment (Athena and NIAK)
-\item Average time courses for brain regions from structurally defined atlases (Athena)
-\item Average time courses for brain regions for regions defined by functional parcellation (Athena and NIAK)
-\item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) - Athena
-\end{enumerate}
+    \item 3D grey matter density maps suitable for voxel-based morphometry as compressed NIfTI files --- Athena and Burner (see Figure~\ref{fig:burner})
+    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment --- Athena and NIAK
+    \item Average time series for brain regions from structurally defined atlases --- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
+    \item Average time series for brain regions for regions defined by functional parcellation --- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
+    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) --- Athena (see Figure~\ref{fig:derivatives})
+\end{itemize}
 
@@
 
+\begin{figure}[!t]
+\begin{center}
+  \includegraphics[width=\linewidth]{fig_burner}
+  \caption{Grey matter density maps generated by the Burner pipeline.
+An example of an individual map is presented, along with the average and standard deviation maps for all subjects in the test subsample of ADHD-200 Preprocessed.}
+  \label{fig:burner}
+\end{center}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{center}
+  \includegraphics[width=\linewidth]{fig_parcels}
+  \caption{The brain parcellations used to generate regional time series in the NIAK (ROI1000 and ROI3000) and Athena (all other parcellations) pipelines.
+Each region was randomly assigned to one color in the colormap, and the in-plane outline of regions was painted white at 1 mm resolution.}
+  \label{fig:parcels}
+\end{center}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{center}
+  \includegraphics[width=\linewidth]{fig_connectomes}
+  \caption{The average functional connectivity matrix (Pearson's correlation coefficient between regional time series) was generated across all individuals of the KKI site, for all parcellations of the release (see text for details).
+This matrix was further binarized by retaining connections with an average correlation larger than 0.3.
+The resulting binary adjacency matrices have been represented with an automated layout generated by the Yfan Hu's multilevel algorithm, as implemented in the Gephi software \citep{bastian2009geph}, \url{https://gephi.org/}.
+The size and color of each node was set proportional to its degree, relative to the min and max inside the graph.}
+  \label{fig:connectomes}
+\end{center}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{center}
+  \includegraphics[]{Figure_01}
+  \caption{Derivatives from the Athena pipeline including ten intrinsic connectivity networks (ICNs), fractional amplitude of low-frequency fluctuations (fALFF), and regional homogeneity (ReHo).
+Asterisks (*) in the latter two derivatives denote the difference in colorbar max/min values, as indicated.}
+  \label{fig:derivatives}
+\end{center}
+\end{figure}
+
 \subsection{Athena Pipeline} 
-The Athena pipeline\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline}}  processed rs-fMRI and s-MRI images using a custom BASH script that combined AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
+The Athena pipeline\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline}}  processed rs-fMRI and s-MRI images using a custom BASH script that combined AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits and was run on the Athena computer cluster at Virginia Tech's Advanced Research Computing center\footnote{\url{http://www.arc.vt.edu/}}.
 The processing scripts for each site are distributed in the repository, along with output log files for each processed dataset.
@@
 A non-linear warp was calculated between the skull-off image and MNI space as represented by the NIHPD 4.5\textendash18.5y age-specific assymmetric template \cite{fonov2011unbiased} using a two step procedure that calculates a linear transform \cite{jenkinson2002_flirt} that is subsequently refined by a non-linear registration procedure \cite{andersson2007non}.
-\emph{Shared s-MRI outputs include:} skull stripped whole brain images and smoothed (by a 6-mm FWHM Gaussian) and unsmoothed GM density maps in MNI space at 1$\times$1$\times$1 mm$^3$ resolution, along with the FSL fNIRT non-linear warp, as compressed nifti files (.nii.gz).
+\emph{Shared s-MRI outputs include:} skull-stripped whole-brain images and smoothed (by a 6 mm FWHM Gaussian) and unsmoothed GM density maps in MNI space at 1$\times$1$\times$1 mm$^3$ resolution, along with the FSL fNIRT non-linear warp, as compressed NIfTI files (.nii.gz).
 
 \subsubsection{Functional processing} Athena's rs-fMRI pipeline involved removing the first four volumes to allow for magnetization to reach equilibrium, site-specific slice timing correction to the middle slice, re-aligning each volume to the first volume to correct for motion \cite{cox1999_motion}, and calculating a linear transform between the mean functional volume and the corresponding s-MRI \cite{jenkinson2002_flirt}.
-The rs-fMRI to s-MRI transform was then combined with the s-MRI to MNI non-linear warp to write the functional into MNI152 space at $4\times4\times4$ mm$^3$ resolution.
-Mean WM and CSF signals extracted using the masks calculated during s-MRI processing were included along with 6 head motion parameters and a third-order polynomial in voxel-wise nuisance regression models to remove variation due to physiological noise, head motion and scanner drifts from the time series\cite{lund2006_nvr,fox2005}.
-The resulting de-noised time series were band-pass filtered ($0.009$ Hz $< f < 0.08$ Hz) to limit the data to the frequencies implicated in resting state functional connectivity \cite{biswal1995,cordes2001} and then spatially smoothed with a 6-mm FWHM Gaussian filter.
-\emph{Shared rs-fMRI outputs include:} denoised rs-fMRI volumes, with and without temporal bandpass filtering, in MNI space (compressed 4D niftis, nii.gz), the mean rs-fMRI image and brain mask in template space (nii.gz), and six parameter head motion traces (tab separated value, AFNI .1D files).
+The rs-fMRI to s-MRI transform was then combined with the s-MRI to MNI non-linear warp to write the functional data into MNI152 space at $4\times4\times4$ mm$^3$ resolution.
+Mean WM and CSF signals extracted using the masks calculated during s-MRI processing were included along with 6 head motion parameters and a third-order polynomial in voxelwise nuisance regression models to remove variation due to physiological noise, head motion and scanner drifts from the time series\cite{lund2006_nvr,fox2005}.
+The resulting denoised time series were band-pass filtered ($0.009$ Hz $< f < 0.08$ Hz) to limit the data to the frequencies implicated in resting state functional connectivity \cite{biswal1995,cordes2001} and then spatially smoothed with a 6 mm FWHM Gaussian filter.
+\emph{Shared rs-fMRI outputs include:} denoised rs-fMRI volumes, with and without temporal bandpass filtering, in MNI space (compressed 4D NIfTIs, nii.gz), the mean rs-fMRI image and brain mask in template space (.nii.gz), and six parameter head motion traces (tab-separated values, AFNI .1D files).
 
@@
 Time series were extracted for each atlas from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
-Each of the conformed ROI atlases are available as compressed 3D nifti files (.nii.gz).
+Each of the conformed ROI atlases are available as compressed 3D NIfTI files (.nii.gz).
 
 \paragraph{Time series for functionally defined regions} The CC200 and CC400 functional brain parcellations were constructed using a two-stage spatially-constrained spectral clustering procedure \cite{craddock2012whole} applied to unfiltered preprocessed rs-fMRI data from a subset ($N=650$) of the participants in the training dataset.
-Participants were chose for inclusion based on registration quality and after exclusion of participants with more than 3 mm translation or 3 degrees rotations in their motion parameters.
-To reduce computation time, the clustering was restricted to grey matter using a group GM mask that was constructed by averaging individual GM masks derived from freesurfer automated segmentation.
+Participants were chosen for inclusion based on registration quality and after excluding participants with more than 3 mm translation or 3 degrees rotations in their motion parameters.
+To reduce computation time, the clustering was restricted to grey matter using a group GM mask that was constructed by averaging individual GM masks derived from FreeSurfer automated segmentation \cite{dale1999freesurfer}.
 Although 200 and 400 ROIs were specified in the functional parcellation procedure, the normalized cut algorithm resulted in 190 and 351 clusters respectfully.
 Time series were extracted for each atlas from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
-CC200 and CC400 brain parcellations are available as compressed 3D nifti files (.nii.gz).
+CC200 and CC400 brain parcellations are available as compressed 3D NIfTI files (.nii.gz).
 
-\paragraph{ICN time series and spatial maps} Time series and spatial maps were derived for 10 ICNs that have been found to be consistent across resting state and a variety of neuroimaging tasks  \cite{smith2009correspondence} by applying a modified dual regression approach \cite{Beckmann2009dualreg} to the unfiltered preprocessed data.
-A spatial multiple regression was first used to extract time courses corresponding to each network.
-In a second step, each time course was independently correlated with whole brain time series to generate subject-specific functional connectivity maps for each network.
-Alternatively, all time courses were entered simultaneously into a multiple (temporal) regression, and the regression cofficients associated with each time course constituted the functional connectivity maps.
-The resulting ICN time series are distributed as tab-separated values (AFNI .1D) files and the spatial maps for both temporal regression approaches are distributed as compressed 4D NIFTI files (.nii.gz).
+\paragraph{ICN time series and spatial maps} Time series and spatial maps were derived for 10 ICNs that have been found to be consistent across resting-state datasets and a variety of neuroimaging tasks \cite{smith2009correspondence} by applying a modified dual-regression approach \cite{Beckmann2009dualreg} to the unfiltered preprocessed data.
+A spatial multiple regression was first used to extract time series corresponding to each network.
+In a second step, each time course was independently correlated with whole-brain time series to generate subject-specific functional connectivity maps for each network.
+Alternatively, all time series were entered simultaneously into a multiple (temporal) regression, and the regression coefficients associated with each time series constituted the functional connectivity maps.
+The resulting ICN time series are distributed as tab-separated values (AFNI .1D) files and the spatial maps for both temporal regression approaches are distributed as compressed 4D NIfTI files (.nii.gz).
 
@@
 ReHo was estimated from the unfiltered data at each voxel by the Kendall's Coefficient of Concordance \cite{kendall1939w} between the voxel and its 26 face-, edge-, and corner- touching neighbors.
-The resulting fALFF and ReHo whole brain maps are distributed as compressed 3D NIFTI files (.nii.gz).
+The resulting fALFF and ReHo whole brain maps are distributed as compressed 3D NIfTI files (.nii.gz).
 
@@
 
-No specific quality control was applied to Athena data before release, this was left out to accommodate different opinions on what qualifies as good data.
+No specific quality control was applied to Athena data before release.
+This decision was taken to accommodate for differing opinions as to what might qualify as useable data.
 In addition to files containing the six motion parameters for each rs-fMRI dataset, and anatomical and mean EPI images in template space, which can be visually inspected to determine high motion data or poor registrations, quality metrics derived from structural data, GM masks, mean EPI images, fALFF maps and FC maps were included to help with the QC process.
-For each data type a mean and standard deviation image is calculated from all of the scans from all of the subjects.
-These images are used to perform a voxel-wise z-score transformation on each data type for each subject $z_i = \frac{(v_i-m_i)}{\sigma_i}$.
-The absolute values of these z-scores are then thresholded at 3, and then summed across voxels for a quality score for that image.
+% possibly cut previous sentence into smaller portions for clarity.
+For each data type a mean and standard deviation image was calculated from all of the scans from all of the subjects.
+These images were used to perform a voxelwise z-score transformation on each data type for each subject $z_i = \frac{(v_i-m_i)}{\sigma_i}$.
+The absolute values of these z-scores were thresholded at 3, and summed across voxels for a quality score for that image.
 The higher the resulting sum, the larger the number of voxels a image has that are $\geq 3$ and the more likely the images are outliers.
-Using this metric it is possible to rank images, and allows a more directed search for poor quality scans.
-These metrics are distributed in participant specific text files along with the BASH scripts that implement the procedure.
+Using this metric it is possible to rank images, and allows for a more directed search for poor quality scans.
+These metrics are distributed in participant-specific text files along with the BASH scripts that implement the procedure.
 
@@
 
-Processing begins by segmenting s-MRI images into GM and WM probability maps using SPM8's unified segmentation procedure, which iteratively registers the data to a template and performs tissue classification until both are optimized \cite{ashburner2005unified}.
-Next, SPM8's DARTEL toolbox \cite{ashburner2007dartel} was used to generate a template from the s-MRI data of all participants using another iterative method based on that calculates the nonlinear transforms for warping all participant WM and GM maps to a common space.
-The resulting non-linear deformations were applied to each participants GM probability maps to transform them into the space of population average at 1.5 $\times$ 1.5 $\times$ 1.5 mm$^3$ resolution and modulated to conserve the global tissue volumes after normalization.
-The resulting grey matter density maps are distributed at 3D NIFTI files (.nii).
+Processing began by segmenting s-MRI images into GM and WM probability maps using SPM8's unified segmentation procedure, which iteratively registers the data to a template and performs tissue classification until both are optimized \cite{ashburner2005unified}.
+Next, SPM8's DARTEL toolbox \cite{ashburner2007dartel} was used to generate a template from the s-MRI data of all participants using another iterative method that calculates the nonlinear transforms for warping all participant WM and GM maps to a common space.
+The resulting non-linear deformations were applied to each participant's GM probability maps to transform them into the space of the population average at 1.5 $\times$ 1.5 $\times$ 1.5 mm$^3$ resolution and modulated to conserve the global tissue volumes after normalization.
+The resulting grey matter density maps are distributed at 3D NIfTI files (.nii).
 
 \subsubsection{Quality Assessment}
-Stringent quality control was not applied to the data to accommodate different opinions on what constitutes poor quality data.
+Stringent quality control was not applied to the data in order to accommodate different opinions on what constitutes poor quality data.
 Images for four participants were excluded after visual inspection by Dr.
-Chiu because they were determined to be too poor quality to be processed.
+Chu because they were determined to be of insufficient quality for further processing.
 
@@
 
-Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D nifti files (.nii.gz).
+Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D NIfTI files (.nii.gz).
 Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL wrap .nii.gz file for Athena and in .xfm/.mnc MINC wrap files for NIAK.
-In addition, ancillary files such as the estimated rigid-body motion parameters (AFNI .1D tab-separated-value for Athena, and HDF5 files .mat files for NIAK), mean functional image (.nii.gz files) as well as individual and group brain masks (.nii.gz files) were released in separate archives.
+In addition, ancillary files such as the estimated rigid-body motion parameters (AFNI .1D tab-separated values for Athena, and HDF5 files .mat files for NIAK), mean functional image (.nii.gz files) as well as individual and group brain masks (.nii.gz) were released in separate archives.
+
+% Following paragraph is unclear regarding specific references to Athena: (to be updated)
+\paragraph{The NIAK pipeline} The preprocessing steps in NIAK followed those of the Athena pipeline with differences at the following steps: (1) Only the first three volumes were suppressed, instead of four.
+(4) Although both Athena and NIAK used the MNI non-linear stereotaxic template space described in \citep{fonov2011unbiased}, the NIAK used the young adult (ICBM152) symmetric variant, while Athena used the NIHPD asymmetric pediatric template (4.5 y.o.-18.5 y.o.).
+(5) The fMRI volumes were resampled in stereotaxic space at 3 mm isotropic (instead of 4 mm), and this was done only right before spatial smoothing (step 5 was moved before step 8).
+(6) No regression of confounds was performed.
+Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{perlbarg2007corsica} after temporal filtering (steps 6 and 7 were inverted).
+(7) Only a high-pass filter was implemented ($0.01$ Hz $< f$), instead of a band-pass.
 
@@
 The  NIAK distributed them as HDF5 files (.mat Matlab).
-All brain parcellations were also released as compressed nifti files (.nii.gz).
+All brain parcellations were also released as compressed NIfTI files (.nii.gz).
+\paragraph{Anatomical parcellations} For both Athena and NIAK, regional time series were extracted by averaging preprocessed resting-state volumes within different brain parcels.
+The Athena pipeline first used a series of parcellations delineated on the basis of anatomical landmarks:
 
-\subsection{Brain maps}
-The Athena pipeline derived a number of brain maps derived from the preprocessed fMRI datasets: fractional amplitude of low frequency fluctuations (fALFF) maps, regional homogeneity (ReHO) maps and dual-regression based on a group independent component analysis (ICA) with 10 resting-state networks \citep{smith2009correspondence}.
-One compressed nifti file (.nii.gz) was released per fMRI dataset and type of brain map, with in addition the time courses of the dual regression available in text files (.1D AFNI).
+\paragraph{The ROI1000 and ROI3000 functional parcellations} A region-growing algorithm \citep{bellec2006identification} based on the iterative merging of mutual-nearest-neighbours was implemented to generate functional brain parcellations.
+The spatial dimension was selected arbitrarily by setting the size where the growing process stopped, measured in mm$^3$.
+Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting into roughly 1000 and 3000 ROIs covering the grey matter.
+The regions were built to maximize the average correlation between the time series associated with any pair of voxels of the region.
+The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance) at the KKI site (training data only), such that the homogeneity was maximized on average for all subjects, and the small homogeneous regions were identical for all subjects.
+Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{tzourio2002automated}.
+
+% The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo.
+
+%Details on the NIAK pipeline can be found on the NITRC website.
+
+% http://www.nitrc.org/plugins/mwiki/index.php/niak:FmriPreprocessing064#Summary_of_the_pipeline
+
+\subsubsection{Quality control}
+
+Both the Athena and NIAK pipelines generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset.
+The output of the Burner pipeline were visually inspected by Dr Chu.
+The individual results of the NIAK pipeline were visually reviewed by M.
+Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space.
+The conclusions of the NIAK quality control procedure are available on NITRC\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+
+%%%
+%%% - tables
+%%%
 
@@
 \caption{{\bf ADHD-200 participants by site.} BHBU: Bradley Hospital/ Brown University, KKI: Kennedy Krieger Institute, NI: NeuroIMAGE sample, NYU: New York University Child Study Center, OHSU: Oregon Health Sciences University, PKU: Peking University, Pitt: University of Pittsburgh, WUSTL: Washington University at Saint Louis, avg.: average.
-$^*$Diagnostic labels are current not available for BHBU, they have been listed as TDC in the table, but not included in the totals.}\label{part_table}
+$^*$Diagnostic labels are currently not available for BHBU, they have been listed as TDC in the table, but not included in the totals.}\label{part_table}
   \begin{tabular}{llrrrr}
@@
              & 0 & - \\
-         & M &  9$^*$ & 12.00 - 17.83 (15.96) 
+         & M &  9$^*$ & 12 - 18 (16.1) 
              & 0 & - \\
-    KKI  & F & 28 & 8.12 - 12.36 (10.19) 
-             & 10 & 8.10 - 12.99 (9.97) \\
-         & M & 41 & 8.02 - 12.87 (10.35) 
-             & 15 & 8.19 - 12.98 (10.08) \\
-    NI  & F & 25 & 11.66 - 26.31 (18.69) 
-             & 5 & 11.85 - 19.66 (15.07) \\
-         & M & 12 & 12.84 - 25.04 (18.02) 
-             & 31 & 11.05 - 20.89 (17.05) \\
-    NYU  & F & 55 & 7.17 - 17.96 (12.20) 
-             & 34 & 7.35 - 17.15 (10.27) \\
-         & M & 56 & 7.19 - 17.96 (12.20) 
-             & 117 & 7.24 - 17.61 (11.19) \\
-    OHSU  & F & 40 & 7.33 - 12.50 (8.98) 
-             & 13 & 7.42 - 11.33 (9.01) \\
-         & M & 30 & 7.17 - 11.92 (9.48) 
-             & 30 & 7.42 - 11.83 (8.94) \\
-    PKU  & F & 59 & 8.33 - 15.17 (10.90) 
-             & 10 & 8.83 - 15.92 (10.88) \\
-         & M & 84 & 8.08 - 14.92 (11.80)  
-             & 92 & 8.33 - 17.33 (12.22) \\ 
-    Pitt  & F & 44 & 10.16 - 20.45 (15.65) 
-             & 1 & 15.04 \\
-         & M & 50 & 10.11 - 18.96 (14.55)  
-             & 3 & 13.72 - 17.03 (15.55) \\ 
-    WUSTL  & F & 28 & 7.09 - 21.81 (11.33) 
+    KKI  & F & 28 & 8 - 12 (10.3) 
+             & 10 & 8 - 13 (9.9) \\
+         & M & 41 & 8 - 13 (10.4) 
+             & 15 & 8 - 13 (10.1) \\
+    NI  & F & 25 & 12 - 26 (18.8) 
+             & 5 & 12 - 20 (15.2) \\
+         & M & 12 & 13 - 25 (17.9) 
+             & 31 & 11 - 21 (17.1) \\
+    NYU  & F & 55 & 7 - 18 (12.2) 
+             & 34 & 7 - 17 (10.1) \\
+         & M & 56 & 7 - 18 (12.0) 
+             & 117 & 7 - 18 (11.2) \\
+    OHSU  & F & 40 & 7 - 12 (9.0) 
+             & 13 & 7 - 11 (8.9) \\
+         & M & 30 & 7 - 12 (9.5) 
+             & 30 & 7 - 12 (8.9) \\
+    PKU  & F & 59 & 8 - 15 (10.9) 
+             & 10 & 9 - 16 (10.9) \\
+         & M & 84 & 8 - 15 (11.8)  
+             & 92 & 8 - 17 (12.2) \\ 
+    Pitt  & F & 44 & 10 - 20 (15.7) 
+             & 1 & 15 \\
+         & M & 50 & 10 - 19 (14.5)  
+             & 3 & 14 - 17 (15.7) \\ 
+    WUSTL  & F & 28 & 7 - 22 (11.3) 
              & 0 & - \\
-         & M & 33 & 7.25 - 21.83 (11.58)  
+         & M & 33 & 7 - 22 (11.5)  
              & 0 & - \\ 
-    \bf{Totals} & F & 279$^*$ & 7.09 - 26.31 (11.9)
-               & 73 & 7.35 - 19.66 (10.48) \\
-           & M & 306$^*$ & 7.17 - 25.04 (12.20)
-               & 288 & 7.24 - 20.89 (11.90) \\
+    \noalign{\vskip 1ex}  
+    \hline
+    \noalign{\vskip 1ex}
+    \bf{Totals} & F & 279$^*$ & 7 - 26 (12.3)
+               & 73 & 7 - 20 (10.4) \\
+           & M & 306$^*$ & 7 - 25 (12.1)
+               & 288 & 7 - 21 (11.9) \\
     \noalign{\vskip 1ex}  
@@
 
-\section{Processing strategies}
-Further details on the processing strategies can be found on the ``ADHD200 preprocessed'' website\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:ADHDpreproc}}.
+Table~\ref{tab_parcellations} summarizes the characteristics of the parcellations, which were also presented in Figure~\ref{fig_parcellations}.
 
-\subsection{Preprocessed sMRI and rs-fMRI}
-
-\paragraph{The NIAK pipeline} The preprocessing steps in NIAK followed those of the Athena pipeline with differences at the following steps.
-(1) Only the first three volumes were suppressed, instead of four.
-(4) Although both Athena and NIAK used the MNI non-linear stereotaxic template space described in \citep{fonov2011unbiased}, the NIAK used the young adult (ICBM152) symmetric variant, while Athena used the NIHPD asymmetric pediatric template (4.5 y.o.-18.5 y.o.).
-(5) The fMRI volumes were resampled in stereotaxic space at 3 mm isotropic (instead of 4 mm), and this was done only right before spatial smoothing (step 5 was moved before step 8).
-(6) No regression of confounds was performed.
-Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{perlbarg2007corsica} after temporal filtering (steps 6 and 7 were inverted).
-(7) Only a high-pass filter was implemented ($0.01$ Hz $< f$), instead of a band pass.
-
-\subsection{Regional time series}
-Table \ref{tab_parcellations} summarizes the characteristics of the parcellations, which were also presented in Figure \ref{fig_parcellations}. 
 \begin{table}[htbp]
 \label{tab_parcellations}
-\caption{Summary of the characteristics of all brain parcellations used in the ADHD200 preprocessed release. All reported size for the parcels are measured in mm$^3$.}
+\caption{Summary of the characteristics of all brain parcellations used in the ADHD-200 Preprocessed release. All reported size for the parcels are measured in mm$^3$.}
 \begin{tabular}{llrrrrr}
@@
 % PB - @CC: I found a mismatch between the # of ROIs for AAL, EZ, HO and TT from my own extraction and the NITRC table. Any idea why?
-% I suspect you eliminated small regions (HO, TT and CC400 have regions with only one voxel). But I am deriving the stats from the nifti files 
+% I suspect you eliminated small regions (HO, TT and CC400 have regions with only one voxel). But I am deriving the stats from the NIfTI files 
 % shipped with the release so I also want to be consistent with what people get. 
+%
+% CC - @PB: I think that these 1 voxel clusters are errors introduced when downsampling the data to the resolution of the functional data.
 
-\paragraph{Anatomical parcellations} For both Athena and NIAK, regional time series were extracted by averaging preprocessed resting-state volumes within different brain parcels.
-The Athena pipeline first used a series of parcellations delineated on the basis of anatomical landmarks:
+\section{Recommendations for using the data}
 
-\paragraph{The ROI1000 and ROI3000 functional parcellations} A region-growing algorithm \citep{bellec2006identification} based on the iterative merging of mutual-nearest-neighbours was implemented to generate functional brain parcellations.
-The spatial dimension was selected arbitrarily by setting the size where the growing process stopped, measured in mm$^3$.
-Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting into roughly 1000 and 3000 ROIs covering the grey matter.
-The regions were built to maximize the average correlation between the time series associated with any pair of voxels of the region.
-The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance) at the KKI site (training data only), such that the homogeneity was maximized on average for all subjects, and the small homogeneous regions were identical for all subjects.
-Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{tzourio2002automated}.
+Besides identifying rs-fMRI based biomarkers of ADHD --- the reason that the ADHD-200 Sample was originally created and its most common use so far --- there are a variety of interesting analyses that can be performed using this data \cite{craddock2015}.
+With 585 TDC participants between the ages of 7 and 26, and the inclusion of measures of intelligence, the ADHD-200 Preprocessed is a valuable resource for mapping developmental trajectories \cite{dosenbach2010, zuo2010, dimartino2014} and other sources of inter-individual variation \cite{kelly2012}.
+Perhaps most exciting are new methods that cluster individuals based on connectivity profiles \cite{miranda2014connectotyping, finn2015fingerprinting}, which are providing new hope for using neuroimaging data to parse the heterogeneity within mental health disorders \cite{castellanos2013}.
+One of the biggest outstanding needs for neuroimaging, and connectomics in particular, is the development and validation of new analytical tools and processing strategies \cite{craddock2013,varoquaux2013,craddock2015} and it is our hope that the ADHD-200 Preprocessed data will become a benchmark dataset for evaluating new tools as they are proposed.
 
-% The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo.
+The two biggest challenges for using this data are head motion \cite{power2012, vandijk2012, sattertwhaite2012, fair2012ADHD-200, yan2013motion, yan2013small} and inter-site variation in the equipment, parameters, and experimental procedures used to collect the data \cite{Olivetti2012,yan2013std}.
+A variety of different approaches have been proposed for addressing head motion in hyperkinetic populations \cite{power2012, sattertwhaite2013}, and in the ADHD-200 Sample in particular \cite{fair2012ADHD-200}, that should be considered when analyzing the data.
+At the very least, some statistic that characterizes individual motion (such as root mean square deviation \cite{JenkinsonTR99}) should be included as a nuisance regressor in the group level model \cite{sattertwhaite2012, yan2013motion}.
+Differences in the manner in which data was collected at each site can introduce addition and multiplicative effects (batch effects) to the data, which may obscure the underlying biological signal \cite{Olivetti2012,yan2013std}.
+Including a regressor for acquisition protocol (see tables \ref{smri_params_table} and \ref{rsfmri_params_table} for different protocols), the average pairwise correlation between all regions in the brain (GCOR) \cite{saad2013gcor}, or the whole-brain average of the feature under inquiry \cite{yan2013std}, have all been shown effective for dealing with inter-site variation.
 
-%Details on the NIAK pipeline can be found on the NITRC website.
-
-% http://www.nitrc.org/plugins/mwiki/index.php/niak:FmriPreprocessing064#Summary_of_the_pipeline
-
-\section{Quality control}
-
-Both the Athena and NIAK pipelines generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset.
-
-The output of the Burner pipeline were visually inspected by Dr Chu.
-The individual results of the NIAK pipeline were visually reviewed by M.
-Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space.
-The conclusions of the NIAK quality control procedure are available on NITRC\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+% CC-@PB please include any citations to your work that you think help in the talk of parcellations
+Beyond personal ideology, or the availability of particular features, there is no clear reason to prefer one pipeline over the other.
+Hopefully, the presence of multiple pipelines will enable researchers to compare the robustness of their tools or analysis results to different processing choices.
+It isn't clear which of the parcellations provide the best time series, although there is growing consensus that functionally defined brain regions areas represent the brains intrinsic connectivity better than structurally defined atlases \cite{craddock2012whole, Blumensath2013, thirion2014}.
+Similarly, it isn't clear which scale of parcellation is the best.
+More, smaller parcels tend to be better at representing connectivity present at the voxel scale \cite{bellec2006identification, craddock2012whole, thirion2014}, but fewer parcels may be more manageable for the analysis at hand.
 
@@
 
-The ADHD200 preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD200 competition, with over 10,500 downloads by more than 600 users, as well as 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over 3 years, with more in press or under review.
+The ADHD-200 Preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD-200 competition, with over 10,500 downloads by more than 600 users, as well as 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over 3 years, with more in press or under review.
 The resource was also used outside of the neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
-In particular, the winning team of the ADHD200 global competition was based at the Johns Hopkins Biostatistics Department and used ADHD200
-% i don't think that we can conclude that the availability of the time series was the driving factor behind the pubs by non-neuroimagers
-% PB->CC OK so I quickly checked some of these references, and they are definitely using a variety of derivatives. OK. 
-% Just a note is She2014.
-In this paper if you blink you will miss the fMRI section.
-It's 10 lines long, in an otherwise highly theoretical paper, and the other application (also 10 lines) is about yeast gene regulation network.
-I think this is awesome, and possible because you can grab time series without having any clue what they represent and run with it.
-But I am extrapolating too much from this example.
-preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
+In particular, the winning team of the ADHD-200 global competition was based at the Johns Hopkins Biostatistics Department and used ADHD-200 Preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
 \par 
-Our conclusions are more mitigated regarding the secondary objective of ``ADHD200 preprocessed'', which was to cater to multiple data processing philosophies.
-The release was a success in the sense that almost all variants of processing strategies included in the ADHD200 release have been used in follow-up published manuscripts.
-However, no publication we are aware of actually implemented a face-to-face comparison between processing techniques.
+Our conclusions are more mitigated regarding the secondary objective of ``ADHD-200 Preprocessed'', which was to cater to multiple data processing philosophies.
+The release has been a success in the sense that almost all variants of processing strategies included in the ADHD-200 release have been used in follow-up published manuscripts.
+However, we are not aware of a publication that has performed a face-to-face comparison between processing techniques.
 With the approach we took, any direct comparison between Athena and NIAK was difficult to interpret, as the two pipelines did not use the same specific stereotaxic space, varied in many ways in terms of selected parameters, and also had quite different approaches for QC, derivatives or even packaging the derivatives.
@@
 \par 
-The impact of the ``ADHD200 preprocessed'' repository emphasized the need to reduce computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
+The impact of the ``ADHD-200 Preprocessed'' repository emphasized the need to reduce computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
 This need is further emphasized by a recent survey of FCP/INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
-We do not plan to expand or update the ADHD200 release as such, which we hope will continue to serve as a legacy benchmark dataset.
+We do not plan to expand or update the ADHD-200 release as such, which we hope will continue to serve as a legacy benchmark dataset.
 We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data to accelerate neuroimaging research.
-We are now working on new initiatives learning from the ADHD200 preprocessed experiment, notably including a larger number of alternative analytical workflows as well as a careful harmonization of processing, quality control and data packaging strategies.
-Our hope is that ADHD200 preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.
+We are now working on new initiatives learning from the ADHD-200 Preprocessed experiment, notably including a larger number of alternative analytical workflows as well as a careful harmonization of processing, quality control and data packaging strategies.
+Our hope is that ADHD-200 Preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.
 
-%% References
-%%
-%% Following citation commands can be used in the body text:
 %% Usage of \cite is as follows:
@@
 %%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
 
 %% References with bibTeX database:
-
 \bibliographystyle{elsarticle-num-names}
@@
 
-\bibliography{adhd200_pubs}
-
+\bibliography{ADHD-200_pubs}
 \end{document}
-
-%%
-%% End of file `elsarticle-template-num.tex'.

### 2015-12-22 Bellec_ADHD200_2016.tex
additional changes

@@
 
-\section{Recommendations for using the data}
+\section{Usage recommendations}
 
-Besides identifying rs-fMRI based biomarkers of ADHD --- the reason that the ADHD-200 Sample was originally created and its most common use so far --- there are a variety of interesting analyses that can be performed using this data \cite{craddock2015}.
-With 585 TDC participants between the ages of 7 and 26, and the inclusion of measures of intelligence, the ADHD-200 Preprocessed is a valuable resource for mapping developmental trajectories \cite{dosenbach2010, zuo2010, dimartino2014} and other sources of inter-individual variation \cite{kelly2012}.
+The ADHD-200 Sample was originally created to identify rs-fMRI based biomarkers of ADHD; however, the dataset provides ample opportunity for further analyses \cite{craddock2015}.
+With 585 TDC participants between the ages of 7 and 26, and the inclusion of intelligence measures, the ADHD-200 Preprocessed is a valuable resource for mapping developmental trajectories \cite{dosenbach2010, zuo2010, dimartino2014} and other sources of inter-individual variation \cite{kelly2012}.
 Perhaps most exciting are new methods that cluster individuals based on connectivity profiles \cite{miranda2014connectotyping, finn2015fingerprinting}, which are providing new hope for using neuroimaging data to parse the heterogeneity within mental health disorders \cite{castellanos2013}.
-One of the biggest outstanding needs for neuroimaging, and connectomics in particular, is the development and validation of new analytical tools and processing strategies \cite{craddock2013,varoquaux2013,craddock2015} and it is our hope that the ADHD-200 Preprocessed data will become a benchmark dataset for evaluating new tools as they are proposed.
+One of the outstanding needs for neuroimaging, and connectomics in particular, is the development and validation of new analytical tools and processing strategies \cite{craddock2013,varoquaux2013,craddock2015}.
+In the service of this aim, the ADHD-200 Preprocessed repository has the necessary components to become a benchmark dataset for evaluating new tools as they are proposed.
 
-The two biggest challenges for using this data are head motion \cite{power2012, vandijk2012, sattertwhaite2012, fair2012ADHD-200, yan2013motion, yan2013small} and inter-site variation in the equipment, parameters, and experimental procedures used to collect the data \cite{Olivetti2012,yan2013std}.
-A variety of different approaches have been proposed for addressing head motion in hyperkinetic populations \cite{power2012, sattertwhaite2013}, and in the ADHD-200 Sample in particular \cite{fair2012ADHD-200}, that should be considered when analyzing the data.
-At the very least, some statistic that characterizes individual motion (such as root mean square deviation \cite{JenkinsonTR99}) should be included as a nuisance regressor in the group level model \cite{sattertwhaite2012, yan2013motion}.
+The two biggest challenges for using the ADHD-200 Preprocessed data are head motion \cite{power2012, vandijk2012, sattertwhaite2012, fair2012adhd200, yan2013motion, yan2013small} and inter-site variation in the acquisition equipment, parameters, and experimental procedures \cite{Olivetti2012,yan2013std}.
+A variety of different approaches have been proposed for addressing head motion in hyperkinetic populations \cite{power2012, sattertwhaite2013}, and in the ADHD-200 Sample in particular \cite{fair2012adhd200}, that should be considered when analyzing the data.
+At the very least, some statistic that characterizes individual motion (such as root mean square deviation \cite{JenkinsonTR99}) should be included as a nuisance regressor in the group-level model \cite{sattertwhaite2012, yan2013motion}.
 Differences in the manner in which data was collected at each site can introduce addition and multiplicative effects (batch effects) to the data, which may obscure the underlying biological signal \cite{Olivetti2012,yan2013std}.
-Including a regressor for acquisition protocol (see tables \ref{smri_params_table} and \ref{rsfmri_params_table} for different protocols), the average pairwise correlation between all regions in the brain (GCOR) \cite{saad2013gcor}, or the whole-brain average of the feature under inquiry \cite{yan2013std}, have all been shown effective for dealing with inter-site variation.
+Including a regressor for acquisition protocol (see Tables~\ref{smri_params_table} and \ref{rsfmri_params_table} for a summary of the different protocols), the average pairwise correlation between all regions in the brain (GCOR) \cite{saad2013gcor}, or the whole-brain average of the feature under inquiry \cite{yan2013std}, have all been shown to be effective for dealing with inter-site variation.
 
@@
 Hopefully, the presence of multiple pipelines will enable researchers to compare the robustness of their tools or analysis results to different processing choices.
-It isn't clear which of the parcellations provide the best time series, although there is growing consensus that functionally defined brain regions areas represent the brains intrinsic connectivity better than structurally defined atlases \cite{craddock2012whole, Blumensath2013, thirion2014}.
-Similarly, it isn't clear which scale of parcellation is the best.
-More, smaller parcels tend to be better at representing connectivity present at the voxel scale \cite{bellec2006identification, craddock2012whole, thirion2014}, but fewer parcels may be more manageable for the analysis at hand.
+It isn't clear which of the parcellations provide the optimal time series, although there is growing consensus that functionally-defined brain regions represent the brain's intrinsic connectivity better than structurally-defined atlases \cite{craddock2012whole, Blumensath2013, thirion2014}.
+Similarly, it isn't clear which scale of parcellation is optimal.
+While smaller parcels tend to be better at representing connectivity present at the voxel-scale \cite{bellec2006identification, craddock2012whole, thirion2014}, fewer parcels may be more manageable for the specific analysis at hand.
+% DM: Should we also mention the degrees of freedom issue here in addition to the point regarding 'manageability'?
 
@@
 
-The ADHD-200 Preprocessed initiative was a success in terms of its primary objective: the data repository was effectively used by many researchers during and after the ADHD-200 competition, with over 10,500 downloads by more than 600 users, as well as 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over 3 years, with more in press or under review.
-The resource was also used outside of the neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
-In particular, the winning team of the ADHD-200 global competition was based at the Johns Hopkins Biostatistics Department and used ADHD-200 Preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
-\par 
-Our conclusions are more mitigated regarding the secondary objective of ``ADHD-200 Preprocessed'', which was to cater to multiple data processing philosophies.
-The release has been a success in the sense that almost all variants of processing strategies included in the ADHD-200 release have been used in follow-up published manuscripts.
-However, we are not aware of a publication that has performed a face-to-face comparison between processing techniques.
-With the approach we took, any direct comparison between Athena and NIAK was difficult to interpret, as the two pipelines did not use the same specific stereotaxic space, varied in many ways in terms of selected parameters, and also had quite different approaches for QC, derivatives or even packaging the derivatives.
+The ADHD-200 Preprocessed initiative was successful in its primary objective: the data repository was effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
+The resource also expanded the boundaries of the traditional neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
+In particular, the winning team of the ADHD-200 Global Competition was based at the Johns Hopkins Biostatistics Department and used ADHD-200 Preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
+
+Our conclusions are more mitigated regarding the secondary objective of ADHD-200 Preprocessed, which was to cater to multiple data processing philosophies.
+The release has been a success in the sense that almost all variants of processing strategies included in the ADHD-200 Preprocessed repository have been used in follow-up publications.
+However, we are not aware of a publication that has performed direct comparisons between processing techniques.
+With the approach we took, any direct comparison between Athena and NIAK was difficult to interpret, as the two pipelines did not use the same specific stereotaxic space, varied in many ways in terms of selected parameters, and also had quite different approaches for quality control, derivatives and even packaging the derivatives.
 This lack of harmonization was essentially driven by the tight deadline for data release imposed by the competition, rather than a design choice.
-We since came to the conclusion that it would be useful to build the processing pipelines on a common stereotaxic space and possibly sets of registration, so that the strategies of noise reduction can be more readily compared.
-\par 
-The impact of the ``ADHD-200 Preprocessed'' repository emphasized the need to reduce computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
-This need is further emphasized by a recent survey of FCP/INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
-We do not plan to expand or update the ADHD-200 release as such, which we hope will continue to serve as a legacy benchmark dataset.
-We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data to accelerate neuroimaging research.
-We are now working on new initiatives learning from the ADHD-200 Preprocessed experiment, notably including a larger number of alternative analytical workflows as well as a careful harmonization of processing, quality control and data packaging strategies.
+We have since concluded that it would be preferable to build the processing pipelines on a common stereotaxic space (and possibly sets of registration)
+% 'sets of registration' is unclear. Perhaps: 'sets of template registration spaces'
+, so that the various noise reduction strategies can be more readily compared.
+
+The impact of the ADHD-200 Preprocessed repository demonstrated the need for reducing computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
+This need is further emphasized by a recent survey of INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
+% CC: Should we include stats or remove?
+We do not plan to expand or update the ADHD-200 Preprocessed release as such, which we hope will continue to serve as a legacy benchmark dataset.
+We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroimaging research.
+Current initiatives include a larger number of alternative analytical workflows as well as a careful harmonization of processing, quality control, and data packaging strategies.
 Our hope is that ADHD-200 Preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.

### 2015-12-24 Bellec_ADHD200_2016.tex
Updates from ShareLaTeX
pierres latest

@@
 \author[label0,label3]{Carlton Chu}
-\address[label3]{Deep Mind, London, UK}
+\address[label3]{Google DeepMind, London, UK}
 \ead{carltonchu1@gmail.com}
 
-\author[label0,label1,label4]{Fran\c{c}ois Chouinard-Descortes}
-\address[label4]{McGill University, Montreal, CA}
-\ead{carltonchu1@gmail.com}
+\author[label0,label1,label4]{Fran\c{c}ois Chouinard-Descorte}
+\address[label4]{Integrated Program in Neuroscience, McGill University, Montreal, CA}
+\ead{francois.chouinard@gmail.com}
 
@@
 %%
-% \linenumbers
-\section*{Highlights}
-\begin{itemize}
-\item Processed derivatives generated from structural and resting-state fMRI in 973 individuals. 
-\item The sample includes 585 typically developing children, 362 children with attention-deficit/hyperactivity disorder, and 26 with unknown diagnostic status.
-\item Functional MRI volumes were denoised and aligned using two alternative processing pipelines. 
-\item Derivatives include regional time series, grey matter segmentation as well as two variants of connectivity maps and a measure of intrinsic brain activity. 
-\item These resources are freely available, with minimal access requirements. 
-\end{itemize}
+\linenumbers
+
+%\section*{Highlights}
+%\begin{itemize}
+%\item Processed derivatives generated from structural and resting-state fMRI in 973 individuals. 
+%\item The sample includes 585 typically developing children, 362 children with attention-deficit/hyperactivity disorder, and 26 with unknown diagnostic status.
+%\item Functional MRI volumes were denoised and aligned using two alternative processing pipelines. 
+%\item Derivatives include regional time series, grey matter segmentation as well as two variants of connectivity maps and a measure of intrinsic brain activity. 
+%\item These resources are freely available, with minimal access requirements. 
+%\end{itemize}
+
 \section{Introduction}
@@
 The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}.
-Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels for test data for which diagnostic information was withheld.
+Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld.
 The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise.
@@
 The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry.
-The NIAK pipeline processed rs-fMRI and s-MRI using a workflow composed of tools from the neuroimaging analysis kit (NIAK) \cite{Bellec2011}, which were assembled with the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
+The NIAK pipeline processed rs-fMRI and s-MRI using the NeuroImaging Analysis Kit \cite{Bellec2011}.
 
@@
 
-Nearly all of the imaging data from the ADHD-200 Sample was included in the preprocessing effort, though some individuals were excluded for poor quality or missing data.
-\footnote{Further information regarding excluded data can be found at the respective pipeline wiki page: Athena: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline#Excluded_Data}; Burner: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:BurnerPipeline}; NIAK: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}.}
+Nearly all of the imaging data from the ADHD-200 Sample was included in the preprocessing effort, though some individuals were excluded for poor quality or missing data\footnote{Further information regarding excluded data can be found at the respective pipeline wiki page: Athena: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline#Excluded_Data}; Burner: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:BurnerPipeline}; NIAK: \url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}.}.
 The results of the preprocessing are made available as a collection of compressed tar files that are organized by pipeline, sites of data collection, training and test samples, as well as by derivatives.
@@
 \tightlist
-    \item 3D grey matter density maps suitable for voxel-based morphometry as compressed NIfTI files --- Athena and Burner (see Figure~\ref{fig:burner})
-    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment --- Athena and NIAK
-    \item Average time series for brain regions from structurally defined atlases --- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
-    \item Average time series for brain regions for regions defined by functional parcellation --- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
-    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) --- Athena (see Figure~\ref{fig:derivatives})
+    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner})
+    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK
+    \item Average time series for brain regions from structurally defined parcellations -- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
+    \item Average time series for brain regions for regions defined by functional parcellation -- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
+    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) -- Athena (see Figure~\ref{fig:derivatives})
 \end{itemize}
@@
 \begin{center}
-  \includegraphics[width=\linewidth]{fig_burner}
+  \includegraphics[width=0.6\linewidth]{fig_burner}
   \caption{Grey matter density maps generated by the Burner pipeline.
@@
 This matrix was further binarized by retaining connections with an average correlation larger than 0.3.
-The resulting binary adjacency matrices have been represented with an automated layout generated by the Yfan Hu's multilevel algorithm, as implemented in the Gephi software \citep{bastian2009geph}, \url{https://gephi.org/}.
+The resulting binary adjacency matrices have been represented with an automated layout generated by the Yfan Hu's multilevel algorithm, as implemented in the Gephi software \cite{bastian2009gephi}, \url{https://gephi.org/}.
 The size and color of each node was set proportional to its degree, relative to the min and max inside the graph.}
@@
 
-\subsubsection{Functional processing} Athena's rs-fMRI pipeline involved removing the first four volumes to allow for magnetization to reach equilibrium, site-specific slice timing correction to the middle slice, re-aligning each volume to the first volume to correct for motion \cite{cox1999_motion}, and calculating a linear transform between the mean functional volume and the corresponding s-MRI \cite{jenkinson2002_flirt}.
+\subsubsection{Functional processing}
+
+\paragraph{Preprocessing}Athena's rs-fMRI pipeline involved removing the first four volumes to allow for magnetization to reach equilibrium, site-specific slice timing correction to the middle slice, re-aligning each volume to the first volume to correct for motion \cite{cox1999_motion}, and calculating a linear transform between the mean functional volume and the corresponding s-MRI \cite{jenkinson2002_flirt}.
 The rs-fMRI to s-MRI transform was then combined with the s-MRI to MNI non-linear warp to write the functional data into MNI152 space at $4\times4\times4$ mm$^3$ resolution.
@@
 \paragraph{Time series for structurally defined brain areas} Regional time series were extracted for the automated anatomical labeling (AAL) \cite{tzourio2002automated}, Eickhoff-Zilles (EZ) \cite{eickhoff2005new}, Harvard-Oxford (HO) \cite{HO_atlas_1, HO_atlas_2, HO_atlas_3, HO_atlas_4}, and Talairach and Tournoux (TT) \cite{lancaster2000automated} parcellations.
-The EZ atlas was derived from the max-propagation atlas distributed with the SPM Anatomy Toolbox\footnote{\url{http://www.fz-juelich.de/inm/inm-1/EN/Forschung/_docs/SPMAnatomyToolbox/SPMAnatomyToolbox_node.html}} and was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary.
-The HO atlas was constructed from 25\% thresholded cortical and subcortical max-propagation atlases distributed with FSL.
-The atlases were bisected into left and right hemispheres at the midline ($x=0$), ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical atlas and then the subcortical and cortical ROIs were combined into a single atlas.
-The AAL atlas distributed with the SPM8 version of the AAL Toolbox\footnote{\url{http://www.cyceron.fr/index.php/en/plateforme-en/freeware}} and the TT atlas distributed with AFNI were coregistered and warped into template space.
+The EZ parcellation was derived from the max-propagation parcellation distributed with the SPM Anatomy Toolbox\footnote{\url{http://www.fz-juelich.de/inm/inm-1/EN/Forschung/_docs/SPMAnatomyToolbox/SPMAnatomyToolbox_node.html}} and was transformed into template space using the Colin 27 template (also distributed with the toolbox) as an intermediary.
+The HO parcellation was constructed from 25\% thresholded cortical and subcortical max-propagation parcellations distributed with FSL.
+The parcellations were bisected into left and right hemispheres at the midline ($x=0$), ROIs representing left/right WM, left/right GM, left/right CSF and brainstem were removed from the subcortical parcellation and then the subcortical and cortical ROIs were combined into a single parcellation.
+The AAL parcellation distributed with the SPM8 version of the AAL Toolbox\footnote{\url{http://www.cyceron.fr/index.php/en/plateforme-en/freeware}} and the TT parcellation distributed with AFNI were coregistered and warped into template space.
 Each of the anatomical templates were resampled into the functional space using nearest-neighbor interpolation.
-Time series were extracted for each atlas from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
-Each of the conformed ROI atlases are available as compressed 3D NIfTI files (.nii.gz).
+The average time series within each parcel were extracted from both the filtered and unfiltered data and are distributed in tab-separated values format (AFNI .1D).
+Each of the conformed ROI parcellations are available as compressed 3D NIfTI files (.nii.gz).
 
-\paragraph{Time series for functionally defined regions} The CC200 and CC400 functional brain parcellations were constructed using a two-stage spatially-constrained spectral clustering procedure \cite{craddock2012whole} applied to unfiltered preprocessed rs-fMRI data from a subset ($N=650$) of the participants in the training dataset.
+\paragraph{Time series for functionally defined parcellations} The CC200 and CC400 functional brain parcellations were constructed using a two-stage spatially-constrained spectral clustering procedure \cite{craddock2012whole} applied to unfiltered preprocessed rs-fMRI data from a subset ($N=650$) of the participants in the training dataset.
 Participants were chosen for inclusion based on registration quality and after excluding participants with more than 3 mm translation or 3 degrees rotations in their motion parameters.
@@
 Although 200 and 400 ROIs were specified in the functional parcellation procedure, the normalized cut algorithm resulted in 190 and 351 clusters respectfully.
-Time series were extracted for each atlas from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
+Time series were extracted for each parcellation from both the filtered and unfiltered data by averaging the voxel time series contained within each labeled region and are distributed in tab-separated values format (AFNI .1D).
 CC200 and CC400 brain parcellations are available as compressed 3D NIfTI files (.nii.gz).
@@
 
-\subsubsection{Quality Assessment}
+\subsubsection{Quality Control}
 
 No specific quality control was applied to Athena data before release.
-This decision was taken to accommodate for differing opinions as to what might qualify as useable data.
+This decision was taken to accommodate for differing opinions as to what might qualify as usable data.
 In addition to files containing the six motion parameters for each rs-fMRI dataset, and anatomical and mean EPI images in template space, which can be visually inspected to determine high motion data or poor registrations, quality metrics derived from structural data, GM masks, mean EPI images, fALFF maps and FC maps were included to help with the QC process.
@@
 \subsubsection{Structural processing} 
+Processing began by segmenting s-MRI images into GM and WM probability maps using SPM8's unified segmentation procedure, which iteratively registers the data to a template and performs tissue classification until both are optimized \cite{ashburner2005unified}.
+Next, SPM8's DARTEL toolbox \cite{ashburner2007dartel} was used to register the s-MRI of all participants into a common space using an iterative method.
+Initially, all WM and GM maps were rigidly aligned, and the initial GM and WM templates were created by averaging all aligned maps.
+Then, all WM and GM maps were non-linearly registered to the templates.
+New templates were created after each such iteration of registration.
+The procedure was repeated six times (i.e.
+template creation and registration) to generate sharper templates and warping all participant WM and GM maps to the template space.
+The final (6th iteration) non-linear deformations were applied to each participant's GM probability maps to transform them into the space of the population average at 1.5 $\times$ 1.5 $\times$ 1.5 mm$^3$ resolution and modulated to conserve the global tissue volumes after normalization.
+The resulting grey matter density maps are distributed as 3D NIfTI files (.nii).
 
-Processing began by segmenting s-MRI images into GM and WM probability maps using SPM8's unified segmentation procedure, which iteratively registers the data to a template and performs tissue classification until both are optimized \cite{ashburner2005unified}.
-Next, SPM8's DARTEL toolbox \cite{ashburner2007dartel} was used to generate a template from the s-MRI data of all participants using another iterative method that calculates the nonlinear transforms for warping all participant WM and GM maps to a common space.
-The resulting non-linear deformations were applied to each participant's GM probability maps to transform them into the space of the population average at 1.5 $\times$ 1.5 $\times$ 1.5 mm$^3$ resolution and modulated to conserve the global tissue volumes after normalization.
-The resulting grey matter density maps are distributed at 3D NIfTI files (.nii).
-
-\subsubsection{Quality Assessment}
+\subsubsection{Quality Control}
 Stringent quality control was not applied to the data in order to accommodate different opinions on what constitutes poor quality data.
@@
 \subsection{NIAK Pipeline}
+The NIAK\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}} is a collection of workflows composed of generic medical image processing modules, the MINC tools\footnote{\url{http://en.wikibooks.org/wiki/MINC}}, as well as original Matlab/Octave scripts.
+Multiple stages of processing are assembled into workflows using the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
+The NIAK verion 0.6.4.1 pipeline was run on a server of the Canadian Brain Imaging Research Platform, CBRAIN \cite{sherif2014cbrain}.
+The NIAK is distributed as an open-source software under MIT license and the code is available on NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=411}} and Github\footnote{\url{https://github.com/SIMEXP/niak}}.
+The processing scripts for ADHD200 are available on github\footnote{\url{https://github.com/SIMEXP/Projects/tree/master/adhd200}}.
+The log files for execution were included with the derivatives and can be accessed through the PSOM interface\footnote{\url{http://psom.simexp-lab.org/how_to_use_psom.html}}.
 
-Both the Athena and NIAK pipelines released denoised rs-fMRI volumes resampled into a reference, stereotaxic space (variants of the MNI template) as compressed 4D NIfTI files (.nii.gz).
-Transformations from native to stereotaxic space for each dataset were released in separate files, in FSL wrap .nii.gz file for Athena and in .xfm/.mnc MINC wrap files for NIAK.
-In addition, ancillary files such as the estimated rigid-body motion parameters (AFNI .1D tab-separated values for Athena, and HDF5 files .mat files for NIAK), mean functional image (.nii.gz files) as well as individual and group brain masks (.nii.gz) were released in separate archives.
+\subsubsection{Structural processing} The NIAK implements a variant of the CIVET pipeline \cite{ad2006civet}.
+Each individal s-MRI scan was first corrected for intensity non-uniformities \cite{sled1998nonparametric} and the brain was extracted using a region growing algorithm \cite{park2009skull}.
+Individual scans were then registered linearly (9 parameters) with the T1 MNI symmetric template \cite{fonov2011unbiased}, restricted to the brain with the previous mask.
+Note that, by selecting a symmetric template, it is possible to study functional connectivity between homotopic regions by simply flipping the $x$ axis in stereotaxic space.
+The s-MRI scans wre corrected again for intensity non-uniformities in stereotaxic space, this time restricted to the template brain mask.
+An individual brain mask was extracted a second time on this improved image \cite{park2009skull} and combined with template priors.
+Finally, an iterative non-linear registration on the template space was estimated, restricted to the brain mask \cite{collins1994automatic}.
+A final brain mask of the T1 image in native space was extracted from the template brain mask by inverting the linear and non-linear transformation.
+This final mask was used for registration between rs-fMRI and sMRI data (see below).
+\emph{Shared s-MRI outputs include:} non-uniformity corrected T1 volumes in native and stereotaxic space (after linear or non-linear transformations) at 1 mm isotropic resolution, brain masks in all spaces, as well as the linear and non-linear transformations from native to template space, as .xfm MINC files.
 
-% Following paragraph is unclear regarding specific references to Athena: (to be updated)
-\paragraph{The NIAK pipeline} The preprocessing steps in NIAK followed those of the Athena pipeline with differences at the following steps: (1) Only the first three volumes were suppressed, instead of four.
-(4) Although both Athena and NIAK used the MNI non-linear stereotaxic template space described in \citep{fonov2011unbiased}, the NIAK used the young adult (ICBM152) symmetric variant, while Athena used the NIHPD asymmetric pediatric template (4.5 y.o.-18.5 y.o.).
-(5) The fMRI volumes were resampled in stereotaxic space at 3 mm isotropic (instead of 4 mm), and this was done only right before spatial smoothing (step 5 was moved before step 8).
-(6) No regression of confounds was performed.
-Instead, a physiological noise correction based on automatic labeling of ICA components was implemented \citep{perlbarg2007corsica} after temporal filtering (steps 6 and 7 were inverted).
-(7) Only a high-pass filter was implemented ($0.01$ Hz $< f$), instead of a band-pass.
+\subsubsection{Functional processing}
 
-\subsection{Regional time series} Regional time series were extracted based on a series of different brain parcellations.
-The NIAK pipeline only used functional parcels generated by a region growing method \cite{bellec2006identification} with two resolutions: 954 and 2843 parcels.
-The  NIAK distributed them as HDF5 files (.mat Matlab).
-All brain parcellations were also released as compressed NIfTI files (.nii.gz).
-\paragraph{Anatomical parcellations} For both Athena and NIAK, regional time series were extracted by averaging preprocessed resting-state volumes within different brain parcels.
-The Athena pipeline first used a series of parcellations delineated on the basis of anatomical landmarks:
+\paragraph{Preprocessing} The NIAK rs-fMRI pipeline involved removing the first three volumes to allow for magnetization to reach equilibrium, site-specific slice timing correction to the middle slice, and estimating the parameters of a rigid-body motion between each time frame and the median volume of a run, followed by spatial resampling across frames.
+The fMRI time series were then corrected from slow time drifts (high-pass filter with a 0.01 Hz cut-off, using a discrete cosines transform) and physiological noise using an automated labeling of noise components in an individual independent component analysis, ICA \citep{perlbarg2007corsica}.
+Finally, the median volume of one selected fMRI run for each subject was coregistered (restricted to the brain) with a T1 individual scan using Minctracc \cite{collins1994automatic}.
+The fMRI-to-T1 transform and T1-to-stereotaxic (non-linear) transform were combined, and the functional volumes were resampled in the MNI space at a 3 mm isotropic resolution.
+The fMRI volumes were finally spatially smoothed with a 6 mm FWHM Gaussian filter.
+\emph{Shared rs-fMRI outputs include:} denoised rs-fMRI volumes in MNI space (compressed 4D NIfTIs, nii.gz), the mean / standard deviation rs-fMRI volumes and brain mask in native and template space (.nii.gz), six parameter head motion traces (HDF5 .mat files) as well as individual ICA reports (.pdf).
 
-\paragraph{The ROI1000 and ROI3000 functional parcellations} A region-growing algorithm \citep{bellec2006identification} based on the iterative merging of mutual-nearest-neighbours was implemented to generate functional brain parcellations.
+\paragraph{Time series for functionally defined regions} A region-growing algorithm \citep{bellec2006identification} based on the iterative merging of mutual-nearest-neighbours was implemented to generate functional brain parcellations.
 The spatial dimension was selected arbitrarily by setting the size where the growing process stopped, measured in mm$^3$.
-Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting into roughly 1000 and 3000 ROIs covering the grey matter.
-The regions were built to maximize the average correlation between the time series associated with any pair of voxels of the region.
-The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance) at the KKI site (training data only), such that the homogeneity was maximized on average for all subjects, and the small homogeneous regions were identical for all subjects.
+Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting into the so-called ROI1000 and ROI3000 parcellations, featuring roughly 1000 and 3000 ROIs covering the grey matter, respectively.
+The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance) at the KKI site (training data only).
+The homogeneity was thus maximized on average for all subjects, and the regions were identical for all subjects.
 Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{tzourio2002automated}.
+The average time series for each ROI were extracted for both parcellations and are distributed in individual HDF5 (.mat) files.
+The ROI1000 and ROI3000 parcellations are also available as compressed 3D NIfTI files (.nii.gz).
 
@@
 
-Both the Athena and NIAK pipelines generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset.
-The output of the Burner pipeline were visually inspected by Dr Chu.
-The individual results of the NIAK pipeline were visually reviewed by M.
-Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space.
-The conclusions of the NIAK quality control procedure are available on NITRC\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+The NIAK pipeline generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset, which are available in a comma separated value table (.csv).
+The maximum changes in translation and rotation were inspected and subjects were categorized according to minimal (<1mm or degree), moderate (2 to 3 mm or degrees) and severe motion (>3 mm or degrees).
+The average structural and functional scans after linear and non-linear transformations, as well as the average of all anatomical and functional brain masks are available for each site of the training and test samples \cite{lavoie2012integration}.
+The individual results of the NIAK pipeline were visually inspected by M.
+Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space, as well as for common artefacts such as ghosting and important signal loss.
+When substandard registration outcomes were identified, the parameter of the correction for s-MRI non-uniformities was adjusted and the analysis was repeated until the coregistration results were satisfactory.
+The results of the visual quality control, as well as statistics for the amplitude of motion for all sites are available on NITRC\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
 
@@
 
-Table~\ref{tab_parcellations} summarizes the characteristics of the parcellations, which were also presented in Figure~\ref{fig_parcellations}.
+%Table~\ref{tab_parcellations} summarizes the characteristics of the parcellations, which were also presented in Figure~\ref{fig:parcels}.
 
@@
 Hopefully, the presence of multiple pipelines will enable researchers to compare the robustness of their tools or analysis results to different processing choices.
-It isn't clear which of the parcellations provide the optimal time series, although there is growing consensus that functionally-defined brain regions represent the brain's intrinsic connectivity better than structurally-defined atlases \cite{craddock2012whole, Blumensath2013, thirion2014}.
+It isn't clear which of the parcellations provide the optimal time series, although there is growing consensus that functionally-defined brain regions represent the brain's intrinsic connectivity better than structurally-defined parcellations \cite{craddock2012whole, Blumensath2013, thirion2014}.
 Similarly, it isn't clear which scale of parcellation is optimal.
-While smaller parcels tend to be better at representing connectivity present at the voxel-scale \cite{bellec2006identification, craddock2012whole, thirion2014}, fewer parcels may be more manageable for the specific analysis at hand.
+While smaller parcels tend to be better at representing connectivity present at the voxel-scale \cite{bellec2006identification, craddock2012whole, thirion2014}, fewer parcels may be more manageable or adapted for specific algorithms \cite[e.g.]{michel2012supervised,bellec2015impact}.
 % DM: Should we also mention the degrees of freedom issue here in addition to the point regarding 'manageability'? 
+% PB: agreed, I added "adapted"
+\section{Conclusions}
 
-\section{Lessons learned and future work}
-
-The ADHD-200 Preprocessed initiative was successful in its primary objective: the data repository was effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
+The ADHD-200 Preprocessed initiative was successful in its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
 The resource also expanded the boundaries of the traditional neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
@@
 
-Our conclusions are more mitigated regarding the secondary objective of ADHD-200 Preprocessed, which was to cater to multiple data processing philosophies.
+%Our conclusions are more mitigated regarding the secondary objective of ADHD-200 Preprocessed, which was to cater to multiple data processing philosophies.
 The release has been a success in the sense that almost all variants of processing strategies included in the ADHD-200 Preprocessed repository have been used in follow-up publications.
@@
 This lack of harmonization was essentially driven by the tight deadline for data release imposed by the competition, rather than a design choice.
-We have since concluded that it would be preferable to build the processing pipelines on a common stereotaxic space (and possibly sets of registration)
-% 'sets of registration' is unclear. Perhaps: 'sets of template registration spaces'
-, so that the various noise reduction strategies can be more readily compared.
+We have since concluded that it would be preferable to build the processing pipelines on a common stereotaxic space (and possibly sets of registration),
+% 'sets of registration' is unclear. Perhaps: 'sets of template registration spaces' so that the various noise reduction strategies can be more readily compared.
 
 The impact of the ADHD-200 Preprocessed repository demonstrated the need for reducing computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
-This need is further emphasized by a recent survey of INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
-% CC: Should we include stats or remove?
 We do not plan to expand or update the ADHD-200 Preprocessed release as such, which we hope will continue to serve as a legacy benchmark dataset.
@@
 Our hope is that ADHD-200 Preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.
+
+%This need is further emphasized by a recent survey of INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
+% CC: Should we include stats or remove?
 
@@
 
-\bibliography{ADHD-200_pubs}
+%\bibliography{ADHD-200_pubs}
+\bibliography{adhd200_pubs}
 \end{document}

### 2015-12-25 Bellec_ADHD200_2016.tex
pierre's latest changes

@@
 The AAL parcellation distributed with the SPM8 version of the AAL Toolbox\footnote{\url{http://www.cyceron.fr/index.php/en/plateforme-en/freeware}} and the TT parcellation distributed with AFNI were coregistered and warped into template space.
-Each of the anatomical templates were resampled into the functional space using nearest-neighbor interpolation.
+Each of the structural parcellations were resampled into the functional space using nearest-neighbor interpolation.
 The average time series within each parcel were extracted from both the filtered and unfiltered data and are distributed in tab-separated values format (AFNI .1D).
@@
 \hline
-AAL	    & anatomical &  116 &  16726 & 11896 &  768 & 55552\\
-EZ	    & anatomical &  116 &  15880 & 11059 & 1344 & 52608\\
-HO	    & anatomical &  111 &  14540 & 15342 &   64 & 99200\\
-TT	    & anatomical & 	 97 &  17106 & 16164 &   64 & 70400\\
+AAL	    & structural &  116 &  16726 & 11896 &  768 & 55552\\
+EZ	    & structural &  116 &  15880 & 11059 & 1344 & 52608\\
+HO	    & structural &  111 &  14540 & 15342 &   64 & 99200\\
+TT	    & structural & 	 97 &  17106 & 16164 &   64 & 70400\\
 CC200   & functional &  190 &  11351 &  2001 & 2880 & 17856\\

### 2015-12-25 Bellec_ADHD200_2016.tex
cc changes 12-14

--- 2015-12-24 Bellec_ADHD200_2016.tex
@@
 \usepackage{rotating}
+\usepackage[colorinlistoftodos]{todonotes}
 
@@
 %% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
+\usepackage{lineno}
 
@@
 \title{The Neuro Bureau ADHD-200 Preprocessed Repository}
-
-% - CC - What about just sticking to the name of the repository? The experiment
-% part might make people think that is not an ongoing data sharing initiative.
-% We are sharing more that just the statistical derivatives and
-% we are also sharing processed structural MRI. I think that capturing all of that
-% in a subtitle would be too long.
-% - PB - Agreed, it's a cool title.
-
-% The ADHD-200 Preprocessed experiment: lowering the barriers to a neuroimaging competition
-% The ADHD-200 Preprocessed Repository:\Openly sharing preprocessed data and derivatives
 
@@
 
-% PB -> CC: the following information is redundant with the rest of the paper. It's also not introductory material. As the paper is short, I would tend to avoid repetition.
-
-% The results from the pipelines are shared on the Neuro Bureau project page at the Neuroimaging Informatics Tools and Resources Clearinghouse (NITRC)\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}.
-The data was used by several teams who competed in the ADHD-200 Global Competition, including the winning entry by a group of biostaticians with limited prior neuroimaging experience \cite{Eloyan2012}.
-The initiative has had an significant impact beyond the competition, having been used in 49 publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} in just over 3 years, with more in press or under review.
-
 \section{Organization and access to the repository}
@@
 No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account.
-This registration enables downloads to be tracked for usage statistics.
-Registered users can also be contacted in the event that errors are found in the dataset.
+This registration enables downloads to be tracked for usage statistics users to be contacted in the event that errors are found in the dataset.
 The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/ADHD-200/}}.
@@
 \tightlist
-    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner})
+    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner} \todo{ in figure Sagittal slices are different sizes?})
     \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK
@@
 
-% PB->CC I did the breakdown by derivatives, not by pipeline.
-Otherwise there is too much repetition between NIAK and Athena.
-This is true for content description but even more for the methods section, where it's nice for example to have the different approaches for generating parcellations under one section, rather than disjointed into two "Athena" and "NIAK" sections.
-I've also left the details of the methods (e.g.
-resolution for resampling) to the methods section.
-
-% I understand, but I am not sure that the repetition is bad.
-From my understanding, since this is essentially a data paper, we need to be very explicit about what data is available.
-the way it was before missed alot of useful details, i haven't removed your original content yet, just experimenting with an alternative approach.
-I would actually prefer it if we could put it into a table, but since what is available varies so much by pipeline, it would be a very lopsided table.
-Also, since most of the derivatives are pipeline specific, you are essentially breaking them down by derivatives.
-I think it would be better if the processing and 'contents' sections were merged.
-
 \begin{figure}[!t]
@@
   \caption{Grey matter density maps generated by the Burner pipeline.
-An example of an individual map is presented, along with the average and standard deviation maps for all subjects in the test subsample of ADHD-200 Preprocessed.}
+An example of an individual map is presented, along with the average and standard deviation maps for all subjects in the test subsample of ADHD-200 Preprocessed.
+}
   \label{fig:burner}
@@
 This matrix was further binarized by retaining connections with an average correlation larger than 0.3.
-The resulting binary adjacency matrices have been represented with an automated layout generated by the Yfan Hu's multilevel algorithm, as implemented in the Gephi software \cite{bastian2009gephi}, \url{https://gephi.org/}.
+The resulting binary adjacency matrices have been represented with an automated layout generated by Yfan Hu's multilevel algorithm, as implemented in the Gephi software \cite{bastian2009gephi}.
 The size and color of each node was set proportional to its degree, relative to the min and max inside the graph.}
@@
 \end{figure}
+
+%git@github.com:ccraddock/network_diff_v6.git
 
@@
 
-\subsubsection{Structural processing} Athena's s-MRI pipeline began with skull-stripping the images to remove non-brain tissue and background from the images \cite{smith2002_bet} and segmenting the results into white matter (WM), cerebro-spinal fluid (CSF), and grey matter (GM) probability maps \cite{zhang2001_fast}.
+\subsubsection{Structural processing} Athena's s-MRI pipeline began with skull-stripping to remove non-brain tissue and background from the images \cite{smith2002_bet} and segmenting the results into white matter (WM), cerebro-spinal fluid (CSF), and grey matter (GM) probability maps \cite{zhang2001_fast}.
 A non-linear warp was calculated between the skull-off image and MNI space as represented by the NIHPD 4.5\textendash18.5y age-specific assymmetric template \cite{fonov2011unbiased} using a two step procedure that calculates a linear transform \cite{jenkinson2002_flirt} that is subsequently refined by a non-linear registration procedure \cite{andersson2007non}.
@@
 
-No specific quality control was applied to Athena data before release.
-This decision was taken to accommodate for differing opinions as to what might qualify as usable data.
-In addition to files containing the six motion parameters for each rs-fMRI dataset, and anatomical and mean EPI images in template space, which can be visually inspected to determine high motion data or poor registrations, quality metrics derived from structural data, GM masks, mean EPI images, fALFF maps and FC maps were included to help with the QC process.
-% possibly cut previous sentence into smaller portions for clarity.
+With the exception of a few datasets that were missing data, and one dataset that was corrupted, all of the ADHD-200 Sample was processed and released by Athena, regardless of data quality.
+This was done to accomodate differing opinions as to what qualifies as usable data, and to provide poor quality data that may be used by others to develop methods that are robust to noise.
+Files containing the six mostion parameters for each rs-fMRI data and anatomical and mean EPI images in template space have been included in the release to enable users to determine high-motion data or poor registrations.
+Additional quality metrics derived from the s-MRI, GM masks, mean rs-fMRI images, fALFF maps and FC maps were also included to help with the QC process.
+
 For each data type a mean and standard deviation image was calculated from all of the scans from all of the subjects.
@@
 \subsection{NIAK Pipeline}
-The NIAK\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}} is a collection of workflows composed of generic medical image processing modules, the MINC tools\footnote{\url{http://en.wikibooks.org/wiki/MINC}}, as well as original Matlab/Octave scripts.
-Multiple stages of processing are assembled into workflows using the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}.
-The NIAK verion 0.6.4.1 pipeline was run on a server of the Canadian Brain Imaging Research Platform, CBRAIN \cite{sherif2014cbrain}.
+The NIAK\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}} is a collection of workflows, implemented in the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}, that perform s-MRI and rs-fMRI processing using a combination of generic medical image processing modules, the MINC tools\footnote{\url{http://en.wikibooks.org/wiki/MINC}}, and custom Matlab/Octave scripts.
+The ADHD-200 Sample was processing using NIAK version 0.6.4.1, running on a server of the Canadian Brain Imaging Research Platform (CBRAIN) \cite{sherif2014cbrain}.
 The NIAK is distributed as an open-source software under MIT license and the code is available on NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=411}} and Github\footnote{\url{https://github.com/SIMEXP/niak}}.
@@
 Each individal s-MRI scan was first corrected for intensity non-uniformities \cite{sled1998nonparametric} and the brain was extracted using a region growing algorithm \cite{park2009skull}.
-Individual scans were then registered linearly (9 parameters) with the T1 MNI symmetric template \cite{fonov2011unbiased}, restricted to the brain with the previous mask.
-Note that, by selecting a symmetric template, it is possible to study functional connectivity between homotopic regions by simply flipping the $x$ axis in stereotaxic space.
-The s-MRI scans wre corrected again for intensity non-uniformities in stereotaxic space, this time restricted to the template brain mask.
+Individual scans were then linearly registered (9 parameters) with the T1 MNI symmetric template \cite{fonov2011unbiased}, restricted to the brain with the previous mask.
+Note that, by selecting a symmetric template, it is possible to study functional connectivity between homotopic regions by simply flipping the $x$ axis in stereotaxic space, e.g.
+\cite{VMHCpap}.
+The s-MRI scans were again corrected for intensity non-uniformities in stereotaxic space, this time restricted to the template brain mask.
 An individual brain mask was extracted a second time on this improved image \cite{park2009skull} and combined with template priors.
-Finally, an iterative non-linear registration on the template space was estimated, restricted to the brain mask \cite{collins1994automatic}.
+An iterative non-linear registration was estimated between the linearly registered s-MRI and the template space, restricted to the brain mask \cite{collins1994automatic}.
 A final brain mask of the T1 image in native space was extracted from the template brain mask by inverting the linear and non-linear transformation.
 This final mask was used for registration between rs-fMRI and sMRI data (see below).
-\emph{Shared s-MRI outputs include:} non-uniformity corrected T1 volumes in native and stereotaxic space (after linear or non-linear transformations) at 1 mm isotropic resolution, brain masks in all spaces, as well as the linear and non-linear transformations from native to template space, as .xfm MINC files.
+\emph{Shared s-MRI outputs include:} non-uniformity corrected T1 volumes in native and stereotaxic space (after linear or non-linear transformations) at 1 mm isotropic resolution and brain masks in all spaces, in compressed NIFTI format (.nii.gz), as well as the linear and non-linear transformations from native to template space, as .xfm MINC files.
 
@@
 The fMRI time series were then corrected from slow time drifts (high-pass filter with a 0.01 Hz cut-off, using a discrete cosines transform) and physiological noise using an automated labeling of noise components in an individual independent component analysis, ICA \citep{perlbarg2007corsica}.
-Finally, the median volume of one selected fMRI run for each subject was coregistered (restricted to the brain) with a T1 individual scan using Minctracc \cite{collins1994automatic}.
-The fMRI-to-T1 transform and T1-to-stereotaxic (non-linear) transform were combined, and the functional volumes were resampled in the MNI space at a 3 mm isotropic resolution.
-The fMRI volumes were finally spatially smoothed with a 6 mm FWHM Gaussian filter.
+Finally, the median volume of one selected fMRI run for each subject was coregistered (restricted to the brain) with the corresponding s-MRI scan using Minctracc \cite{collins1994automatic}.
+The rs-fMRI to s-MRI transform and s-MRI to template (non-linear) transform were combined to resample the rs-fMRI volumes into MNI space at a 3 mm isotropic resolution and the results were spatially smoothed with a 6 mm FWHM Gaussian filter.
 \emph{Shared rs-fMRI outputs include:} denoised rs-fMRI volumes in MNI space (compressed 4D NIfTIs, nii.gz), the mean / standard deviation rs-fMRI volumes and brain mask in native and template space (.nii.gz), six parameter head motion traces (HDF5 .mat files) as well as individual ICA reports (.pdf).
@@
 \paragraph{Time series for functionally defined regions} A region-growing algorithm \citep{bellec2006identification} based on the iterative merging of mutual-nearest-neighbours was implemented to generate functional brain parcellations.
-The spatial dimension was selected arbitrarily by setting the size where the growing process stopped, measured in mm$^3$.
-Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting into the so-called ROI1000 and ROI3000 parcellations, featuring roughly 1000 and 3000 ROIs covering the grey matter, respectively.
-The region growing was applied on the time series concatenated across all subjects (after correction to zero mean and unit variance) at the KKI site (training data only).
-The homogeneity was thus maximized on average for all subjects, and the regions were identical for all subjects.
-Because of the temporal concatenation of time series, we had to limit the memory demand, and the region-growing was thus applied independently in each of the 116 areas of the AAL template \citep{tzourio2002automated}.
+The spatial dimension was selected arbitrarily by specifying the size where the growing process should stop, measured in mm$^3$.
+Two parameters (1000 mm$^3$ and 330 mm$^3$) were selected, resulting in the ROI1000 and ROI3000 parcellations, which include roughly 1000 and 3000 ROIs covering the grey matter, respectively.
+The region growing was applied on the time series concatenated across all participant's rs-fMRI data (after correction to zero mean and unit variance) from the KKI site (training data only).
+The homogeneity of regions was thus maximized on average for all subjects, and the regions were identical for all subjects.
+To limit the amount of memory required by the region-growing procedure, it was applied seperatedly in each of the 116 areas of the AAL template \citep{tzourio2002automated}.
 The average time series for each ROI were extracted for both parcellations and are distributed in individual HDF5 (.mat) files.
@@
 
-% The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo.
-
-%Details on the NIAK pipeline can be found on the NITRC website.
-
-% http://www.nitrc.org/plugins/mwiki/index.php/niak:FmriPreprocessing064#Summary_of_the_pipeline
-
 \subsubsection{Quality control}
 
-The NIAK pipeline generated the maximum change in translation and rotation for the rigid motion parameters estimated for each rs-fMRI dataset, which are available in a comma separated value table (.csv).
-The maximum changes in translation and rotation were inspected and subjects were categorized according to minimal (<1mm or degree), moderate (2 to 3 mm or degrees) and severe motion (>3 mm or degrees).
-The average structural and functional scans after linear and non-linear transformations, as well as the average of all anatomical and functional brain masks are available for each site of the training and test samples \cite{lavoie2012integration}.
+Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality calls, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal (<1mm or degree), moderate (2 to 3 mm or degrees) or severe motion (>3 mm or degrees).
 The individual results of the NIAK pipeline were visually inspected by M.
-Chouinard-Decortes for quality of the registration of fMRI and sMRI data as well as registration of sMRI data in stereotaxic space, as well as for common artefacts such as ghosting and important signal loss.
-When substandard registration outcomes were identified, the parameter of the correction for s-MRI non-uniformities was adjusted and the analysis was repeated until the coregistration results were satisfactory.
-The results of the visual quality control, as well as statistics for the amplitude of motion for all sites are available on NITRC\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+Chouinard-Decortes for quality of the registration between rs-fMRI and s-MRI data, registration of s-MRI data to template space, and for common artefacts such as ghosting and signal loss.
+When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory.
+To aid in further quality control, the motion statistics are distributed in comma-seperated values format (.csv) for each cite\todo{PB, please verify this}.
+Additionally the average structural and functional scans after linear and non-linear transformations and the average of all anatomical and functional brain masks for each site of the training and test samples are included as compressed nifti format (.nii.gz)\cite{lavoie2012integration}.
 
@@
 \label{tab_parcellations}
-\caption{Summary of the characteristics of all brain parcellations used in the ADHD-200 Preprocessed release. All reported size for the parcels are measured in mm$^3$.}
+\caption{{\bf Summary of the characteristics of all brain parcellations used in the ADHD-200 Preprocessed release.} Sizes for the parcels are reported in mm$^3$.}
 \begin{tabular}{llrrrrr}
@@
 \end{table}
-
-% PB - @CC: I found a mismatch between the # of ROIs for AAL, EZ, HO and TT from my own extraction and the NITRC table. Any idea why?
-% I suspect you eliminated small regions (HO, TT and CC400 have regions with only one voxel). But I am deriving the stats from the NIfTI files 
-% shipped with the release so I also want to be consistent with what people get. 
-%
-% CC - @PB: I think that these 1 voxel clusters are errors introduced when downsampling the data to the resolution of the functional data.
 
@@
 
-% CC-@PB please include any citations to your work that you think help in the talk of parcellations
 Beyond personal ideology, or the availability of particular features, there is no clear reason to prefer one pipeline over the other.
@@
 While smaller parcels tend to be better at representing connectivity present at the voxel-scale \cite{bellec2006identification, craddock2012whole, thirion2014}, fewer parcels may be more manageable or adapted for specific algorithms \cite[e.g.]{michel2012supervised,bellec2015impact}.
-% DM: Should we also mention the degrees of freedom issue here in addition to the point regarding 'manageability'? 
-% PB: agreed, I added "adapted"
+
 \section{Conclusions}
 
-The ADHD-200 Preprocessed initiative was successful in its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2013, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
+The ADHD-200 Preprocessed initiative was successful in its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
 The resource also expanded the boundaries of the traditional neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
 In particular, the winning team of the ADHD-200 Global Competition was based at the Johns Hopkins Biostatistics Department and used ADHD-200 Preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
-
-%Our conclusions are more mitigated regarding the secondary objective of ADHD-200 Preprocessed, which was to cater to multiple data processing philosophies.
-The release has been a success in the sense that almost all variants of processing strategies included in the ADHD-200 Preprocessed repository have been used in follow-up publications.
-However, we are not aware of a publication that has performed direct comparisons between processing techniques.
-With the approach we took, any direct comparison between Athena and NIAK was difficult to interpret, as the two pipelines did not use the same specific stereotaxic space, varied in many ways in terms of selected parameters, and also had quite different approaches for quality control, derivatives and even packaging the derivatives.
-This lack of harmonization was essentially driven by the tight deadline for data release imposed by the competition, rather than a design choice.
-We have since concluded that it would be preferable to build the processing pipelines on a common stereotaxic space (and possibly sets of registration),
-% 'sets of registration' is unclear. Perhaps: 'sets of template registration spaces' so that the various noise reduction strategies can be more readily compared.
 
@@
 
-%This need is further emphasized by a recent survey of INDI users in which 70\% of the respondents indicated that the availability of statistical derivatives is either very important or absolutely critical to the neuroimaging community.
-% CC: Should we include stats or remove?
-
-%% Usage of \cite is as follows:
-%%   \cite{key}         ==>>  [#]
-%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
+\paragraph{Acknowldegements:} The authors would like to thank the ADHD-200 Consortium for assembling and sharing the ADHD-200 Sample and for hosting the ADHD-200 Global competition.
+The Athena would like to thank the developers of AFNI and FSL, and the Advanced Research Computing at Virginia Tech for computational support.
+The scripts used to calculate ReHo were generously provided by Dr.
+Xinian Zuo.
+The Burner would like to thank the developers of SPM.
+The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, and the CBRAIN computational infrastructure\todo{Include other acknowledgements}.
 

### 2015-12-28 Bellec_ADHD200_2016.tex
Updates from ShareLaTeX

@@
 \tightlist
-    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner} \todo{ in figure Sagittal slices are different sizes?})
-    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK
-    \item Average time series for brain regions from structurally defined parcellations -- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
-    \item Average time series for brain regions for regions defined by functional parcellation -- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
-    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) -- Athena (see Figure~\ref{fig:derivatives})
+    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner},
+    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK,
+    \item Average time series for brain regions from structurally defined parcellations -- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes}),
+    \item Average time series for brain regions for regions defined by functional parcellation -- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes}),
+    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) -- Athena (see Figure~\ref{fig:derivatives}).
 \end{itemize}
@@
 The NIAK\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}} is a collection of workflows, implemented in the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}, that perform s-MRI and rs-fMRI processing using a combination of generic medical image processing modules, the MINC tools\footnote{\url{http://en.wikibooks.org/wiki/MINC}}, and custom Matlab/Octave scripts.
-The ADHD-200 Sample was processing using NIAK version 0.6.4.1, running on a server of the Canadian Brain Imaging Research Platform (CBRAIN) \cite{sherif2014cbrain}.
+The ADHD-200 Sample was processed using NIAK version 0.6.4.1, running on a server of the Canadian Brain Imaging Research Platform (CBRAIN) \cite{sherif2014cbrain}.
 The NIAK is distributed as an open-source software under MIT license and the code is available on NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=411}} and Github\footnote{\url{https://github.com/SIMEXP/niak}}.
@@
 When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory.
-To aid in further quality control, the motion statistics are distributed in comma-seperated values format (.csv) for each cite\todo{PB, please verify this}.
+To aid in further quality control, the motion statistics are distributed in comma-seperated values format (.csv) for each site.
 Additionally the average structural and functional scans after linear and non-linear transformations and the average of all anatomical and functional brain masks for each site of the training and test samples are included as compressed nifti format (.nii.gz)\cite{lavoie2012integration}.
@@
 
-\paragraph{Acknowldegements:} The authors would like to thank the ADHD-200 Consortium for assembling and sharing the ADHD-200 Sample and for hosting the ADHD-200 Global competition.
+\paragraph{Acknowldegements} The authors would like to thank the ADHD-200 Consortium for assembling and sharing the ADHD-200 Sample and for hosting the ADHD-200 Global competition.
 The Athena would like to thank the developers of AFNI and FSL, and the Advanced Research Computing at Virginia Tech for computational support.
@@
 The Burner would like to thank the developers of SPM.
-The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, and the CBRAIN computational infrastructure\todo{Include other acknowledgements}.
+The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, and the CBRAIN computational infrastructure.
 

### 2016-05-14 Bellec_ADHD200_2016.tex
Updates from ShareLaTeX
Added Yassine as a co-author.

@@
 \usepackage{rotating}
-\usepackage[colorinlistoftodos]{todonotes}
+%\usepackage[colorinlistoftodos]{todonotes}
 
@@
 
-\author[label0,label1,label4]{Fran\c{c}ois Chouinard-Descorte}
+\author[label0,label1,label4]{Fran\c{c}ois Chouinard-Decorte}
 \address[label4]{Integrated Program in Neuroscience, McGill University, Montreal, CA}
@@
 
-\author[label0,label5]{Daniel S. Margulies}
-\address[label5]{Max Planck Research Group for Neuroanatomy \& Connectivity, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany}
+\author[label0,label1,label5]{Yassine Benhajali}
+\address[label5]{D\'epartement d'Anthropologie, Universit\'e de Montr\'eal, Montr\'eal, CA}
+\ead{yanamarji@gmail.com}
+
+\author[label0,label6]{Daniel S. Margulies}
+\address[label6]{Max Planck Research Group for Neuroanatomy \& Connectivity, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany}
 \ead{margulies@cbs.mpg.de}
 
-\author[label0,lab6,lab7]{R. Cameron Craddock\corref{cor1}}
-\address[lab6]{Computational Neuroimaging Laboratory, Center for Biomedical Imaging and Neuromodulation, Nathan S. Kline Institute for Psychiatric Research, Orangeburg, NY, USA}
-\address[lab7]{Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
+\author[label0,lab7,lab8]{R. Cameron Craddock\corref{cor1}}
+\address[lab7]{Computational Neuroimaging Laboratory, Center for Biomedical Imaging and Neuromodulation, Nathan S. Kline Institute for Psychiatric Research, Orangeburg, NY, USA}
+\address[lab8]{Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
 \ead{ccraddock@nki.rfmh.org}
@@
 %%
-\linenumbers
+%\linenumbers
 

### 2016-05-14 Bellec_ADHD200_2016.tex
Fixed point 7 of reviewer 2 (inproper legend for Figure 1).

@@
 
-In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}.
+In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers, from a variety of analytical backgrounds, to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}.
 The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}.
@@
   \includegraphics[width=0.6\linewidth]{fig_burner}
-  \caption{Grey matter density maps generated by the Burner pipeline.
-An example of an individual map is presented, along with the average and standard deviation maps for all subjects in the test subsample of ADHD-200 Preprocessed.
-}
+  \caption{Average and standard deviation of the grey matter density maps generated by the Burner pipeline, for all subjects in the test subsample of ADHD-200 Preprocessed. }
   \label{fig:burner}

### 2016-05-14 Bellec_ADHD200_2016.tex
A bit of work on the Oxford commas, and fix to point 4 of reviewer 2 (missing "and" l. 31-32).

--- 2016-05-14 Bellec_ADHD200_2016.tex
@@
 The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise.
-These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to high performance computing resources.
+These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods, or access to high performance computing resources.
 Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.
@@
 The ``ADHD-200 Preprocessed'' is a repository of preprocessed rs-fMRI and s-MRI data along with statistical derivatives from the ADHD-200 Sample.
-Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in the toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated.
+Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'', and ``NIAK'') that differed in the toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated.
 The Athena pipeline processed rs-fMRI and s-MRI images using a combination of AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits.
@@
 No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account.
-This registration enables downloads to be tracked for usage statistics users to be contacted in the event that errors are found in the dataset.
+This registration enables downloads to be tracked for usage statistics and users to be contacted in the event that errors are found in the dataset.
 The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/ADHD-200/}}.

### 2016-05-14 Bellec_ADHD200_2016.tex
Added as many "Oxford commas" as I could, as well as extra non-Oxford commas for good measures. Also added Compute Canada in the acknowledgements, as Guillimin was used to generate QC reports and host the sample.

@@
 
-The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis see Table~\ref{part_table}).
+The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis, see Table~\ref{part_table}).
 For each individual, phenotypic data includes sex, age, handedness, ADHD diagnosis (585 TDC, 362 ADHD, 26 unknown), ADHD subtype (ADHD-combined, ADHD-inattentive, ADHD-hyperactive/impulsive), one of three different measures of ADHD severity, one of five measures of intelligence, co-morbid diagnoses, and whether or not they have used medication to treat their symptoms \cite{Milham2012}.
@@
 \subsubsection{Structural processing} Athena's s-MRI pipeline began with skull-stripping to remove non-brain tissue and background from the images \cite{smith2002_bet} and segmenting the results into white matter (WM), cerebro-spinal fluid (CSF), and grey matter (GM) probability maps \cite{zhang2001_fast}.
-A non-linear warp was calculated between the skull-off image and MNI space as represented by the NIHPD 4.5\textendash18.5y age-specific assymmetric template \cite{fonov2011unbiased} using a two step procedure that calculates a linear transform \cite{jenkinson2002_flirt} that is subsequently refined by a non-linear registration procedure \cite{andersson2007non}.
+A non-linear warp was calculated between the skull-off image and MNI space as represented by the NIHPD 4.5\textendash18.5y age-specific assymmetric template \cite{fonov2011unbiased} using a two step procedure that calculates a linear transform \cite{jenkinson2002_flirt}, that is subsequently refined by a non-linear registration procedure \cite{andersson2007non}.
 \emph{Shared s-MRI outputs include:} skull-stripped whole-brain images and smoothed (by a 6 mm FWHM Gaussian) and unsmoothed GM density maps in MNI space at 1$\times$1$\times$1 mm$^3$ resolution, along with the FSL fNIRT non-linear warp, as compressed NIfTI files (.nii.gz).
@@
 The rs-fMRI to s-MRI transform was then combined with the s-MRI to MNI non-linear warp to write the functional data into MNI152 space at $4\times4\times4$ mm$^3$ resolution.
-Mean WM and CSF signals extracted using the masks calculated during s-MRI processing were included along with 6 head motion parameters and a third-order polynomial in voxelwise nuisance regression models to remove variation due to physiological noise, head motion and scanner drifts from the time series\cite{lund2006_nvr,fox2005}.
+Mean WM and CSF signals extracted using the masks calculated during s-MRI processing were included along with 6 head motion parameters and a third-order polynomial in voxelwise nuisance regression models to remove variation due to physiological noise, head motion, and scanner drifts from the time series\cite{lund2006_nvr,fox2005}.
 The resulting denoised time series were band-pass filtered ($0.009$ Hz $< f < 0.08$ Hz) to limit the data to the frequencies implicated in resting state functional connectivity \cite{biswal1995,cordes2001} and then spatially smoothed with a 6 mm FWHM Gaussian filter.
@@
 Each of the structural parcellations were resampled into the functional space using nearest-neighbor interpolation.
-The average time series within each parcel were extracted from both the filtered and unfiltered data and are distributed in tab-separated values format (AFNI .1D).
+The average time series within each parcel were extracted from both the filtered and unfiltered data, and are distributed in tab-separated values format (AFNI .1D).
 Each of the conformed ROI parcellations are available as compressed 3D NIfTI files (.nii.gz).
@@
 This was done to accomodate differing opinions as to what qualifies as usable data, and to provide poor quality data that may be used by others to develop methods that are robust to noise.
-Files containing the six mostion parameters for each rs-fMRI data and anatomical and mean EPI images in template space have been included in the release to enable users to determine high-motion data or poor registrations.
-Additional quality metrics derived from the s-MRI, GM masks, mean rs-fMRI images, fALFF maps and FC maps were also included to help with the QC process.
+Files containing the six motion parameters for each rs-fMRI data and anatomical and mean EPI images in template space have been included in the release to enable users to determine high-motion data or poor registrations.
+Additional quality metrics derived from the s-MRI, GM masks, mean rs-fMRI images, fALFF maps, and FC maps were also included to help with the QC process.
 
@@
 
-Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality calls, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality control reports, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
 Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal (<1mm or degree), moderate (2 to 3 mm or degrees) or severe motion (>3 mm or degrees).
@@
 
-The ADHD-200 Preprocessed initiative was successful in its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013} and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
+The ADHD-200 Preprocessed initiative was successful in its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
 The resource also expanded the boundaries of the traditional neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
@@
 The Burner would like to thank the developers of SPM.
-The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, and the CBRAIN computational infrastructure.
+The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, the CBRAIN computational infrastructure, and the computational resources provided by Compute Canada\footnote{\url{https://computecanada.org/}} and CLUMEQ\footnote{\url{http://www.clumeq.mcgill.ca/}}, which is funded in part by NSERC (MRS), FQRNT, and McGill University.
 

### 2016-05-22 Bellec_ADHD200_2016.tex
Started to address comments by Reviewer 3.

@@
 The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}.
-The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}.
+The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals: 585 typically-developing controls (TDC), 362 ADHD, and 26 whose diagnosis has not been publicly released \cite{Milham2012}.
 Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld.
@@
 The ADHD-200 Preprocessed repository contains preprocessed outputs and derivatives for data from the ADHD-200 Sample, which includes 973 individuals (352 F) between the ages of 7 and 27 aggregated from 17 different studies conducted across 8 different sites (for a breakdown of age and sex by diagnosis, see Table~\ref{part_table}).
-For each individual, phenotypic data includes sex, age, handedness, ADHD diagnosis (585 TDC, 362 ADHD, 26 unknown), ADHD subtype (ADHD-combined, ADHD-inattentive, ADHD-hyperactive/impulsive), one of three different measures of ADHD severity, one of five measures of intelligence, co-morbid diagnoses, and whether or not they have used medication to treat their symptoms \cite{Milham2012}.
+For each individual, phenotypic data includes sex, age, handedness, ADHD diagnosis (585 TDC, 362 ADHD, 26 with diagnosis unavailable), ADHD subtype (ADHD-combined, ADHD-inattentive, ADHD-hyperactive/impulsive), one of three different measures of ADHD severity, one of five measures of intelligence, co-morbid diagnoses, and whether or not they have used medication to treat their symptoms \cite{Milham2012}.
 Imaging data for each individual includes one or more T1-weighted high-resolution s-MRI scan (s-MRI) and one or more rs-fMRI scan.
@@
 \tightlist
-    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner},
+    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner}),
     \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK,
@@
 Files containing the six motion parameters for each rs-fMRI data and anatomical and mean EPI images in template space have been included in the release to enable users to determine high-motion data or poor registrations.
-Additional quality metrics derived from the s-MRI, GM masks, mean rs-fMRI images, fALFF maps, and FC maps were also included to help with the QC process.
-
-For each data type a mean and standard deviation image was calculated from all of the scans from all of the subjects.
+\par
+Additional quality metrics derived from the preprocessed s-MRI, GM masks, mean rs-fMRI images, fALFF maps, and FC maps were also included to help with the QC process.
+For each data type, registered in stereotaxic space,  a mean and standard deviation image was calculated from all of the scans from all of the subjects.
 These images were used to perform a voxelwise z-score transformation on each data type for each subject $z_i = \frac{(v_i-m_i)}{\sigma_i}$.
@@
 Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality control reports, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
-Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal (<1mm or degree), moderate (2 to 3 mm or degrees) or severe motion (>3 mm or degrees).
+Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal ($<$1mm or degree), moderate (2 to 3 mm or degrees) or severe motion ($>$3 mm or degrees).
 The individual results of the NIAK pipeline were visually inspected by M.
@@
 
-The ADHD-200 Sample was originally created to identify rs-fMRI based biomarkers of ADHD; however, the dataset provides ample opportunity for further analyses \cite{craddock2015}.
+In line with the original purpose of the ADHD-200 Global competition, most works derived from the ADHD-200 Preprocessed initiative proposed new machine learning techniques to predict clinical diagnosis in ADHD.
+The most frequently used derivatives have been Athena preprocessed fMRI volumes \citep[e.g.][]{Liang2012,Carmona2015} and Athena regional time series \citep[e.g.][]{Fujita2013,Dey2014}.
+Some works also based their main analysis on the Burner, either in isolation \citep[e.g.][]{Rangarajan2014,Rangarajan2015,Mahanand2013} or in combination with Athena functional derivatives \citep[e.g.][]{Ji2011,Eloyan2012,Olivetti2014}.
+Finally, a few papers utilized the Athena ICA, ReHo and fALFF maps \citep[e.g.][]{Sato2012a} and the NIAK high resolution (either ROI1000 or ROI3000) regional time series in their main analysis \citep[e.g.][]{Ahn2015,Yang2015}.
+Some papers also made a more marginal use of the ADHD200 preprocessed resources than the one listed previously.
+First, several works only re-used the CC200 or CC400 functional brain parcellations \citep[][e.g.]{Dey2012,Dai2012}, and not the ADH200 sample itself.
+\par
+The ADHD-200 sample provides ample opportunity for analyses besides the identification of rs-fMRI based biomarkers of ADHD \cite{craddock2015}.
 With 585 TDC participants between the ages of 7 and 26, and the inclusion of intelligence measures, the ADHD-200 Preprocessed is a valuable resource for mapping developmental trajectories \cite{dosenbach2010, zuo2010, dimartino2014} and other sources of inter-individual variation \cite{kelly2012}.
@@
 In the service of this aim, the ADHD-200 Preprocessed repository has the necessary components to become a benchmark dataset for evaluating new tools as they are proposed.
-
+\par
 The two biggest challenges for using the ADHD-200 Preprocessed data are head motion \cite{power2012, vandijk2012, sattertwhaite2012, fair2012adhd200, yan2013motion, yan2013small} and inter-site variation in the acquisition equipment, parameters, and experimental procedures \cite{Olivetti2012,yan2013std}.
@@
 Including a regressor for acquisition protocol (see Tables~\ref{smri_params_table} and \ref{rsfmri_params_table} for a summary of the different protocols), the average pairwise correlation between all regions in the brain (GCOR) \cite{saad2013gcor}, or the whole-brain average of the feature under inquiry \cite{yan2013std}, have all been shown to be effective for dealing with inter-site variation.
-
+\par
 Beyond personal ideology, or the availability of particular features, there is no clear reason to prefer one pipeline over the other.
@@
 
-\section{Conclusions}
+\section{Discussion and conclusions}
 
-The ADHD-200 Preprocessed initiative was successful in its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Subramanian2013, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Carmona2015a, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and one patent \cite{Dey2013} derived from the release in just over three years, with further publications in press or under review.
-The resource also expanded the boundaries of the traditional neuroimaging community, with several publications in engineering and statistics journals that do not routinely feature neuroimaging applications \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, Chen2015, He2013, Kong2013, Yang2015, Ahn2015}.
+\begin{figure}[!t]
+\begin{center}
+  \includegraphics[]{impact_stats}
+  \caption{Statistics on download and citations of the ADHD200 preprocessed initiative.}
+  \label{fig:usage}
+\end{center}
+\end{figure}
+
+The ADHD-200 Preprocessed initiative was successful in terms of its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and one patent \cite{Dey2013} derived from the release in just over three years.
+Further publications are either in press or under review, and an updated list of publications will be maintained on the Mendeley platform\footnote{\url{https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/}}.
+Although there was clearly a peak in usage around the ADHD-200 Global competition, there has been a sustained ammount of downloads and publications since then, see Figure \ref{fig:usage}, which we take as a demonstration of a long-term interest from the community in this resource.
+\par
+The ADHD-200 preprocessed has helped to expand the boundaries of the traditional neuroimaging community, with several publications in core engineering and statistics journals that do not routinely feature neuroimaging applications, such as Statistica Sinica \citep{Yang2015} or the Journal of the American Statistical Association \citep{Chen2015}, amongst others \citep[e.g.][]{Liang2012, Rangarajan2015, Rangarajan2014, Mahanand2013, Ji2011, Li2015, Li2013, Liu2012, Subramanian2013, Hou2015, Deshpande2015, She2014, He2013, Kong2013, Ahn2015}.
 In particular, the winning team of the ADHD-200 Global Competition was based at the Johns Hopkins Biostatistics Department and used ADHD-200 Preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
-
+We also found interesting that a handful of methodological works used the ADHD-200 Preprocessed sample as one application in a series of benchmarks that could be as varied as positron emission tomography in Alzheimer's disease \citep{Yang2015}, the Yeast gene regulatory network \citep{She2014} or gene expression in brain tissues of patients with HIV-1 associated neurocognitive disorders \citep{Liu2012}.
+This suggests that fully processed samples distributed under easy-to-access formats with minimal licensing could dramatically accelerate the cross-polinization of disciplines.
+\par
 The impact of the ADHD-200 Preprocessed repository demonstrated the need for reducing computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
-We do not plan to expand or update the ADHD-200 Preprocessed release as such, which we hope will continue to serve as a legacy benchmark dataset.
+The ADHD-200 Preprocessed release has contributed and will continue to contribute to respond to that need.
 We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroimaging research.
-Current initiatives include a larger number of alternative analytical workflows as well as a careful harmonization of processing, quality control, and data packaging strategies.
+In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{http://www.nitrc.org/forum/?group_id=383}.
+We are also actively seeking for contributions, notably during brainhack events\citep{Craddock2016}.
+An important current project is the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}} \citep{dimartino2014}.
+This new resource, still under development, will include over 15 different processing strategies for rs-fMRI processing, implemented across 4 different software packages, and 2 different pipelines for structural MRI processing.
+The release will feature an harmonized organization of processed derivatives across packages and extensive quality control.
+We are planning to continue to expand this line on work on other data sources in the near future.
 Our hope is that ADHD-200 Preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.
@@
 \paragraph{Acknowldegements} The authors would like to thank the ADHD-200 Consortium for assembling and sharing the ADHD-200 Sample and for hosting the ADHD-200 Global competition.
-The Athena would like to thank the developers of AFNI and FSL, and the Advanced Research Computing at Virginia Tech for computational support.
+RCC would like to thank the developers of AFNI and FSL, and the Advanced Research Computing at Virginia Tech for computational support.
 The scripts used to calculate ReHo were generously provided by Dr.
 Xinian Zuo.
-The Burner would like to thank the developers of SPM.
-The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, the CBRAIN computational infrastructure, and the computational resources provided by Compute Canada\footnote{\url{https://computecanada.org/}} and CLUMEQ\footnote{\url{http://www.clumeq.mcgill.ca/}}, which is funded in part by NSERC (MRS), FQRNT, and McGill University.
+CC would like to thank the developers of SPM.
+PB would like to thank the developers of MINC tools, the CIVET pipeline, the CBRAIN computational infrastructure, and the computational resources provided by Compute Canada\footnote{\url{https://computecanada.org/}} and CLUMEQ\footnote{\url{http://www.clumeq.mcgill.ca/}}, which is funded in part by NSERC (MRS), FQRNT, and McGill University.
 

### 2016-05-22 Bellec_ADHD200_2016.tex
Bug fix in URL reference.

@@
 We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroimaging research.
-In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{http://www.nitrc.org/forum/?group_id=383}.
+In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{\url{http://www.nitrc.org/forum/?group_id=383}}.
 We are also actively seeking for contributions, notably during brainhack events\citep{Craddock2016}.

### 2016-05-22 Bellec_ADHD200_2016.tex
Finished edits to the discussion. Only very minor points left to address reviews, with the notable exception of working QC inside the text (and finalize release of the QC spreadsheet).

@@
 These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods, or access to high performance computing resources.
-Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.
+Realizing this barrier to entry, the Neuro Bureau, a non-profit organization aimed at facilitating open science grassroots initiatives\footnote{See \url{http://www.neurobureau.org/mission-statement/} for the full mission statement.
+The Neurobureau is a non-profit organization registered in Germany}, prospectively collaborated with all competitors by preprocessing the data and sharing these results.
 
@@
 
-\paragraph{ICN time series and spatial maps} Time series and spatial maps were derived for 10 ICNs that have been found to be consistent across resting-state datasets and a variety of neuroimaging tasks \cite{smith2009correspondence} by applying a modified dual-regression approach \cite{Beckmann2009dualreg} to the unfiltered preprocessed data.
+\paragraph{ICN time series and spatial maps} Time series and spatial maps were derived for 10 group ICNs generated by \cite{smith2009correspondence}, which were found to be consistent across resting-state datasets and a variety of neuroimaging tasks.
+Based on these template ICNs, we applied a modified dual-regression approach \cite{Beckmann2009dualreg} to the unfiltered preprocessed data.
 A spatial multiple regression was first used to extract time series corresponding to each network.
@@
 Note that, by selecting a symmetric template, it is possible to study functional connectivity between homotopic regions by simply flipping the $x$ axis in stereotaxic space, e.g.
-\cite{VMHCpap}.
+\cite{Zuo2010-ec}.
 The s-MRI scans were again corrected for intensity non-uniformities in stereotaxic space, this time restricted to the template brain mask.
@@
 
-In line with the original purpose of the ADHD-200 Global competition, most works derived from the ADHD-200 Preprocessed initiative proposed new machine learning techniques to predict clinical diagnosis in ADHD.
+In line with the original purpose of the ADHD-200 Global competition, most works derived from the ADHD-200 Preprocessed initiative proposed new machine learning techniques and their main application on real data was to predict clinical diagnosis from the ADHD-200 Preprocessed sample.
 The most frequently used derivatives have been Athena preprocessed fMRI volumes \citep[e.g.][]{Liang2012,Carmona2015} and Athena regional time series \citep[e.g.][]{Fujita2013,Dey2014}.
-Some works also based their main analysis on the Burner, either in isolation \citep[e.g.][]{Rangarajan2014,Rangarajan2015,Mahanand2013} or in combination with Athena functional derivatives \citep[e.g.][]{Ji2011,Eloyan2012,Olivetti2014}.
-Finally, a few papers utilized the Athena ICA, ReHo and fALFF maps \citep[e.g.][]{Sato2012a} and the NIAK high resolution (either ROI1000 or ROI3000) regional time series in their main analysis \citep[e.g.][]{Ahn2015,Yang2015}.
-Some papers also made a more marginal use of the ADHD200 preprocessed resources than the one listed previously.
-First, several works only re-used the CC200 or CC400 functional brain parcellations \citep[][e.g.]{Dey2012,Dai2012}, and not the ADH200 sample itself.
+Some works also based their main analysis on the Burner, either in isolation \citep[e.g.][]{Rangarajan2014,Rangarajan2015,Mahanand2013} or in combination with the Athena functional derivatives \citep[e.g.][]{Ji2011,Eloyan2012,Olivetti2014}.
+A few papers utilized the Athena ICA, ReHo and fALFF maps \citep[e.g.][]{Sato2012a} and the NIAK high resolution (either ROI1000 or ROI3000) regional time series in their main analysis \citep[e.g.][]{Ahn2015,Yang2015}.
+Some publications also made a more marginal use of the ADHD-200 Preprocessed repository, by re-using the CC200 or CC400 functional brain parcellations \citep[e.g.][]{Dey2012,Dai2012}, and not the sample itself.
 \par
-The ADHD-200 sample provides ample opportunity for analyses besides the identification of rs-fMRI based biomarkers of ADHD \cite{craddock2015}.
+To the best of our knowledge, no published works have tried to directly compare the results generated by the Athena and NIAK pipeline.
+The two pipelines conceptually implement very similar steps, with key operations including the non-linear volumetric registration of individual structural MRIs in two different variants of the MNI space, and the registration of invidual BOLD and T1 images.
+The most striking difference lied in the reduction of structured noise: the Athena implemented a regression of a battery of nuisance variables (motion parameters, WM and GM signals), while NIAK implemented an automated labeling of structured noise in a spatial ICA \citep{perlbarg2007corsica}.
+The Athena strategy is fairly standard in the rs-fMRI community, while ICA-based noise attenuation techniques are less common.
+The other clear difference lies in the derivatives offered by the two pipelines: Athena featured a more extensive battery of maps and regional time series, while the NIAK included high-resolution (several thousands) brain parcels and associated time series.
+Beyond personal ideology, or the availability of particular features, there is no clear reason to prefer one pipeline over the other.
+It has recently become clear that even subtle variations of processing environments can impact the end-results of processing pipelines \citep{Glatard2015-we}, even when the same processing is replicated.
+We thus believe it is important to check how variable conclusions drawn from MRI data are, depending of the specific software implementation used for processing.
+The NIAK and Athena pipeline will enable researchers to compare the robustness of their tools or analysis results to different processing choices and derivatives.
+\par
+The ADHD-200 Preprocessed sample also provides ample opportunity for analyses besides the identification of rs-fMRI based biomarkers of ADHD \cite{craddock2015}.
 With 585 TDC participants between the ages of 7 and 26, and the inclusion of intelligence measures, the ADHD-200 Preprocessed is a valuable resource for mapping developmental trajectories \cite{dosenbach2010, zuo2010, dimartino2014} and other sources of inter-individual variation \cite{kelly2012}.
@@
 Including a regressor for acquisition protocol (see Tables~\ref{smri_params_table} and \ref{rsfmri_params_table} for a summary of the different protocols), the average pairwise correlation between all regions in the brain (GCOR) \cite{saad2013gcor}, or the whole-brain average of the feature under inquiry \cite{yan2013std}, have all been shown to be effective for dealing with inter-site variation.
-\par
-Beyond personal ideology, or the availability of particular features, there is no clear reason to prefer one pipeline over the other.
-Hopefully, the presence of multiple pipelines will enable researchers to compare the robustness of their tools or analysis results to different processing choices.
-It isn't clear which of the parcellations provide the optimal time series, although there is growing consensus that functionally-defined brain regions represent the brain's intrinsic connectivity better than structurally-defined parcellations \cite{craddock2012whole, Blumensath2013, thirion2014}.
-Similarly, it isn't clear which scale of parcellation is optimal.
-While smaller parcels tend to be better at representing connectivity present at the voxel-scale \cite{bellec2006identification, craddock2012whole, thirion2014}, fewer parcels may be more manageable or adapted for specific algorithms \cite[e.g.]{michel2012supervised,bellec2015impact}.
 
@@
 We also found interesting that a handful of methodological works used the ADHD-200 Preprocessed sample as one application in a series of benchmarks that could be as varied as positron emission tomography in Alzheimer's disease \citep{Yang2015}, the Yeast gene regulatory network \citep{She2014} or gene expression in brain tissues of patients with HIV-1 associated neurocognitive disorders \citep{Liu2012}.
-This suggests that fully processed samples distributed under easy-to-access formats with minimal licensing could dramatically accelerate the cross-polinization of disciplines.
+This suggests that fully processed, easy-to-access samples could dramatically accelerate the cross-polinization of disciplines.
 \par
@@
 In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{\url{http://www.nitrc.org/forum/?group_id=383}}.
-We are also actively seeking for contributions, notably during brainhack events\citep{Craddock2016}.
+We are also actively seeking for contributions, notably during brainhack events\citep{Cameron_Craddock2016-du}.
 An important current project is the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}} \citep{dimartino2014}.

### 2016-05-23 Bellec_ADHD200_2016.tex
Added a description of the visual QC.

@@
 \par
+An online report\footnote{\url{http://simexp.github.io/adhd200_qc_athena/index.html}} of registration quality was generated for all subjects.
+The report includes concurrent visualization of the individual structural images, after non-linear registration, together with the target brain template (MNI pediatric), as well as a concurrent visualization of the individual structural and BOLD images together, again after non-linear registration.
+All these images were visually reviewed, and registration that presented severe misregistration or image quality problems were marked as ``fail'' for QC ($7\%$ failure rate).
+The outcome of the visual quality assessment for registered images has been shared on NITRC in a consolidated tabular-separated (.tsv) spreadsheet that also includes all phenotypic variables.
+The .tsv QC spreadsheet also includes a summary measure of motion amplitude for each dataset, that can be used to exclude subjects above a certain threshold.
+\par
 Additional quality metrics derived from the preprocessed s-MRI, GM masks, mean rs-fMRI images, fALFF maps, and FC maps were also included to help with the QC process.
@@
 
-Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality control reports, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
+Outputs of the NIAK pipeline were subjected to a careful visual inspection and the QC reports, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}.
 Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal ($<$1mm or degree), moderate (2 to 3 mm or degrees) or severe motion ($>$3 mm or degrees).
-The individual results of the NIAK pipeline were visually inspected by M.
-Chouinard-Decortes for quality of the registration between rs-fMRI and s-MRI data, registration of s-MRI data to template space, and for common artefacts such as ghosting and signal loss.
+The individual brain registration of the NIAK pipeline were visually inspected using online QC reports\footnote{\url{simexp.github.io/adhd200_qc_niak/}}, similar to those generated for the Athena pipeline.
 When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory.
-To aid in further quality control, the motion statistics are distributed in comma-seperated values format (.csv) for each site.
-Additionally the average structural and functional scans after linear and non-linear transformations and the average of all anatomical and functional brain masks for each site of the training and test samples are included as compressed nifti format (.nii.gz)\cite{lavoie2012integration}.
-
+Satistfactory results could not be achived with some datasets and have been indicated as ``Fail'' for QC ($5.2\%$ failure rate) in the .tsv spreadsheet including QC assessments, available on NITRC.
 %%%
@@
 
-The ADHD-200 Preprocessed initiative was successful in terms of its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Carmona2015, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and one patent \cite{Dey2013} derived from the release in just over three years.
+The ADHD-200 Preprocessed initiative was successful in terms of its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Subramanian2013, Carmona2015, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and one patent \cite{Dey2013} derived from the release in just over three years.
 Further publications are either in press or under review, and an updated list of publications will be maintained on the Mendeley platform\footnote{\url{https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/}}.

### 2016-05-26 Bellec_ADHD200_2016.tex
Updates from ShareLaTeX

@@
 The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}.
-The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals: 585 typically-developing controls (TDC), 362 ADHD, and 26 whose diagnosis has not been publicly released \cite{Milham2012}.
+The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals: some typically-developing controls (TDC) and patients diagnosed with ADHD \cite{Milham2012}.
 Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld.
@@
 The Athena pipeline\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:AthenaPipeline}} processed rs-fMRI and s-MRI images using a custom BASH script that combined AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits and was run on the Athena computer cluster at Virginia Tech's Advanced Research Computing center\footnote{\url{http://www.arc.vt.edu/}}.
-The processing scripts for each site are distributed in the repository, along with output log files for each processed dataset.
+The processing scripts for each site are distributed in the repository, as well as on Github\footnote{\url{https://github.com/preprocessed-connectomes-project/adhd200_athena_scripts}}, along with output log files for each processed dataset.
 
@@
 The NIAK is distributed as an open-source software under MIT license and the code is available on NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=411}} and Github\footnote{\url{https://github.com/SIMEXP/niak}}.
-The processing scripts for ADHD200 are available on github\footnote{\url{https://github.com/SIMEXP/Projects/tree/master/adhd200}}.
+The processing scripts for ADHD200 are available on github\footnote{\url{https://github.com/preprocessed-connectomes-project/adhd200_niak_scripts}}.
 The log files for execution were included with the derivatives and can be accessed through the PSOM interface\footnote{\url{http://psom.simexp-lab.org/how_to_use_psom.html}}.

### 2016-05-26 responses_reviewers.tex
Response to reviewers.

%% Template Elsevier for Neuroimage

%% Use the option review to obtain double line spacing
%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
\documentclass[authoryear,3p]{elsarticle}
\usepackage{natbib}
\usepackage{amsmath}
%\usepackage{lineno}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\journal{Neuroimage}
%\usepackage{color}

\begin{document}

% Title must be 150 words or less
\begin{frontmatter}
\title{Point-by-point response to the reviews of the manuscript NIMG-15-3295}

\author[label0,label1,label2]{Pierre Bellec\corref{cor1}}
\address[label0]{The Neuro Bureau}
\address[label1]{Centre de Recherche de l'Institut Universitaire de G\'eriatrie de Montr\'eal, Montr\'eal, CA}
\address[label2]{D\'epartement d'Informatique et de Recherche Op\'erationnelle, Universit\'e de Montr\'eal, Montr\'eal, CA}

\cortext[cor1]{Corresponding authors.}

\ead{pierre.bellec@criugm.qc.ca}
\ead[url]{bellec.simexp-lab.org}

\author[label0,label3]{Carlton Chu}
\address[label3]{Google DeepMind, London, UK}
\ead{carltonchu1@gmail.com}

\author[label0,label1,label4]{Fran\c{c}ois Chouinard-Decorte}
\address[label4]{Integrated Program in Neuroscience, McGill University, Montreal, CA}
\ead{francois.chouinard@gmail.com}

\author[label0,label5]{Daniel S. Margulies}
\address[label5]{Max Planck Research Group for Neuroanatomy \& Connectivity, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany}
\ead{margulies@cbs.mpg.de}

\author[label0,lab6,lab7]{R. Cameron Craddock\corref{cor1}}
\address[lab6]{Computational Neuroimaging Laboratory, Center for Biomedical Imaging and Neuromodulation, Nathan S. Kline Institute for Psychiatric Research, Orangeburg, NY, USA}
\address[lab7]{Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
\ead{ccraddock@nki.rfmh.org}
\ead[url]{computational-neuroimaging-lab.org}

\begin{abstract} This is a point-by-point response to the comments of the reviewers for manuscript NIMG-15-3295. We would like to thank both reviewers for their constructive feedback. All changes have been highlighted in the revised manuscript. 
\end{abstract}

\end{frontmatter}

\section{Responses to reviewer 1}

\begin{quote}
$\blacktriangleright$\emph{1. Well, after reading the paper I'd say only one thing: well done. I could follow what you have done, it's described in enough details to be useful - I have therefore only one recommendation for the editor: accept.
Dr Cyril Pernet. }
\end{quote}

Thank you.

\section{Responses to reviewer 2}

\begin{quote}
$\blacktriangleright$\emph{1. The authors document three pre-processing pipelines applied to the ADHD-200 dataset. The work is valuable, and I commend the authors on sharing these pre-processed versions of the ADHD-200 data with the scientific community.} 
\end{quote}

Thank you.

\begin{quote}
$\blacktriangleright$\emph{2. Regarding quality control, the NIAK pipeline output was carefully inspected to ensure that the pipeline itself worked properly. For example, parameter adjustments were made to improve registration in cases where the registration was poor. It appears that similar quality control, focusing on the pipeline performance (not raw data quality), was \emph{not} done for the Athena and Burner pipelines. Is this correct? If so, why not? I do not see any justification for accepting a pre-processing pipeline that might take good raw data and produce bad pre-processed data. The pre-processing pipeline is under the researcher's control, and it should be required to operate correctly. Note that I agree with your decision and reasoning not to exclude poor quality raw data. Raw data quality cannot always be fully controlled by the researcher, and low quality raw data must sometimes be accepted (eg: with difficult participant populations). Please clarify this issue.} 
\end{quote}

The reviewer is correct. In our original release of the ADHD200 preprocessed sample, no systematic visual assessment of brain registration had been implemented for the Athena pipeline. The main reason was the time constraints of the competition. We have implemented a systematic visual review of T1-template and T1-BOLD registrations for both NIAK and Athena, using an assessment protocol that is currently under development\footnote{\url{https://github.com/SIMEXP/niak_manual/raw/master/qc_manual_v1.0/qc_manual_niak.pdf}}. The reports for quality control have been made publicly available for Athena\footnote{\url{http://simexp.github.io/adhd200_qc_athena/index.html}} and NIAK\footnote{\url{http://simexp.github.io/adhd200_qc_niak/index.html}}. We have also released a spreadhseet including the QC status for each dataset, marked either \texttt{Fail}, in the presence of a major issue, or \texttt{Pass}. A subset of 220 subjects was graded independently by two raters, and the Cohen's kappa agreement was high (81\%) between them. The final status of a processed dataset was \texttt{Fail} if it was marked as such by one of the rater. The remaining 745 subjects were graded only once by one of the raters. In total, we evaluated 1165 subjects (accounting for 200 subjects evaluated twice), times 2 modalities, times 2 pipelines, for a grand total of $4740$ visual assessments of coregistration quality. The failure rate for Athena and NIAK were relatively low: 7\% and 5\%, respecively. We are planning to implement a more detailed evaluation of the registration performance as well the quality of raw data in follow up publications.

\begin{quote}
$\blacktriangleright$\emph{3. page 2, line 9: Are the 26 "unknown" subjects from the Brown University site? If so, their diagnoses are known to the researchers who collected those data, but those diagnoses have not been publicly released. It would be clearer to describe these 26 as "diagnoses not publicly released" rather than "unknown". Similarly for page 3, line 46.}
\end{quote}

OK

\begin{quote}
$\blacktriangleright$\emph{4. page 2, lines 31-32: structure error in sentence, missing "and" ?). 
}
\end{quote}

OK

\begin{quote}
$\blacktriangleright$\emph{5. page 3, line 65: missing closing parenthesis}
\end{quote}

OK

\begin{quote}
$\blacktriangleright$\emph{6. Oxford comma used in some places but not others, better style if consistent throughout}
\end{quote}

Fixed.

\begin{quote}
$\blacktriangleright$\emph{7. Figure 1: "An example of an individual map is presented". I do not see a single subject map, just the average and standard deviation maps.}
\end{quote}

Fixed.

\begin{quote}
$\blacktriangleright$\emph{8.  Page 9, line 166: "For each data type a mean and standard deviation image ...": Does each data type mean just {s-MRI, rs-MRI} or does it also include the other derivative images (eg: fALFF maps, etc.)?}
\end{quote}

(CC) I will look over the text and try to clarify, this was done for all of the processed data, and not the raw data.

\begin{quote}
$\blacktriangleright$\emph{9. Page 9, line 166-171: Were the z-score calculations done on the raw data, preprocessed data, or both?}
\end{quote}

?

\begin{quote}
$\blacktriangleright$\emph{10. Page 11, line 260-261: Erroneous symbols (eg: upside down ! and ?)}
\end{quote}

Fixed

\section{Responses to reviewer 3}

\begin{quote}
$\blacktriangleright$\emph{1. The efforts from Neuro Bureau described were extremely important in making the ADHD200 Competition a relative success, as many participants used, at least in part, these intermediate results to assist their work. A large number of publications are reported in the Conclusions section, though it is not immediately apparent to what extent each of these papers hinged on the datasets / intermediate results described here.  It would be very beneficial to provide some additional details (case examples would suffice) on how the data have been used rather than simply providing a bulk citation list. 
}
\end{quote}

We added some case examples.

\begin{quote}
$\blacktriangleright$\emph{2. While the ADHD-200 Preprocessed Repository is of high value, as evidenced by a large number of downloads, there is some concern about the ongoing relevance of this publication, now several years after the initial processing was performed and the ADHD200 challenge was held. The authors state that they have no plans to expand or update the release, and instead only state that they hope it will "continue to serve as a legacy benchmark dataset."  I agree that there is utility in maintaining a benchmark dataset (with multiple publications / results against which new efforts can be compared). However, if this is the goal, then perhaps the authors might also collate and host (alongside the data) some of the benchmark "results" using these methods to make the use of the data for this purpose even easier?  A minimal solution might be including web links from NITRC to results of the ADHD Global Competition, and to papers that used the preprocessed dataset.
}
\end{quote}

Link to the Mendeley library.

\begin{quote}
$\blacktriangleright$\emph{In addition, it would be useful if the authors could provide evidence and further discussion of the long-term relevance of this dataset. For example, how has the number of downloads changed since the ADHD200 Competition ended?  Are the forums still be used?  Are there research groups actively working with these processed data now?}
\end{quote}

Insert and comment new Figure by CC.

\begin{quote}
$\blacktriangleright$\emph{In general, the Discussion ("5. Conclusions") is very light, and it would be helpful to have more of an exposition on the potential forward value of the repository - how unique is it?  How important does it seem to be for ADHD research?  What are the other uses?  Some of this is touched on in Section 4, but a bit more of a forward-looking vision for the repository would be helpful.  Relatedly, do the authors envision any mechanism by which other individuals might add preprocessed results from different processing tools / pipelines to the existing data?
}
\end{quote}

Resurrect the paragraph in the discussion on lessons learned and moving forward.

\begin{quote}
$\blacktriangleright$\emph{5. Additional information could be provided that would be helpful to researchers interested in working with preprocessed results from the repository. In particular, what are the limitations and assumptions of each processing stream?  What are seen as the fundamental differences between the NIAK cleaned rs-fMRI volumes and the Athena volumes? There must have been some justification for providing both, but it is not entirely clear here, other than to say users can decide what they want to use; if one goal is to target non-fMRI scientists, then further explication of these differences would be helpful. It would be even more helpful to provide an explicit comparison between the rs-fMRI data from NIAK and Athena.  Just how similar are the processed rs-fMRI image series?  The authors should also explicitly note the limitations of working with preprocessed data (i.e., results depend somewhat on the particular registration strategy used, etc.), and describe if it is possible for users
to go back to raw data (still available?), modify the processing scripts provided, and obtain new intermediate results since this would seem to be a common use case, especially as new methods are developed.
}
\end{quote}

We added a paragraph in the discussion highlighting some of the key differences in the preprocessing parameters. We also discussed our choices re preprocessing strategies, and how this could be improved. Being an open community initiative, the NeuroBureau welcomes contributions from other groups. The NITRC site includes a discussion forum where any interested contributor can reach out to us. Six groups have contributed to our latest initiative, the ABIDE preprocessed, using this approach. The brainhack meeting series (REF) has also been instrumental to raise awareness and recruit new contributors.

\begin{quote}
$\blacktriangleright$\emph{Some description of the "Neuro Bureau" would be helpful in the introduction - exactly who is this group, and what is their overall mission?
}
\end{quote}

We have added a short summary of the mission statement on Neurobureau.org, along with a link.

\begin{quote}
$\blacktriangleright$\emph{ 7. There is a typo / grammatical error in Section 2 (p. 2) "This registration enables downloads to be tracked for usage statistics users to be contacted..."
}
\end{quote}

Fixed.

\begin{quote}
$\blacktriangleright$\emph{ 
8. There is some redundancy between the description of the contents of the repository (p. 3) and the Introduction (in terms of numbers of subjects, etc.).
}
\end{quote}

?

\begin{quote}
$\blacktriangleright$\emph{ 
9. Why are the NIAK scripts provided on Github, but others provided in NITRC?}
\end{quote}

?

\begin{quote}
$\blacktriangleright$\emph{ 
10. A bit more methodological detail should be provided on the ICN time series and spatial maps (p. 8).  Was the spatial regression based on a set of templates/maps?  Which ones?}
\end{quote}

?

\begin{quote}
$\blacktriangleright$\emph{ 
11. There is a missing citation on page 10 (Section 3.3.1).
}
\end{quote}

Fixed.

\end{document}

### 2016-05-26 responses_reviewers.tex
Updates from ShareLaTeX

@@
 In total, we evaluated 1165 subjects (accounting for 200 subjects evaluated twice), times 2 modalities, times 2 pipelines, for a grand total of $4740$ visual assessments of coregistration quality.
-The failure rate for Athena and NIAK were relatively low: 7\% and 5\%, respecively.
+The failure rate for Athena and NIAK were relatively low: 7\% and 5.2\%, respecively.
 We are planning to implement a more detailed evaluation of the registration performance as well the quality of raw data in follow up publications.
@@
 
-OK
+Fixed (l. XX-XX).
 
@@
 
-Fixed.
+We have edited the document to use the Oxford comma, consistently.
 
@@
 
-Fixed.
+Fixed (l. XX-XX).
 
@@
 
-(CC) I will look over the text and try to clarify, this was done for all of the processed data, and not the raw data.
+It includes all derivatives. The paragraph was edited to clarify this (l. XX-XX).
 
@@
 
-?
+The z-score calculations were done on preprocessed data, registered in stereotaxic space. We edited the paragraph to clarify this (l. XX-XX).
 
@@
 
-Fixed
+Fixed (l.XX-XX).
 
@@
 
-We added some case examples.
+We added a paragraph at the beginning of "usage recommendation" (lines XX-XX) where we describe a few works that used ADHD-200 preprocessed.
+In their vast majority all these publications aimed at predicting clinical labels from brain data, either structurally with Burner or functionally with Athena/NIAK, or both.
+We pointed at different papers based on the derivatives they used.
+In addition, in the discussion (lines XX-XX), we referred to a handful of studies that combined ADHD-200 preprocessed to data samples from unrelated fields to evaluate statistical models, which we see as an important direction enabled by the ADHD-200 preprocessed initiative.
 
@@
 
-Link to the Mendeley library.
+We added a reference in the discussion (l.
+XXX) to the ADHD200 preprocessed Mendeley library (https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/), an online collection of the publications that used the ADHD200.
+This resource is being regularly updated by the laboratory of Dr Craddock.
 
 \begin{quote}
-$\blacktriangleright$\emph{In addition, it would be useful if the authors could provide evidence and further discussion of the long-term relevance of this dataset.
+$\blacktriangleright$\emph{3.
+In addition, it would be useful if the authors could provide evidence and further discussion of the long-term relevance of this dataset.
 For example, how has the number of downloads changed since the ADHD200 Competition ended?
@@
 \end{quote}
+\begin{figure}[!t]
+\begin{center}
+  \includegraphics[width=\linewidth]{impact_stats}
+  \caption{Statistics on download and citations of the ADHD200 preprocessed initiative.}
+  \label{fig:usage}
+\end{center}
+\end{figure}
 
-Insert and comment new Figure by CC.
+Although there was clearly a peak in usage around the ADHD-200 Global competition, there has been a sustained amount of downloads and publications since then, see Figure \ref{fig:usage}, which we take as a demonstration of a long-term interest from the community in this resource.
+We added this point in the discussion (l.
+XX-XX).
 
 \begin{quote}
-$\blacktriangleright$\emph{In general, the Discussion ("5.
+$\blacktriangleright$\emph{4.
+In general, the Discussion ("5.
 Conclusions") is very light, and it would be helpful to have more of an exposition on the potential forward value of the repository - how unique is it?
@@
 
-Resurrect the paragraph in the discussion on lessons learned and moving forward.
+Thanks for the suggestions.
+We have expanded the discussion, as suggested, in two ways.
+First, we better emphasized the type of usage that have appeared in the literature (see our response to point 1 above).
+This helps show how the ADHD-200 prepocessed sample has been used outside of the traditional brain imaging community, and has started to be adopted by researchers doing core statistics, signal processing and machine learning research.
+We believe that to be quite unique and a potentially important development in the field.
+Second, we added a paragraph discussing the value of having two independent processing pipelines availables in the sample, which has not yet been exploited.
+To the best of our knowledge, this is a feature unique to ADHD-200 Preprocessed, which we emphasized in the abstract.
+Third, we have discussed the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}}, which builds on the lessons learned by releasing ADHD-200 Preprocessed.
+In this new release, we were able to include more tools, better quality control, as well as better harmonization of data organization across tools.
+Recruitment of contributions as been implemented openly, notably during public hackathons.
+We have added these points to the discussion (l.
+XX-XX).
 
@@
 
-We added a paragraph in the discussion highlighting some of the key differences in the preprocessing parameters.
+We added a paragraph in the discussion (l.
+XX-XX) highlighting some of the key differences in the preprocessing parameters.
 We also discussed our choices re preprocessing strategies, and how this could be improved.
@@
 Six groups have contributed to our latest initiative, the ABIDE preprocessed, using this approach.
-The brainhack meeting series (REF) has also been instrumental to raise awareness and recruit new contributors.
+The brainhack meeting series (Craddock et al., 2016) has also been instrumental to raise awareness and recruit new contributors.
 
 \begin{quote}
-$\blacktriangleright$\emph{Some description of the "Neuro Bureau" would be helpful in the introduction - exactly who is this group, and what is their overall mission?
+$\blacktriangleright$\emph{6. Some description of the "Neuro Bureau" would be helpful in the introduction - exactly who is this group, and what is their overall mission?
 }
@@
 
-We have added a short summary of the mission statement on Neurobureau.org, along with a link.
+The Neuro Bureau is a non-profit organization registered in Germany and aimed at facilitating open science grassroots initiatives.
+See the following website\footnote{\url{http://www.neurobureau.org/mission-statement/}} for the full mission statement.
+We added these details in the introduction (l.
+XX-XX).
 
@@
 \end{quote}
-
-Fixed.
+Fixed (l. XX).
 
@@
 \end{quote}
-
-?
+We have removed the details on the sample size in terms of clinical category from the introduction, and kept these details in the Section "Contents of the repository".
 
@@
 \end{quote}
-
-?
+Scripts for both releases are now hosted on github. See lines XX and XX.
 
@@
 \end{quote}
-
-?
+The dual regression procedure was implemented based on a template of 10 intrinsic connectivity networks generated using group ICA by Smith and colleagues (PNAS, 2009).
+We modified the text to make this more explicit (l.
+XX-XX).
 
@@
 
-Fixed.
+Fixed (l. XX)
 

### 2016-05-26 Bellec_ADHD200_2016.tex
Updated refs using ADHD200 preproc. Stats are now in line between the text and the graph.

@@
 
-The ADHD-200 Preprocessed initiative was successful in terms of its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 49 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Subramanian2013, Carmona2015, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014}, three PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, three master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and one patent \cite{Dey2013} derived from the release in just over three years.
+The ADHD-200 Preprocessed initiative was successful in terms of its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 52 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Subramanian2013, Carmona2015, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014,nachamai2016sub,Brown20161238,Yu2016,Fujita2015}, 3 PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, 3 master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and 1 patent \cite{Dey2013} derived from the release in just over three years.
 Further publications are either in press or under review, and an updated list of publications will be maintained on the Mendeley platform\footnote{\url{https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/}}.

### 2016-05-26 Bellec_ADHD200_2016.tex
Added links to the "consolidated phenotypics".

@@
 All these images were visually reviewed, and registration that presented severe misregistration or image quality problems were marked as ``fail'' for QC ($7\%$ failure rate).
-The outcome of the visual quality assessment for registered images has been shared on NITRC in a consolidated tabular-separated (.tsv) spreadsheet that also includes all phenotypic variables.
+The outcome of the visual quality assessment for registered images has been shared on NITRC in a consolidated tabular-separated (.tsv) spreadsheet\footnote{\url{https://www.nitrc.org/frs/download.php/9024/adhd200_preprocessed_phenotypics.tsv}} that also includes all phenotypic variables.
 The .tsv QC spreadsheet also includes a summary measure of motion amplitude for each dataset, that can be used to exclude subjects above a certain threshold.
@@
 When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory.
-Satistfactory results could not be achived with some datasets and have been indicated as ``Fail'' for QC ($5.2\%$ failure rate) in the .tsv spreadsheet including QC assessments, available on NITRC.
+Satisfactory results could not be achived with some datasets and have been indicated as ``Fail'' for QC ($5.2\%$ failure rate) in the .tsv spreadsheet including QC assessments, available on NITRC\footnote{\url{https://www.nitrc.org/frs/download.php/9024/adhd200_preprocessed_phenotypics.tsv}}.
 %%%
@@
 We also found interesting that a handful of methodological works used the ADHD-200 Preprocessed sample as one application in a series of benchmarks that could be as varied as positron emission tomography in Alzheimer's disease \citep{Yang2015}, the Yeast gene regulatory network \citep{She2014} or gene expression in brain tissues of patients with HIV-1 associated neurocognitive disorders \citep{Liu2012}.
-This suggests that fully processed, easy-to-access samples could dramatically accelerate the cross-polinization of disciplines.
+This suggests that fully processed, easy-to-access imaging samples could help validate general-purpose methods on a wider scope of applications.
 \par

### 2016-05-28 Bellec_ADHD200_2016.tex
Updates from ShareLaTeX

@@
 
+Images were visually inspected and attempts were made to fix gross misregistration errors by hand adjusting the offending images to center them on the anterior commisure and rotate them into rough correspondence with the MNI template.
 With the exception of a few datasets that were missing data, and one dataset that was corrupted, all of the ADHD-200 Sample was processed and released by Athena, regardless of data quality.
-This was done to accomodate differing opinions as to what qualifies as usable data, and to provide poor quality data that may be used by others to develop methods that are robust to noise.
+This was done to accommodate differing opinions as to what qualifies as usable data, and to provide poor quality data that may be used by others to develop methods that are robust to noise.
 Files containing the six motion parameters for each rs-fMRI data and anatomical and mean EPI images in template space have been included in the release to enable users to determine high-motion data or poor registrations.
 \par
-An online report\footnote{\url{http://simexp.github.io/adhd200_qc_athena/index.html}} of registration quality was generated for all subjects.
-The report includes concurrent visualization of the individual structural images, after non-linear registration, together with the target brain template (MNI pediatric), as well as a concurrent visualization of the individual structural and BOLD images together, again after non-linear registration.
-All these images were visually reviewed, and registration that presented severe misregistration or image quality problems were marked as ``fail'' for QC ($7\%$ failure rate).
-The outcome of the visual quality assessment for registered images has been shared on NITRC in a consolidated tabular-separated (.tsv) spreadsheet\footnote{\url{https://www.nitrc.org/frs/download.php/9024/adhd200_preprocessed_phenotypics.tsv}} that also includes all phenotypic variables.
-The .tsv QC spreadsheet also includes a summary measure of motion amplitude for each dataset, that can be used to exclude subjects above a certain threshold.
+Additional quality metrics derived from the preprocessed s-MRI, GM masks, mean rs-fMRI images, fALFF maps, and FC maps were also included to help with the QC process.
+For each data type a mean and standard deviation image was calculated from all of the scans (in stereotaxic space) from all of the subjects.
+These images were used to perform a voxelwise z-score transformation on each data type for each subject $z_i = \frac{(v_i-m_i)}{\sigma_i}$.
+For each image (or map), the number of these z-scores whose absolute value exceeded 3 where summed to generate a quality score.
+The higher the resulting sum, the larger the number of voxels a image has with $\left|z\right| \geq 3$ and the more likely the images are outliers.
+Using this metric it is possible to rank images for a more directed search for poor quality scans.
+These metrics are distributed in participant-specific text files along with the BASH scripts that implement the procedure.
 \par
-Additional quality metrics derived from the preprocessed s-MRI, GM masks, mean rs-fMRI images, fALFF maps, and FC maps were also included to help with the QC process.
-For each data type, registered in stereotaxic space,  a mean and standard deviation image was calculated from all of the scans from all of the subjects.
-These images were used to perform a voxelwise z-score transformation on each data type for each subject $z_i = \frac{(v_i-m_i)}{\sigma_i}$.
-The absolute values of these z-scores were thresholded at 3, and summed across voxels for a quality score for that image.
-The higher the resulting sum, the larger the number of voxels a image has that are $\geq 3$ and the more likely the images are outliers.
-Using this metric it is possible to rank images, and allows for a more directed search for poor quality scans.
-These metrics are distributed in participant-specific text files along with the BASH scripts that implement the procedure.
+A rigorous visual inspection of registration has also been performed using the same procedures and raters (PB and YB) as the NIAK pipeline.
+The procedure entailed generating an online report\footnote{\url{http://simexp.github.io/adhd200_qc_athena/index.html}} of registration quality for all subjects.
+The report includes a visualization of the individual structural images in standard space overlaid onto the corresponding brain template (MNI pediatric), as well as a visualization of the individual mean EPI image overlaid onto the corresponding structural image, both in standard space.
+These images were visually reviewed, and images with severe misregistraion or quality problems were marked as ``fail'' ($7\%$ failure rate).
+The outcome of the visual quality assessment along with summary measures of motion for the resting state fMRI scans and all other phenotypic variables have been consolidated into a tabular-separated (.tsv) spreadsheet that can be downloaded from NITRC\footnote{\url{https://www.nitrc.org/frs/download.php/9024/adhd200_preprocessed_phenotypics.tsv}}.
 
@@
 
-In line with the original purpose of the ADHD-200 Global competition, most works derived from the ADHD-200 Preprocessed initiative proposed new machine learning techniques and their main application on real data was to predict clinical diagnosis from the ADHD-200 Preprocessed sample.
+In line with the original purpose of the ADHD-200 Global competition, most of the publications that have used the ADHD-200 Preprocessed initiative data have proposed new machine learning techniques for predicting ADHD diagnosis or subtype.
 The most frequently used derivatives have been Athena preprocessed fMRI volumes \citep[e.g.][]{Liang2012,Carmona2015} and Athena regional time series \citep[e.g.][]{Fujita2013,Dey2014}.
-Some works also based their main analysis on the Burner, either in isolation \citep[e.g.][]{Rangarajan2014,Rangarajan2015,Mahanand2013} or in combination with the Athena functional derivatives \citep[e.g.][]{Ji2011,Eloyan2012,Olivetti2014}.
-A few papers utilized the Athena ICA, ReHo and fALFF maps \citep[e.g.][]{Sato2012a} and the NIAK high resolution (either ROI1000 or ROI3000) regional time series in their main analysis \citep[e.g.][]{Ahn2015,Yang2015}.
-Some publications also made a more marginal use of the ADHD-200 Preprocessed repository, by re-using the CC200 or CC400 functional brain parcellations \citep[e.g.][]{Dey2012,Dai2012}, and not the sample itself.
+Works have used Burner pipeline data both in isolation \citep[e.g.][]{Rangarajan2014,Rangarajan2015,Mahanand2013} or in combination with the Athena functional derivatives \citep[e.g.][]{Ji2011,Eloyan2012,Olivetti2014}.
+A fewer number of publications have also used Athena ICN, ReHo and fALFF maps \citep[e.g.][]{Sato2012a} and the NIAK high resolution (either ROI1000 or ROI3000) regional time series in their main analysis \citep[e.g.][]{Ahn2015,Yang2015}.
+Researchers have also found value in this initiative beyond the processed data, such as the CC200 or CC400 functional brain parcellations \citep[e.g.][]{Dey2012,Dai2012} and the Athena processing scripts \citep[.e.g][]{Fujita2015}.
+The three PhD dissertations \cite{Colby2012a, Dey2014phd, Zhang2012} and three master's theses \citep[][]{VanGalenLast2011,Wang2013,Vidal2014} that have used this resource have all focused on disease state prediction and data dimensionality reduction techniques.
 \par
-To the best of our knowledge, no published works have tried to directly compare the results generated by the Athena and NIAK pipeline.
-The two pipelines conceptually implement very similar steps, with key operations including the non-linear volumetric registration of individual structural MRIs in two different variants of the MNI space, and the registration of invidual BOLD and T1 images.
-The most striking difference lied in the reduction of structured noise: the Athena implemented a regression of a battery of nuisance variables (motion parameters, WM and GM signals), while NIAK implemented an automated labeling of structured noise in a spatial ICA \citep{perlbarg2007corsica}.
+To the best of our knowledge, there are no published comparisons between the results generated by the Athena and NIAK pipeline.
+The two pipelines conceptually implement very similar steps, with key operations including the non-linear volumetric registration of individual structural MRIs in two different variants of the MNI space, and the registration of individual EPI and T1 images.
+The most striking differences between the pipelines are in the software that they used and the opinions that drove the parameter choices.
+The Athena implemented nuisance variable regression \citep{lund2006_nvr,fox2005} (motion parameters, WM and GM signals), while NIAK implemented an automated labeling of structured noise in a spatial ICA \citep{perlbarg2007corsica}.
 The Athena strategy is fairly standard in the rs-fMRI community, while ICA-based noise attenuation techniques are less common.
-The other clear difference lies in the derivatives offered by the two pipelines: Athena featured a more extensive battery of maps and regional time series, while the NIAK included high-resolution (several thousands) brain parcels and associated time series.
-Beyond personal ideology, or the availability of particular features, there is no clear reason to prefer one pipeline over the other.
+Athena provided time series for a variety of low-dimension anatomical and functional brain parcellations, whereas NIAK favored much higher-resolution (several thousands) brain parcels.
+There are also differences in the type of data that each pipeline offers, Athena provides a wide variety of statistical derivatives calculated from both the functional and structural data, whereas Burner provided structural derivatives only, and NIAK primarily focused on function.
+Beyond personal ideology, the availability of particular features, or allegiances to certain software tools there is no clear reason to prefer one pipeline over the other.
 It has recently become clear that even subtle variations of processing environments can impact the end-results of processing pipelines \citep{Glatard2015-we}, even when the same processing is replicated.
-We thus believe it is important to check how variable conclusions drawn from MRI data are, depending of the specific software implementation used for processing.
-The NIAK and Athena pipeline will enable researchers to compare the robustness of their tools or analysis results to different processing choices and derivatives.
+The variety of data available through this initiative enables researchers to compare the robustness of their tools or analysis results to different processing choices and derivatives.
 \par
@@
 At the very least, some statistic that characterizes individual motion (such as root mean square deviation \cite{JenkinsonTR99}) should be included as a nuisance regressor in the group-level model \cite{sattertwhaite2012, yan2013motion}.
-Differences in the manner in which data was collected at each site can introduce addition and multiplicative effects (batch effects) to the data, which may obscure the underlying biological signal \cite{Olivetti2012,yan2013std}.
+Differences in the manner in which data was collected at each site can introduce additive and multiplicative effects (batch effects) to the data, which may obscure the underlying biological signal \cite{Olivetti2012,yan2013std}.
 Including a regressor for acquisition protocol (see Tables~\ref{smri_params_table} and \ref{rsfmri_params_table} for a summary of the different protocols), the average pairwise correlation between all regions in the brain (GCOR) \cite{saad2013gcor}, or the whole-brain average of the feature under inquiry \cite{yan2013std}, have all been shown to be effective for dealing with inter-site variation.
@@
 The ADHD-200 Preprocessed initiative was successful in terms of its primary objectives: the derivatives shared in the repository were effectively used by many researchers during and after the ADHD-200 Global Competition, with over 10,500 downloads by more than 600 users, as well as 52 resulting publications \cite{Rangarajan2014, Liang2012, Tabas2014, Rangarajan2015, Mahanand2013, Lifshitz2012, Fujita2013, Ji2011, Li2015, Li2013, Liu2012, DosSantosSiqueira2014, Olivetti2014, Han2015, Wang2013a, Dey2014, Bellec2012, Bohland2012, Chang2012, Cheng2012, Colby2012, Dai2012, Dey2012, Eloyan2012, Olivetti2012, Sato2012a, Subramanian2013, Carmona2015, Hou2015, Deshpande2015, She2014, Lavoie-Courchesne2012b, Chen2015, Nunez-Garcia2015, Solmaz2012, Anderson2014, KadkhodaeianBakhtiari2012, Sato2013, Kyeong2015, Sato2012, Takahashi2012, He2013, Kong2013, Yao2013, Yang2015, Ahn2015, Fujita2014, Reiss2014,nachamai2016sub,Brown20161238,Yu2016,Fujita2015}, 3 PhD theses \cite{Colby2012a, Dey2014phd, Zhang2012}, 3 master's dissertations \cite{VanGalenLast2011, Vidal2014, Wang2013}, and 1 patent \cite{Dey2013} derived from the release in just over three years.
-Further publications are either in press or under review, and an updated list of publications will be maintained on the Mendeley platform\footnote{\url{https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/}}.
-Although there was clearly a peak in usage around the ADHD-200 Global competition, there has been a sustained ammount of downloads and publications since then, see Figure \ref{fig:usage}, which we take as a demonstration of a long-term interest from the community in this resource.
+Further publications are either in press or under review, and an updated list of publications will be maintained in a public Mendeley group\footnote{\url{https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/}}.
+Although there was clearly a peak in usage around the ADHD-200 Global competition, there has been a sustained amount of downloads and publications since then, see Figure \ref{fig:usage}, which we take as a demonstration of a long-term interest from the community in this resource.
 \par
@@
 In particular, the winning team of the ADHD-200 Global Competition was based at the Johns Hopkins Biostatistics Department and used ADHD-200 Preprocessed to develop their diagnostic algorithm \cite{Eloyan2012}.
-We also found interesting that a handful of methodological works used the ADHD-200 Preprocessed sample as one application in a series of benchmarks that could be as varied as positron emission tomography in Alzheimer's disease \citep{Yang2015}, the Yeast gene regulatory network \citep{She2014} or gene expression in brain tissues of patients with HIV-1 associated neurocognitive disorders \citep{Liu2012}.
+We also found interesting that a handful of methodological publications used the ADHD-200 Preprocessed sample as one application in a series of benchmarks that could be as varied as positron emission tomography in Alzheimer's disease \citep{Yang2015}, the Yeast gene regulatory network \citep{She2014} or gene expression in brain tissues of patients with HIV-1 associated neurocognitive disorders \citep{Liu2012}.
 This suggests that fully processed, easy-to-access imaging samples could help validate general-purpose methods on a wider scope of applications.
@@
 The impact of the ADHD-200 Preprocessed repository demonstrated the need for reducing computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data.
-The ADHD-200 Preprocessed release has contributed and will continue to contribute to respond to that need.
-We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroimaging research.
-In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{\url{http://www.nitrc.org/forum/?group_id=383}}.
-We are also actively seeking for contributions, notably during brainhack events\citep{Cameron_Craddock2016-du}.
+While the ADHD-200 Preprocessed initiative will have a long-term impact on that need, we believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroscience research.
+In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via our web-based forum\footnote{\url{http://www.nitrc.org/forum/?group_id=383}}.
+We are  actively seeking new contributions to the Preprocessed Connectomes Project, notably during Brainhack events\citep{Cameron_Craddock2016-du}.
 An important current project is the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}} \citep{dimartino2014}.
-This new resource, still under development, will include over 15 different processing strategies for rs-fMRI processing, implemented across 4 different software packages, and 2 different pipelines for structural MRI processing.
+This new resource, still under development, will include 16 different processing strategies for rs-fMRI processing, implemented across 4 different software packages, and 2 different pipelines for structural MRI processing.
 The release will feature an harmonized organization of processed derivatives across packages and extensive quality control.

### 2016-05-28 responses_reviewers.tex
Updates from ShareLaTeX

@@
 The reports for quality control have been made publicly available for Athena\footnote{\url{http://simexp.github.io/adhd200_qc_athena/index.html}} and NIAK\footnote{\url{http://simexp.github.io/adhd200_qc_niak/index.html}}.
-We have also released a spreadhseet including the QC status for each dataset, marked either \texttt{Fail}, in the presence of a major issue, or \texttt{Pass}.
+We have also released a spreadsheet including the QC status for each dataset, marked either \texttt{Fail}, in the presence of a major issue, or \texttt{Pass}.
+\par 
 A subset of 220 subjects was graded independently by two raters, and the Cohen's kappa agreement was high (81\%) between them.
@@
 
-It includes all derivatives. The paragraph was edited to clarify this (l. XX-XX).
+``Each data type'' includes all derivatives. The paragraph was edited to clarify this (l. XX-XX).
 
@@
 We added a paragraph at the beginning of "usage recommendation" (lines XX-XX) where we describe a few works that used ADHD-200 preprocessed.
-In their vast majority all these publications aimed at predicting clinical labels from brain data, either structurally with Burner or functionally with Athena/NIAK, or both.
+The vast majority of these publications aimed at predicting clinical labels from brain data, either structurally with Burner or functionally with Athena/NIAK, or both.
 We pointed at different papers based on the derivatives they used.
-In addition, in the discussion (lines XX-XX), we referred to a handful of studies that combined ADHD-200 preprocessed to data samples from unrelated fields to evaluate statistical models, which we see as an important direction enabled by the ADHD-200 preprocessed initiative.
+In addition, in the discussion (lines XX-XX), we referred to a handful of studies that combined ADHD-200 preprocessed with data samples from unrelated fields to evaluate statistical models, which we see as an important direction enabled by the ADHD-200 preprocessed initiative.
 
@@
 
-Although there was clearly a peak in usage around the ADHD-200 Global competition, there has been a sustained amount of downloads and publications since then, see Figure \ref{fig:usage}, which we take as a demonstration of a long-term interest from the community in this resource.
+Although there was clearly a peak in usage around the ADHD-200 Global competition, there has been a sustained amount of downloads and publications since then (Figure \ref{fig:usage}), which we take as a demonstration of a long-term interest from the community in this resource.
 We added this point in the discussion (l.
@@
 We also discussed our choices re preprocessing strategies, and how this could be improved.
-Being an open community initiative, the NeuroBureau welcomes contributions from other groups.
+Being an open community initiative, the NeuroBureau welcomes contributions from any interested research group.
 The NITRC site includes a discussion forum where any interested contributor can reach out to us.
@@
 
-The Neuro Bureau is a non-profit organization registered in Germany and aimed at facilitating open science grassroots initiatives.
+The Neuro Bureau is a non-profit organization and aimed at facilitating open science grassroots initiatives.
 See the following website\footnote{\url{http://www.neurobureau.org/mission-statement/}} for the full mission statement.

### 2016-08-01 responses_reviewers.tex

@@
 
-Fixed (l. XX-XX).
+Fixed (l. 48).
 
@@
 
-Fixed (l. XX-XX).
+Fixed (l. 33).
 
@@
 
-Fixed (l. XX-XX).
+Fixed (l. 66).
 
@@
 
-Fixed (l. XX-XX).
+Fixed (legend of Figure 1, in the manuscript).
 
@@
 
-``Each data type'' includes all derivatives. The paragraph was edited to clarify this (l. XX-XX).
+``Each data type'' includes all derivatives. The paragraph was edited to clarify this (l. 174).
 
@@
 
-The z-score calculations were done on preprocessed data, registered in stereotaxic space. We edited the paragraph to clarify this (l. XX-XX).
+The z-score calculations were done on preprocessed data, registered in stereotaxic space. We edited the paragraph to clarify this (l. 172).
 
@@
 
-Fixed (l.XX-XX).
+Fixed (l. 277-278).
 
@@
 
-We added a paragraph at the beginning of "usage recommendation" (lines XX-XX) where we describe a few works that used ADHD-200 preprocessed.
+We added a paragraph at the beginning of "usage recommendation" (lines 294-306) where we describe a few works that used ADHD-200 preprocessed.
 The vast majority of these publications aimed at predicting clinical labels from brain data, either structurally with Burner or functionally with Athena/NIAK, or both.
 We pointed at different papers based on the derivatives they used.
-In addition, in the discussion (lines XX-XX), we referred to a handful of studies that combined ADHD-200 preprocessed with data samples from unrelated fields to evaluate statistical models, which we see as an important direction enabled by the ADHD-200 preprocessed initiative.
+In addition, in the discussion (lines 385-390), we referred to a handful of studies that combined ADHD-200 preprocessed with data samples from unrelated fields to evaluate statistical models, which we see as an important direction enabled by the ADHD-200 preprocessed initiative.
 
@@
 We added a reference in the discussion (l.
-XXX) to the ADHD200 preprocessed Mendeley library (https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/), an online collection of the publications that used the ADHD200.
+372) to the ADHD200 preprocessed Mendeley library (https://www.mendeley.com/groups/4198361/adhd-200-preprocessed/), an online collection of the publications that used the ADHD200.
 This resource is being regularly updated by the laboratory of Dr Craddock.
@@
 We added this point in the discussion (l.
-XX-XX).
+372-375).
 
@@
 We have expanded the discussion, as suggested, in two ways.
-First, we better emphasized the type of usage that have appeared in the literature (see our response to point 1 above).
-This helps show how the ADHD-200 prepocessed sample has been used outside of the traditional brain imaging community, and has started to be adopted by researchers doing core statistics, signal processing and machine learning research.
+First, we better emphasized the type of usage that have appeared in the literature (lines 294-306, see our response to point 1 above).
+This helps show how the ADHD-200 prepocessed sample has been used outside of the traditional brain imaging community, and has started to be adopted by researchers doing core statistics, signal processing and machine learning research (we added these points in the discussion, lines 380-381 and lines 385-390).
 We believe that to be quite unique and a potentially important development in the field.
-Second, we added a paragraph discussing the value of having two independent processing pipelines availables in the sample, which has not yet been exploited.
-To the best of our knowledge, this is a feature unique to ADHD-200 Preprocessed, which we emphasized in the abstract.
+Second, we added a paragraph discussing the value of having two independent processing pipelines availables in the sample, which has not yet been exploited (lines 307-328).
+To the best of our knowledge, this is a feature unique to ADHD-200 Preprocessed.
 Third, we have discussed the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}}, which builds on the lessons learned by releasing ADHD-200 Preprocessed.
 In this new release, we were able to include more tools, better quality control, as well as better harmonization of data organization across tools.
-Recruitment of contributions as been implemented openly, notably during public hackathons.
-We have added these points to the discussion (l.
-XX-XX).
+Recruitment of contributions as been implemented openly, notably during public hackathons (see lines 404-409).
 
@@
 We added a paragraph in the discussion (l.
-XX-XX) highlighting some of the key differences in the preprocessing parameters.
-We also discussed our choices re preprocessing strategies, and how this could be improved.
+307-328) highlighting some of the key differences in the preprocessing parameters.
+We also discussed our choices regarding preprocessing strategies, and how this could be improved.
 Being an open community initiative, the NeuroBureau welcomes contributions from any interested research group.
@@
 See the following website\footnote{\url{http://www.neurobureau.org/mission-statement/}} for the full mission statement.
-We added these details in the introduction (l.
-XX-XX).
+We added these details in the introduction (lines 17-18 and footnote 1, same page).
 
@@
 \end{quote}
-Fixed (l. XX).
+Fixed (l. 33).
 
@@
 \end{quote}
-We have removed the details on the sample size in terms of clinical category from the introduction, and kept these details in the Section "Contents of the repository".
+We have removed the details on the sample size in terms of clinical category from the introduction (line 9), and kept these details in the Section "Contents of the repository".
 
@@
 \end{quote}
-Scripts for both releases are now hosted on github. See lines XX and XX.
+Scripts for both releases are now hosted on github. See lines 80 and 221.
 
@@
 We modified the text to make this more explicit (l.
-XX-XX).
+141-143).
 
@@
 
-Fixed (l. XX)
+Fixed (l. 230)
 

### 2016-08-01 Bellec_ADHD200_2016.tex

@@
 A rigorous visual inspection of registration has also been performed using the same procedures and raters (PB and YB) as the NIAK pipeline.
-The procedure entailed generating an online report\footnote{\url{http://simexp.github.io/adhd200_qc_athena/index.html}} of registration quality for all subjects.
+The procedure entailed generating an online report\footnote{\url{http://preprocessed-connectomes-project.org/adhd200_visual_qc_athena/}} of registration quality for all subjects.
 The report includes a visualization of the individual structural images in standard space overlaid onto the corresponding brain template (MNI pediatric), as well as a visualization of the individual mean EPI image overlaid onto the corresponding structural image, both in standard space.
 These images were visually reviewed, and images with severe misregistraion or quality problems were marked as ``fail'' ($7\%$ failure rate).
-The outcome of the visual quality assessment along with summary measures of motion for the resting state fMRI scans and all other phenotypic variables have been consolidated into a tabular-separated (.tsv) spreadsheet that can be downloaded from NITRC\footnote{\url{https://www.nitrc.org/frs/download.php/9024/adhd200_preprocessed_phenotypics.tsv}}.
+The outcome of the visual quality assessment along with all available phenotypic variables have been consolidated into a tabular-separated (.tsv) spreadsheet that can be downloaded from NITRC\footnote{\url{https://www.nitrc.org/frs/download.php/9024/adhd200_preprocessed_phenotypics.tsv}}.
 
@@
 Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal ($<$1mm or degree), moderate (2 to 3 mm or degrees) or severe motion ($>$3 mm or degrees).
-The individual brain registration of the NIAK pipeline were visually inspected using online QC reports\footnote{\url{simexp.github.io/adhd200_qc_niak/}}, similar to those generated for the Athena pipeline.
+The individual brain registration of the NIAK pipeline were visually inspected using online QC reports\footnote{\url{http://preprocessed-connectomes-project.org/adhd200_visual_qc_niak/}}, similar to those generated for the Athena pipeline.
 When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory.
